### 2018-07-12 paper.tex
Add figures and partial comments to numerical results

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{epstopdf}

\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{subcaption}
\captionsetup{compatibility=false} % otherwise it raises some issues regarding compatibility

\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
%\usepackage{algorithm}% http://ctan.org/pkg/algorithms
%\usepackage{algorithmicx} 
%\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{cleveref}

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{
    % most recent feature set of pgfplots
    compat=newest,
    % some settings for grid
    grid style={black!20!white, thin, densely dotted},
    % modify plot appearance
    every axis plot/.append style={no markers, thick},
    % i like the labels a bit smaller
    label style={font=\small},
    tick label style={font=\small}
}
\usepgfplotslibrary{external} 
\tikzexternalize[prefix=TikzFigures/]

%\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
%\usepackage{hyperref} % For hyperlinks in the PDF

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{Model Order Redcution of Fluid Flow While Preserving Quadratic Invariants}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Bababk Maboudi Afkham, Nicol\`o Ripamonti, Qian Wang, Jan S. Hesthaven and Karen E. Willcox}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
\and Name of Second Author \at Name, Address of Institute \email{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

%\abstract*{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content. The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access. This allows unregistered users to read the abstract as a teaser for the complete chapter. As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.
%Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf. source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript. Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}

\abstract{In the context of model order reduction, conservation of stability in the reduced order systems of partial differential equation, especially with a strong advection term, remains a challenge. Recently preserving structures, invariants and conservation laws, in order to help with stability, and ensure robustness in long-time integrations, has been an area of active research. Energy conservation is a fundamental feature of fluid flows which is often violated in the course of model reduction. In this paper we discuss a model reduction routine, that exploits skew-symmetry of conservative and centered discretization schemes, to recover conservation of energy at the level of reduced system. This results in an, overall, correct evolution of the fluid and ensures robustness of the reduced system. We evaluate the performance of the proposed method through numerical simulation of various fluid flows, and also in a numerical simulation of continuous variable resonance combustor model.}

% sections are added here

\input{./sections/1.intro.tex}
\input{./sections/2.mor.tex}
\input{./sections/3.skew.tex}
\input{./sections/4.mor_skew.tex}
\input{./sections/5.res.tex}
\input{./sections/6.con.tex}

\bibliographystyle{plain}
\bibliography{references}

\end{document}

### 2018-07-12 sections/5.res.tex
Add figures and partial comments to numerical results

\section{Numerical Experiments} \label{sec:res}

\subsection{The incompressible Euler Equation}
\subsubsection{2D vortex merging problem}
Consider the $2D$ of the incompressible Euler equation \eqref{eq:3.8} on the square $[0,2\pi]^2$, provided with periodic boundary conditions. To treat spatial derivatives, we use Fourier spectral methods, which are equivalent to a centered finite differences scheme using as differentiation stencil the entire domain. To capture the fine details characterizing the solution, $256\times 256$ modes have been adopted. The initial condition is given in terms of the vorticity distribution $\mathbf{\omega}$. We consider the evolution of three different vortices, and the initial structure is given by
\begin{equation}\label{eqn:initial_cond_vort}
\omega = \omega_0 + \sum_{i=1}^{3} \alpha_i e^{-\dfrac{\left(x-x_i\right)^{2}+\left(y-y_i\right)^{2}}{\beta^2}}.
\end{equation}
In \eqref{eqn:initial_cond_vort}, $(x,y)$ represent the spatial coordinates, $\left( x_i, y_i\right)$ the center of the $i$-th vortex and $\alpha_i$ its maximum amplitude. In our example, we consider three vortices positioned close to the center of the domain 
\begin{equation}
\left( x_1, y_1 \right) = \left(0.75\pi,\pi\right) , \left( x_2, y_2 \right) = \left(1.25\pi,\pi\right), \left( x_3, y_3 \right) = \left(1.25\pi,1.5\pi\right),
\end{equation}
two of them having positive spin $\left( \alpha_{1,2} = \pi \right)$ and the last one rotating in the opposite direction $\left( \alpha_3 = -0.5\pi \right)$. The coefficient $\beta$, for all the vortices, is set to $\frac{1}{\pi}$. The considered triangular arrangement of vortices, is an effective initial condition for the representation of merging processes: in practice, mergers are often caused by fast-moving dipoles running into another vortex. The numerical challenge raised by this setting is the formation of thin vorticity filaments: the forces developed during the merging process drain vorticity out of the main structures into long, narrow and spiral-shaped strips of intense vorticity \cite{filaments_vort}. Given the absence of natural dissipation characterizing the Euler equation, the correct preservation of this delicate structures is necessary for an energy preserving, and consequently stable, reduced models. To have initial conditions in terms of velocity components and pressure, we define first as stream-function $\Psi$ the solution of the problem $\nabla \Psi = \omega$, and then the initial velocity is given by the curl of $\Psi$. To solve the stream-function problem, we need that the integral of $\omega$ is null: to satisfy this requirement we set $\omega_0 = 0.038$. The pressure is recovered by solving the related Poisson pressure equation. 
We use the implicit midpoint scheme as time integrator to preserve the kinetic energy of the initial condition. Having a skew-symmetric nonlinearity is of the essence: in Figure \ref{fig:unstable_full_models}, we show that formulations that are not skew symmetric lead to unstable solutions, characterized by a sudden change in the conserved quantity. The merging phenomenon is simulated for a total of $18$s using a temporal step $\Delta t=0.004$s: the same setting is adopted for simulations of reduced systems.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Comparison Skew symmetric, divergence and advective form %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
  \centering
  \begin{tikzpicture}[scale=0.5452]
    \begin{axis}[ylabel=$E_K(t)$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=south west,
                 legend entries={Skew Symmetric form, Divergent form, Advective form},
                 legend style={font=\large},
                 width=0.7\linewidth, 
                 height=0.5\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=4},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_skew_symmetric.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_divergence.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_convective.txt};
    \end{axis}%  
  \end{tikzpicture}
  \caption{Evolution of the quadratic invariant $K(t)$ for the solution to Euler equation considering three different formulations (skew-symmetric, divergent and convective forms).}
  \label{fig:unstable_full_models}
\end{figure}
Time is the only parameter considered in the reduction and $5000$ uniformly sampled snapshots are stored. A useful information regarding system reducibility is given by the singular value behaviour and in particular by the relative information content, reported in Figure \ref{fig:RIC}. Taking the first $35$ POD modes allows to maintain more than $99\%$ of the energy of the high fidelity solution: this suggest that, given the stability of the reduction procedure, we should expect an accurate reduction if a similar number of basis functions is used. Nevertheless, also smaller sets of basis functions are considered in our simulations to study the behaviour and stability of the reduced system in underrepresented scenarios.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Singular values decay merging vorteces %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\begin{tikzpicture}[scale=0.5452]
    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
                 xlabel=Basis ,
                 label style={font=\large},
                 %legend pos=north east,
                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=0.7\linewidth, 
                 height=0.5\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymin=0,
                 ymax = 2,
                 samples = 100]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = s] {./data/Incompressible_Euler/Singular_values/sv.txt};
    \end{semilogyaxis}
\end{tikzpicture}
\caption{Singular values decay of the snapshot matrix related to POD algorithms for the velocity components of the solution to the incompressible Euler problem.}
\label{fig:RIC}
\end{figure}
In Figure \ref{fig:approx_error_incompressible_Euler} we show that the error with respect to the high fidelity solution can be reduced, as expected, by increasing the number of basis and an arbitrary accuracy can be achieved at the cost of dealing with a more computationally expensive problem to be solved.

In Figure \ref{fig:energy_error_incompressible_Euler} we compare the quadratic invariant related to the high fidelity solution with the solution to the reduced models. As proved in section \ref{sec:skew.2}, the energy is preserved through the entire simulation for reduced models and it converges to the correct value as we enrich the approximating solution space.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Approximation error and energy conservation %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\centering
\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{semilogyaxis}[ylabel = $\left | \mathbf{v}(t)-\mathbf{v}^r(t) \right |^2$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 samples = 100,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_5.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_8.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_11.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_14.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_23.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_26.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_29.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_35.txt};
    \end{semilogyaxis}
\end{tikzpicture}
\caption{}
\label{fig:approx_error_incompressible_Euler}
\end{subfigure} \hfill
\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[ylabel = $|K(t)-K_r^{r}(t)|$,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=south west,
                 legend entries={$k=5$ , $k=8$, $k=11$, $k=14$, $k=23$, $k=26$, $k=29$, $k=35$},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymax = 0.5598,
                 samples = 100,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_5.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_8.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_11.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_14.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_23.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_26.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_29.txt};
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_35.txt};
    \end{axis}
\end{tikzpicture}
\caption{}
\label{fig:energy_error_incompressible_Euler}
\end{subfigure}
\label{fig:energy_approx_err}
\caption{(\protect\subref{fig:approx_error_incompressible_Euler}) Evolution of $L_2(t)$ error between the high fidelity and the reduced velocity for the Euler incompressible problem, with $k$ being the number of basis considered. (\protect\subref{fig:energy_error_incompressible_Euler}) Conservation of the kinetic energy for the solutions of the reduced problem for different values of $k$.}
\end{figure}
For a qualitative analysis, in Figure \ref{fig:snap_solution_incompressible_Euler}, four snapshots at different time frames are shown for the high fidelity solution and for different reduced solutions. The dynamic of the solution, in particular the formation and development of vorticity filaments, is correctly represented even with a moderate number of basis functions. With fewer bases, even though small details are not captured by the POD models, the positions and spreadings of the vorticity masses match.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% Snapshots of merging process %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_2.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_2.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_2.png}\\

\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_3.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_3.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_3.png}\\

\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_4.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_4.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_4.png}\\

\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_5.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_5.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_5.png}

\caption{Solutions of the three-vortices merging problem at $t=\left\{ 4,8,12,18 \right\}$. From left to right we have the solution of the reduced model with $k=17$, $k=35$ and the high fidelity solution.}
\label{fig:snap_solution_incompressible_Euler}
\end{figure}

\subsection{The Compressible Euler Equation}
\subsubsection{2D Kelvin-Helmholtz instability}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Singular values KH problem %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection{1D Shock problem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Singular values 1D problem %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\begin{tikzpicture}[scale=0.5452]
    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
                 xlabel=Basis,
                 label style={font=\large},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=0.7\linewidth, 
                 height=0.5\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymin=0,
                 ymax = 2,
                 samples = 100]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = n, y = sing_values] {./data/Compressible_Euler/1D/Singular_values/sv.txt};
    \end{semilogyaxis}
\end{tikzpicture}
\caption{Singular values decay of the snapshot matrix related to POD algorithms for the 1D compressible Euler problem.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Mass, Total momentum & Energy %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  % MASS
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{axis}[ylabel = Mass,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
                 legend entries={$k=102$ Conv,$k=201$ Conv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymin=0,
                 ymax = 2,
                 samples = 100]
                 \addplot[color=red,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/mass_102_1.txt};
                 \addplot[color=blue,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/mass_201_1.txt};
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/mass_102_1.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/mass_201_1.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_102_1.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_201_1.txt};
    \end{axis}%  
  \end{tikzpicture}
  \end{subfigure}\hfill% 
  % MASS (focus)
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{axis}[xlabel=$t$,
                 label style={font=\large},
                 legend pos=south west,
                 legend entries={$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymax=0.5000001]
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_24_1.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_102_1.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_201_1.txt};
    \end{axis}%  
  \end{tikzpicture}
  \end{subfigure}
 % TOTAL MOMENTUM
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{axis}[ylabel = Momentum,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymin=1,
                 ymax = 2,
                 samples = 100]
                 \addplot[color=red,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/momentum_102_1.txt};
                 \addplot[color=blue,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/momentum_201_1.txt};
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/momentum_102_1.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/momentum_201_1.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_102_1.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_201_1.txt};
    \end{axis}%  
  \end{tikzpicture} 
  \end{subfigure}\hfill% 
 % TOTAL MOMENTUM (focus)
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{axis}[xlabel=$t$,
                 label style={font=\large},
                 legend pos=south west,
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 ymax=1.04963,
                 scale only axis]
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_24_1.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_102_1.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_201_1.txt};
    \end{axis}%  
  \end{tikzpicture}
  \end{subfigure}
 % ENERGY
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{axis}[ylabel = Energy,
                 xlabel=$t$,
                 label style={font=\large},
                 legend pos=north east,
                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymin=2.5,
                 ymax = 4.5,
                 samples = 100]
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/energy_102_1.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/energy_201_1.txt};                
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/energy_102_1.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/energy_201_1.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_102_1.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_201_1.txt};
    \end{axis}%  
  \end{tikzpicture} 
  \caption{}
  \label{conservation_1D}
  \end{subfigure}\hfill% 
 % ENERGY (focus)
  \begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{axis}[xlabel=$t$,
                 label style={font=\large},
                 legend pos=south west,
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 ymax = 2.87438]
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_24_1.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_102_1.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_201_1.txt};
    \end{axis}%  
  \end{tikzpicture}
  \caption{}
  \label{conservation_1D_focus}
  \end{subfigure}
  \caption{(\protect\subref{conservation_1D})  Evolution of the three conserved quantities for the reduced solution of the compressible Euler equation (mass, total momentum and total energy).  The divergent, advective and skew-symmetric formulations have been considered and $k=102,204$ basis are used for the reduction. (\protect\subref{conservation_1D_focus}) Focus on the conserved quantity in case of stable reduction using the skew-symmetric formulation.} 
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\begin{subfigure}[]{0.48\linewidth}
  \begin{tikzpicture}[scale=0.55]
    \begin{semilogyaxis}[xlabel=$t$,
                 ylabel=$e(t)$
                 label style={font=\large},
                 legend pos=outer north east,
                 legend style={font=\large},
                 legend entries={$k=75$,$k=126$,$k=177$,$k=225$,$k=276$,$k=327$,$k=375$,$k=426$},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis,
                 cycle list name=exotic]
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_75.txt};  
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_126.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_177.txt}; 
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_225.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_276.txt};  
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_327.txt}; 
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_375.txt};      
                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_426.txt};              
    \end{semilogyaxis}%  
  \end{tikzpicture}
\end{subfigure}
\caption{Evolution in time of the error  between the high fidelity solution of the 1D compressible Euler and the reduced solution for different number of basis $k$. As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2\|\mathbf{p}-\mathbf{p}^r\|^2}$}.
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Snapshot of pressure and density %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[xlabel=$x$,
                 ylabel=Density,
                 label style={font=\large},
                 legend pos=south west,
                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_300.txt};
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_300.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_300.txt};
                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_300.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_300.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_300.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_300.txt};
    \end{axis}% 
\end{tikzpicture}
\end{subfigure} 
\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[xlabel=$x$,
                 ylabel=Pressure,
                 label style={font=\large},
                 legend pos=south west,
                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_300.txt};
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_300.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_300.txt};
                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_300.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_300.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_300.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_300.txt};
    \end{axis}% 
\end{tikzpicture}
\label{density_reduction}
\end{subfigure}

\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[xlabel=$x$,
                 ylabel=Density,
                 label style={font=\large},
                 legend pos=south west,
                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_1000.txt};
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_1000.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_1000.txt};
                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_1000.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_1000.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_1000.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_1000.txt};
    \end{axis}% 
\end{tikzpicture}
\end{subfigure} 
\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[xlabel=$x$,
                 ylabel=Pressure,
                 label style={font=\large},
                 legend pos=south west,
                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_1000.txt};
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_1000.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_1000.txt};
                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_1000.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_1000.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_1000.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_1000.txt};
    \end{axis}% 
\end{tikzpicture}
\end{subfigure}

\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[xlabel=$x$,
                 ylabel=Density,
                 label style={font=\large},
                 legend pos=south west,
                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_3000.txt};
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_3000.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_3000.txt};
                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_3000.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_3000.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_3000.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_3000.txt};
    \end{axis}% 
\end{tikzpicture}
\caption{}
\label{density_reduction_1D}
\end{subfigure} 
\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[xlabel=$x$,
                 ylabel=Pressure,
                 label style={font=\large},
                 legend pos=south west,
                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1.0\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_3000.txt};
                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_3000.txt};
                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_3000.txt};
                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_3000.txt};
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_3000.txt};
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_3000.txt};
                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_3000.txt};
    \end{axis}% 
\end{tikzpicture}
\caption{}
\label{pressure_reduction_1D}
\end{subfigure}
\caption{Qualitative comparison between different formulations for the reduced model in terms of density (\protect\subref{density_reduction_1D})  and pressure(\protect\subref{pressure_reduction_1D}) at $t=0.1,0.3$ and $1$s. Results for the advective formulation are not showed here because the related reduced solutions are unstable after few time steps.}
\end{figure}

\begin{figure}[h!]
\centering
\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[ylabel = e(T),
                 xlabel=Basis DEIM,
                 label style={font=\large},
                 legend pos=north east,
                 legend entries={POD+DEIM,POD},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_DEIM.txt};      
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_POD.txt};
    \end{axis}
\end{tikzpicture}
\caption{}
\label{error_DEIM}
\end{subfigure}
\begin{subfigure}[]{0.47\linewidth}
\begin{tikzpicture}[scale=0.58]
    \begin{axis}[ylabel = Energy(T),
                 xlabel=Basis DEIM,
                 label style={font=\large},
                 legend pos=north east,
                 legend entries={POD+DEIM,POD},
                 legend style={font=\large},
                 grid=both,
                 ticks=both,
                 width=1.4\linewidth, 
                 height=1\linewidth,
                 minor x tick num=1,
                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
                 scaled x ticks = true,
                 enlargelimits=false,
                 scale only axis]
                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_energy_DEIM.txt};      
                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_energy_POD.txt};
    \end{axis}
\end{tikzpicture}
\caption{}
\label{energy_DEIM}
\end{subfigure}
\caption{Comparison between standard POD and POD with DEIM treatment of the nonlinear term in terms of the error (\protect\subref{error_DEIM}) and the total energy (\protect\subref{energy_DEIM}).}
\label{fig:RIC2}
\end{figure}

\subsection{Continuous Variable Resonance Combustor}

CVRC is a model rocket combustor designed and operated at Purdue University (Indiana, U.S.) to investigate combustion instabilities \cite{yu2008combustion}. This setup is called the Continuously Variable Resonance Combustor (CVRC) because the length of the oxidizer injector can be varied continuously, allowing for a detailed investigation of the coupling between acoustics and combustion in the chamber \cite{garby2013simulations}. The 2D/3D high-fidelity simulations of CVRC are expensive. Thus to get a fast analysis tool, a quasi-1D model has been proposed by Smith et al. \cite{smith2008computational} and further developed by Frezzotti et al. \cite{frezzotti2015determination,frezzotti2017numerical,frezzotti2018quasi}.

The CVRC consists of three parts: oxidizer post, combustion chamber and exit nozzle, as shown in Fig. \ref{fig:radius}. The oxidizer is injected from the left end of the oxidizer post and meets the fuel that is injected through an annular ring around the oxidizer injector, at the back-step. The combustion happens in a region around the back-step. The combustion products flow through the chamber and exit the system from the nozzle.  Both the injector and the nozzle are operated at choked condition during the experiment. The length of the oxidizer post $L_{op}$ of the CVRC can be varied continuously, leading to different behavior of the combustion stability. In this paper, we will focus on the case with $L_{op}= 14.0$ cm, in which the combustion is unstable.

The geometry parameters of the quasi-1D CVRC with a oxidizer post length  $L_{op}= 14.0$ cm are shown in Table \ref{tab:geometry_parameters}.  The back-step and the converging part of the nozzle are sinusoidally contoured to avoid discontinuity of the radius that will invalidate the quasi-1D governing equations presented in the next subsection.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{pic/radius}
	\caption{Geometry of quasi-1D CVRC model.}
	\label{fig:radius}
\end{figure}

\begin{table} [h]
	\centering
	\caption{Geometry parameters of the quasi-1D CVRC with an oxidizer post length $L_{op}=14$ cm.}
	\centering
	\begin{tabular}{c c c c c c }
		\toprule
		\centering
		\multirow{2}{*}{Section} &
		\multicolumn{2}{c}{Oxidizer post} &
		\multirow{2}{*}{Chamber} &
		\multicolumn{2}{c}{Nozzle} \\
		\cmidrule(lr){2-3} \cmidrule(lr){5-6}
		& injector & back-step & & converging part & diverging part\\
		\midrule
		Length (cm) & 12.99 & 1.01 & 38.1 & 1.27 & 3.4 \\
		Radius (cm) & 1.02  & $1.02 \sim 2.25$ & 2.25 & $2.25 \sim 1.04$ & $1.04 \sim 1.95$ \\
		\bottomrule
		\label{tab:geometry_parameters}
	\end{tabular} 
\end{table}

The fuel is pure gaseous methane. The oxidizer is a mixture of 42\% oxygen and 58\% water (per unit mass). The oxidizer is injected in the oxidizer post at a temperature $T_{ox}=1030$ K so that both water and oxygen are in the gaseous phase. The operating conditions are listed in Table \ref{tab:operating-conditions}.

\begin{table} [h]
	\centering
	\caption{CVRC operating conditions.}
	\centering
	\begin{tabular}{l l l}
		\toprule
		\centering
		Parameter & Unit & Value \\
		\midrule
		Fuel mass flow rate, $\dot{m}_{f}$ & kg/s & 0.027   \\
		Fuel temperature, $T_{f}$ & K & 300   \\
		Oxidizer mass flow rate, $\dot{m}_{ox}$ & kg/s & 0.32   \\
		Oxidizer temperature, $T_{ox}$ & K & 1030   \\
		$O_2$ mass fraction in oxidizer, $Y_{O_2}$ & -- & 42.4\%   \\
		$H_2O$ mass fraction in oxidizer, $Y_{H_2O}$ & -- & 57.6\%   \\
		Mean chamber pressure & MPa & 1.34 \\
		Equivalence ratio, $E_r$ & -- & 0.8 \\
		\bottomrule
		\label{tab:operating-conditions}
	\end{tabular} 
\end{table}

For the combustion, we consider the one-step reaction model
\begin{equation*}\label{eq:combustion}
CH_4 + 2O_2 \rightarrow CO_2 + 2H_2O
\end{equation*}
We assume that the fuel reacts instantaneously to form products, allowing us to neglect intermediate species and finite reaction rates. As the equivalence ratio is less than one, there is oxidizer left after the combustion. Therefore, only two species need to be considered: oxidizer and combustion products.

The governing equations that describe the conservation of mass, momentum, and energy of the quasi-1D CVRC flow, are the quasi-1D unsteady Euler equations for multiple species, expressed in conservative form as
\begin{equation*}\label{eq:quasi-1D-equation}
\frac{\partial \mathbf{u}}{\partial t} + \frac{\partial \mathbf{f}}{\partial x} = \mathbf{s}_A + \mathbf{s}_f + \mathbf{s}_q.
\end{equation*}
The conserved variable vector $\mathbf{u}$ and the convective flux vector $\mathbf{f}$ are
\begin{equation*}\label{eq:CVRC-u-f}
\mathbf{u}= \left( \begin{gathered}
\rho A  \\
\rho uA  \\
\rho EA  \\
\rho Y_{ox} A \\
\end{gathered} \right), 
\mathbf{f} = \left( \begin{gathered}
\rho uA  \\
\left(\rho u^2 + p\right)A  \\
\left(\rho E + p\right)uA  \\
\rho uY_{ox} A \\
\end{gathered} \right),
\end{equation*}
where $\rho$ is the density, $u$ is the velocity, $p$ is the pressure, $E$ is the total energy, $Y_{ox}$ is the mass fraction of oxidizer, and $A=A(x)$ is the cross section area of the duct. The pressure $p$ can be computed using the conserved variables as
\begin{equation*}\label{eq:total-engery}
E = \frac{p}{\rho (\gamma - 1)} + \frac{u^2}{2} - C_p T_{ref},
\end{equation*}
where $T_{ref}$ is the reference temperature and is set as 298.15 K in this paper. The temperature $T$ is recovered from the equation of state $p = \rho R T$. The gas properties  $C_p$, $R$ and $\gamma$ are computed as $C_p= \sum C_{pi}Y_i$, $R=\sum R_iY_i$ and $ \gamma= C_p/(C_p-R)$, respectively.

The source terms are
\begin{equation*}\label{eq:source-terms}
\mathbf{s}_A = \left( \begin{gathered}
0  \\
p \frac{dA}{dx}  \\
0  \\
0 \\
\end{gathered} \right), 
\mathbf{s}_f = \left( \begin{gathered}
{\dot \omega}_f  \\
{\dot \omega}_f u  \\
{\dot \omega}_f \left(h_{0}^{f} + \Delta h_{0}^{rel} \right)  \\
{\dot \omega}_{ox} \\
\end{gathered} \right), 
{\mathbf{s}_q} = \left( \begin{gathered}
0  \\
0  \\
q'  \\
0 \\
\end{gathered} \right),
\end{equation*}
where $\dot{\omega}_f$ is the depletion rate of the fuel, $\dot{\omega}_{ox}$ is the depletion rate of the oxidizer, $h_0^f$ is the total enthalpy of the fuel, $\Delta h_{0}^{rel}$ is the heat of reaction per unit mass of fuel and $q'$ is the unsteady heat release term. $\mathbf{s}_A$ accounts for area variations, $\mathbf{s}_f$ and $\mathbf{s}_q$ are related to the combustion. $\mathbf{s}_f$ represents the addition of the fuel and its combustion with the oxidizer, which in turn results in the creation of the combustion products. The depletion rate of the fuel is
\begin{equation}\label{eq:wf}
\dot{\omega}_{f}= \frac{k_f \dot{m}_f Y_{ox} \left(1+sin\xi\right)}{l_f-l_s},
\end{equation} 
where
\begin{equation*}\label{eq:xi}
\xi= -\frac{\pi}{2} + 2\pi\frac{x-l_s}{l_f-l_s}, \hspace{0.5cm} \forall \hspace{0.2cm} l_s < x < l_f.
\end{equation*}
The setting of the fuel injection restricts the combustion to the region $l_s < x < l_f$. The reaction constant $k_f$ is selected to insure that the fuel is consumed within the specified combustion zone. The depletion rate of the oxidizer is computed by 
\begin{equation*}\label{eq:wox}
\dot{\omega}_{ox} = C_{o/f} \dot{\omega}_f,
\end{equation*}
where $C_{o/f}$ is the oxidizer-to-fuel ratio.

The unsteady heat release term $q'$, also called the combustion response function, models the coupling between acoustics and combustion. In this paper, we use the combustion response function designed by Frezzotti et al. \cite{frezzotti2017numerical,frezzotti2018quasi}, which is a function of the velocity, sampled at specific abscissa $\hat{x}$ that is almost coincident with the antinode of the first longitudinal modal shape, with a certain time lag $\tau$, i.e.,
\begin{equation}\label{eq:response-function}
q'\left( x,t\right) = \alpha g\left(x\right)  A\left(x\right) \left[ u\left( \hat{x},t-\tau \right) - \bar{u}\left( \hat{x} \right) \right].
\end{equation}
Here $\bar{u}$ is the time averaged velocity, estimated with the steady-state quasi-1D model assuming $q'=0$, and $g(x)$ is a Gaussian distribution  
\begin{equation*}\label{eq:gx}
g\left(x\right)= \frac{e^{-\frac{\left(x-\mu\right)^2}{2\sigma^2}}}{\sqrt{2\pi\sigma^2}},
\end{equation*}
where $\mu$ is the mean and $\sigma$ is the standard deviation. The amount of heat release due to velocity oscillations is controlled by the parameter $\alpha$.

The boundary conditions for the quasi-1D CVRC flow include the fixed mass flow rate and the stagnation temperature at the head-end of the oxidizer injector, and the supersonic outflow at the exit of the nozzle.

Prior to unsteady simulation, the quasi-1D CVRC needs to be excited, which can be achieved by adding a perturbation to the steady-state solution. The perturbation is added by forcing the mass flow rate with a multi-sine signal
\begin{equation}\label{eq:multisine}
\dot{m}_{ox} \left(t\right)= \dot{m}_{ox,0} \left[1 + \delta\sum_{k=1}^{K}  sin\left(2\pi k\Delta f t\right) \right],
\end{equation}
where $\dot{m}_{ox,0}$ is the oxidizer mass flow rate in Table \ref{tab:operating-conditions}, $\Delta f$ is the frequency resolution and $K$ is the number of frequencies. In this paper, $\Delta f = 50 $ Hz and $K=140$, resulting in a minimal frequency of 50 Hz and a maximal frequency of 7000 Hz. $\delta$ is required to be small to control the amplitude of the perturbation and is set as 0.1\%.

The procedure of the unsteady simulation of the quasi-1D CVRC flow includes three steps:
\begin{enumerate}[(1)]
	\item  Compute the steady-state solution by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $ and $q'=0$.
	\item  Excite the system by adding a perturbation to the oxidizer mass flow rate according to (\ref{eq:multisine}) and setting $q'=0$.
	\item  Perform the unsteady simulation by turning on the combustion response function $q'$ in (\ref{eq:response-function}) and turning off the oxidizer mass flow rate perturbation by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $.	
\end{enumerate}

A high-fidelity quasi-1D CVRC flow solver is built by employing the MUSCL reconstruction \cite{delis1998tvd}, the Lax-Friedrichs flux \cite{shu1988efficient} and the strong stability preserving, three-stage Runge-Kutta (SSP RK3) time stepping \cite{jiang1996efficient}.

### 2018-07-12 sections/5.res.tex
Add error kelvin-helmholtz problem and fix labels and caption for 1D compressible Euler example.

@@
 \subsubsection{2D Kelvin-Helmholtz instability}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%% Singular values KH problem %%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[xlabel=$t$,
+                 ylabel=$e(t)$,
+                 label style={font=\large},
+                 legend pos=outer north east,
+                 legend style={font=\large},
+                 legend entries={$k=200$,$k=300$,$k=400$,$k=500$,$k=600$},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 cycle list name=exotic]
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_200.txt};  
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_300.txt};      
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_400.txt}; 
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_500.txt};      
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_600.txt};               
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+\end{subfigure}
+\caption{Evolution in time of the error  between the high fidelity solution of the Kelvin-Helmoltz and the reduced solution for different number of basis $k$.
+As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
+\end{figure}
 
@@
     \begin{semilogyaxis}[xlabel=$t$,
-                 ylabel=$e(t)$
+                 ylabel=$e(t)$,
                  label style={font=\large},
@@
 \caption{Evolution in time of the error  between the high fidelity solution of the 1D compressible Euler and the reduced solution for different number of basis $k$.
-As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2\|\mathbf{p}-\mathbf{p}^r\|^2}$}.
+As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2+\|\mathbf{p}-\mathbf{p}^r\|^2}$.}
 \end{figure}

### 2018-07-12 sections/5.res.tex
Add error in energy, mass and momentum conservation for KH example

@@
 As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[ylabel = $\left|\mathbf{1}^T(\mathbf{r}-\mathbf{r}^r)(t)\right|$,
+                 xlabel=$t$,
+                 label style={font=\large},
+                 legend pos=north east,
+                 legend entries={$k=200$ ,$k=300$, $k=400$,$k=500$,$k=600$},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 cycle list name=exotic]
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_200.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_300.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_400.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_500.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_600.txt};
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+  \caption{}
+  \label{mass_error_KH}
+  \end{subfigure}\hfill
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[ylabel = $\left|(\mathbf{r}^{T}\mathbf{u}-\mathbf{r}^{rT}\mathbf{u}^{r})(t)\right|$,
+                 xlabel=$t$,
+                 label style={font=\large},
+                 legend pos=north east,
+%                 legend entries={$k=200$ Conv,$k=201$ Conv},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 cycle list name=exotic]
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_200.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_300.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_400.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_500.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_600.txt};
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+  \caption{}
+  \label{momentum_error_KH}
+  \end{subfigure}
+
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[ylabel = $\left| \dfrac{1}{2}\left( \mathbf{u}^{rT}\mathbf{R}^r\mathbf{u}^r-\mathbf{u}^{T}\mathbf{R}\mathbf{u}\right)\right|$,
+                 xlabel=$t$,
+                 label style={font=\large},
+                 legend pos=north east,
+%                 legend entries={$k=200$ Conv,$k=201$ Conv},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 cycle list name=exotic]
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_200.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_300.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_400.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_500.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_600.txt};
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+   \caption{}
+  \label{energy_error_KH}
+  \end{subfigure}
+\caption{Comparison between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
 \end{figure}

### 2018-07-12 sections/5.res.tex
Picture for Kelvin-Helmholtz example

@@
 \caption{Comparison between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%% Snapshots of KH %%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_307.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_307.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_307.png}\\
+
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_461.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_461.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_461.png}\\
+
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_614.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_614.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_614.png}\\
+
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_768.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_768.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_768.png}
+
+\caption{Solutions of the Kelvin-Helmholtz problem at $t=\left\{ 0.4, 0.6, 0.8, 1 \right\}$.
+From left to right we have the solution of the reduced model with $k=200$, $k=500$ and the high fidelity solution.}
+\label{fig:snap_solution_incompressible_Euler}
 \end{figure}

### 2018-07-12 paper.tex
first section of results corrected

@@
 
+\newcommand{\commnet}{\color{red}}
+
 \usepackage{tikz}
@@
 
-\title*{Model Order Redcution of Fluid Flow While Preserving Quadratic Invariants}
+\title*{Conservative Model Order Reduction of Fluid Flow}
 % Use \titlerunning{Short Title} for an abbreviated version of
@@
 
-\abstract{In the context of model order reduction, conservation of stability in the reduced order systems of partial differential equation, especially with a strong advection term, remains a challenge.
+%\abstract{In the context of model order reduction, conservation of stability for systems of hyperbolic partial differential equations, remains a challenge.
 Recently preserving structures, invariants and conservation laws, in order to help with stability, and ensure robustness in long-time integrations, has been an area of active research.
@@
 In this paper we discuss a model reduction routine, that exploits skew-symmetry of conservative and centered discretization schemes, to recover conservation of energy at the level of reduced system.
+This results in an, overall, correct evolution of the fluid and ensures robustness of the reduced system.
+We evaluate the performance of the proposed method through numerical simulation of various fluid flows, and also in a numerical simulation of continuous variable resonance combustor model.}
+
+\abstract{In the past decade, model order reduction (MOR) has been successful in reducing the computational complexity of elliptic and parabolic systems of partial differential equations (PDEs).
+However, MOR of hyperbolic equations remains a challenge.
+Symmetries and conservation laws, which are a distinctive feature of such systems, are often destroyed over the course of conventional MOR techniques.
+This often result in a perturbed, and often unstable reduced system.
+The importance of the conservation of energy is well-known in a correct numerical integration of fluid flow.
+In this paper, we discuss a model reduction routine, that exploits skew-symmetry of conservative and centered discretization schemes, to recover conservation of energy at the level of reduced system.
+Moreover, we argue that the reduced system, constructed with the new method, can be identified by a reduced energy that mimics the energy of the high-fidelity system.
+Therefore, the loss in energy, associated with model reduction, remains constant in time.
 This results in an, overall, correct evolution of the fluid and ensures robustness of the reduced system.

### 2018-07-12 sections/1.intro.tex
first section of results corrected

\section{Introduction} \label{sec:intro}

Model order reduction (MOR), and in particular reduced basis (RB) methods, has emerged as a powerful approach to cope with the complex and computationally intensive models in engineering and science. Such techniques, construct a reduced ordered representation for the state of a model which accurately approximates the configuration of the system. The evaluation of the this representation is, then, possible with considerable acceleration.

Although RB methods are successful in reducing the computational complexity of models with elliptic and parabolic partial differential equations (PDEs), MOR of systems of hyperbolic equations, or models with strong advective terms, remains a challenge. Often, such models arise from a set of invariants and conservation laws. Such symmetries are violated over the course of MOR which result in a qualitatively wrong, and sometimes unstable, solution.

Constructing MOR techniques and RB methods that preserve intrinsic structures has recently attracted attention \cite{doi:10.1137/17M1111991,1705.00498,kalashnikova2014stabilization,farhat2015structure,doi:10.1137/110836742,beattie2011structure,doi:10.1137/140978922}. Structure preservation can recover a physically meaningful reduced model, rather than a pure algebraic coupling of equations. This enforces robustness and can help with the stability of reduced model. A non-exhaustive list of recent works on structure preserving MOR is as follows. Preserving time-symmetries of Lagrangian, Hamiltonian, and port-Hamiltonian systems can be found in the works of \cite{Carlberg:2014ky,doi:10.1137/140978922,doi:10.1137/17M1111991,1705.00498,beattie2011structure,chaturantabut2016structure,gugercin2012structure}. Conserving the inf-sup stability, in the context of finite element methods, can be found in the works of \cite{farhat2015structure,ballarin2015supremizer}. Furthermore, a flux preserving model reduction for finite volume methods is presented in \cite{carlberg2018conservative}.

Large scale simulation of fluid flows appear in a wide range of disciplines and industries. Therefore, MOR of fluid flows, specially when advective terms are dominant, is of a high importance. It is well known that conservation of the energy, specially kinetic energy, is essential for a qualitatively correct numerical integration of fluid flows. Conventional model reduction techniques often violates conservation of mass, momentum \cite{carlberg2018conservative}, or energy in fluid flows which result in an unstable reduced system, specially over long time-integration. The method discussed in \cite{carlberg2018conservative} conserves the mass and momentum for a finite volume discretization scheme. However, a method that also conserves the energy of the fluid flow is not known to the authors.

Skew-symmetric forms for fluid flows are centered time and space discretization schemes, typically using a finite differences discretization method, that recovers time-symmetries of a fluid at the discrete level. Such discretization schemes are studies comprehensively over the past few decades and can be found in the works of \cite{morinishi2010skew,morinishi1998fully,desjardins2008high,reiss2014conservative,reiss2014conservative} and the references therein. These schemes construct a skew-symmetric differential operator, acting on the momentum vector field, that ensures conservation quadratic invariants, such as energy.

In this paper we discuss how to preserve skew-symmetry of differential operators at the level of reduced system. This results in conservation of quadratic invariants. Furthermore, we show that the reduced system, as a system of coupled differential equations, contains quadratic invariants and an associated energy which approximates the energy of the high-fidelity system. Therefore, a proper time stepping scheme can preserve the reduced representation of the energy, and therefore, the loss in energy due to model reduction remains constant in time.

The rest of this paper is organized as follows. In \Cref{sec:mor} we summarize the theory on MOR and introduce proper orthogonal decomposition (POD) as a conventional RB method. We discuss skew-symmetric and conservatives methods for compressible and incompressible fluid flows in \Cref{sec:skew}. Conservative and energy-preserving model reduction of fluid flows is discussed in \Cref{sec:mor_skew}. We evaluate the performance of the method, in numerical simulations of incompressible and compressible fluid flow in \Cref{sec:res}. We also apply the method to construct a reduced system for the continuous variable resonance combustor, a one dimensional reaction-diffusion model for a rocket engine. Finally, we present conclusive remarks in \Cref{sec:con}.

### 2018-07-12 sections/2.mor.tex
first section of results corrected

\section{Model Order Reduction for Time Dependent Problems} \label{sec:mor}

Consider a dynamical system of the form
\begin{equation} \label{eq:1}
	\left\{
	\begin{aligned}
		\frac{d}{dt} u(t) &= f(t,u(t)),\\
		u(0) &= u_0.
	\end{aligned}
	\right.
\end{equation}
Here, $u(t),u_0\in \mathbb R^{n}$ and $f: [0,T]\times \mathbb R^{n} \to \mathbb R^{n}$, for some $T<\infty$, is a Lipschitz function. We may apply the \emph{method of lines} \cite{Edsberg:2008:ICM:1477735} to a system of partial differential equations to obtain a dynamical system of the form \eqref{eq:1}. The \emph{solution manifold} for \eqref{eq:1} is defined as
\begin{equation} \label{eq:2}
	\mathcal M_u := \{ u(t) | t \in [0,T] \}.
\end{equation}
When $\mathcal M_u$ has a low-dimensional representation, it is referred to as \emph{reducible}. Assume that $\mathcal M_u$ can be well approximated by $k$-dimensional linear subspace $\mathcal V_k$, with $k\ll n$ and let $E_k = \{ v_1,\dots,v_k \}$ be the basis vectors for $\mathcal V_k$ and $V_k$ the basis matrix that contains these vectors in its columns. A reduced basis (RB) method assumes that $u \approx \tilde u = V_k v$, where $v$ is the expansion coefficients of $\tilde u$ in the basis $E_k$. Substituting this into \eqref{eq:1} yields
\begin{equation} \label{eq:3}
	V_k \frac{d}{dt} v(t) = f(t,V_{k}v) + r(t,u).	
\end{equation}
Here, $r$ is the error vector in this approximation. The Petrov-Galerkin projection of \eqref{eq:1} onto $\mathcal V_k$ requires $r$ to be orthogonal to a $k$-dimensional subspace $\mathcal W_k$. One can construct a projection operator $P_{\mathcal V_{k},\mathcal W_k}$ that projects elements of $\mathbb R^{n}$ onto $\mathcal V_k$, orthogonal to $\mathcal W_k$ as $P_{\mathcal V_{k},\mathcal W_k} = V_k(W_k^TV_k)^{-1}W_k^T$, where $W_k$ is the basis matrix that contains the basis vectors of $\mathcal W_k$ in its columns and $W_k^TV_k$ is assumed to be invertible. With this projection, \eqref{eq:1} reduces to
\begin{equation} \label{eq:4}
	\left\{
	\begin{aligned}
		\frac{d}{dt} v(t) &= (W_k^TV_k)^{-1} f(t,V_{k}v),\\
		v(0) &= (W_k^TV_k)^{-1}u_0.
	\end{aligned}
	\right.
\end{equation}
When we require $W_k=V_k$, then \eqref{eq:4} is referred to as the \emph{Galerkin} projection of \eqref{eq:1} onto $\mathcal V_k$. Since \eqref{eq:4} has a smaller size, as compared to \eqref{eq:1}, one can expect accelerated evaluation. To numerically identify the best possible subspace $\mathcal V_{k}$ we first discretize the solution manifold to obtain
\begin{equation} \label{eq:5}
	\mathcal M_{u}^{\Delta} = \{ u(t_i) | i\in \{ 1,\dots,N_t \} \}.
\end{equation}
Members of $M_{u}^{\Delta}$ are referred to as \emph{snapshots} of \eqref{eq:1}. One can obtain these snapshots by applying a time-integration scheme, e.g. the Runge-Kutta methods, to \eqref{eq:1} to obtain $\tilde {\mathcal M}_{u}^{\Delta}$ an approximation to $\mathcal M_{u}^{\Delta}$. Throughout this paper, we assume that we can choose $\tilde{\mathcal M}_{u}^{\Delta}$ arbitrary close to $\mathcal M_{u}^{\Delta}$, therefore, by an abuse of notation, we may drop the overscript ``\textasciitilde''. For a Galerkin projection, the best possible basis $V_k$ is the one that minimizes the collective projection error \cite{hesthaven2015certified}, i.e., the solution to the minimization problem
\begin{equation} \label{eq:6}
\begin{aligned}
&  \underset{V_k\in\mathbb R^{n\times k}}{\text{minimize}}
& &  \| S - V_kV_k^TS\|_F, \\
& \text{subject to}
& & V_k^TV_k=I_k.
\end{aligned}
\end{equation}
Here $S$ collects vectors in $\mathcal M_{u}^{\Delta}$ in its columns, referred to as the \emph{snapshot matrix}, $\|\cdot \|_F$ is the Frobenius norm \cite{trefethen97}, and $I_{k}$ is the identity matrix of size $k$. Note that the constraint in \eqref{eq:6} requires $V_k$ to be orthonormal. The basis matrix $V_k$ that solves the minimization problem \eqref{eq:6} is referred to as the \emph{proper orthogonal decomposition} (POD) of $S$ of size $k$ \cite{hesthaven2015certified}, and according to the Schmidt-Mirsky theorem, can be constructed using the left singular vectors of $S$ as
\begin{equation}
	V_{k} = [u_i]_{i=1}^{k}.
\end{equation}
Here $u_i$, for $i=1,\dots k$, are the first $k$ singular vectors of $S$.

Often MOR is studied in the parametric setting, where the vector $u,u_0$, and the right hand side function $f$ of \eqref{eq:1} are of the form $u(t;\mu)$, $u_0(\mu)$, and $f(t,u;\mu)$, respectively. Here $\mu$ belongs to $\mathbb P$, a closed subset of $\mathbb R^d$. In this case, the reduced system can approximate the quantities of interest at an accelerated rate. Since the nature of time, as a parameter, is different from other spacial and physical parameters, in this paper we solely focus on $t$ as the parameter. Nevertheless, it is straight forward to extend the results of this paper to the parameter setting by using POD in time and parameter space, or by using the POD-greedy \cite{haasdonk2013convergence,hesthaven2015certified,quarteroni2015reduced} method to generate a basis $V_k$.

Since the approximated solution $\tilde u$ is a linear combination of the POD basis vectors, $\tilde u$ inherits linear properties of these basis vectors. However, when the solution $u$ to \eqref{eq:1} satisfies some nonlinear invariants, there is no guarantee that, in general, $\tilde u$ also satisfy such invariants \cite{doi:10.1137/140959602,doi:10.1137/140978922,doi:10.1137/17M1111991,MaboudiAfkham2018}. This results in a qualitatively wrong and often unstable solution. In the later sections, we discuss how the skew-symmetric formulation of the fluid flow allows conservation of quadratic invariants, e.g. the kinetic energy, at the level of the reduced system.

### 2018-07-12 sections/3.skew.tex
first section of results corrected

\section{Skew Symmetric and Centered Schemes for Fluid Flows} \label{sec:skew}

In this section we summarize the conservative properties of skew-symmetric forms and discretization schemes, following, closely, the works of \cite{morinishi2010skew,morinishi1998fully,reiss2014conservative}.

\subsection{Conservation Laws} \label{sec:skew.1}
Transport of conserved quantities, in the context of fluid flows, can be formulated as
\begin{equation} \label{eq:3.1}
	\frac{\partial }{\partial t} \rho \varphi + \nabla \cdot ( \rho u \varphi  ) = \nabla \cdot F_{\varphi}\quad \text{defined in} \quad \Omega \subset \mathbb R^{d}.
\end{equation}
Here, $d = 1,2$ or $3$, $\rho:\Omega\to \mathbb R$ is the density, $u\in \Omega \to \mathbb R^{d}$ is the velocity vector field, $\varphi$ is a measured scalar quantity of the flow, and $F_{\varphi}$ is the flux function associated to $\varphi$. Integration of \eqref{eq:3.1} over $ \Omega$ yields
\begin{equation} \label{eq:3.2}
	\frac{d}{dt} \int_{\Omega} \rho \varphi \ dx = \int_{\partial \Omega} (F_{\varphi} - \rho u \varphi) \cdot \hat n\ ds,
\end{equation}
where $\partial \Omega$ is the boundary of $\Omega$, and $\hat n$ is the unit outward normal vector to $\partial \Omega$. When the right hand side of \eqref{eq:3.2} vanishes, e.g. in case where $\Omega$ is periodic and $\varphi$ is flux-free, the quantity $(\rho \varphi)$ is conserved. Therefore, the form \eqref{eq:3.1} is referred to the \emph{conservative form} and the convective term in \eqref{eq:3.1} is referred to as the \emph{divergence form}. However, using the \emph{continuity equation}
\begin{equation} \label{eq:3.3}
	\frac{\partial }{\partial t} \rho + \nabla \cdot (\rho u) = 0,
\end{equation}
we can rewrite \eqref{eq:3.1} as
\begin{equation} \label{eq:3.4}
	\rho \frac{\partial }{\partial t} \varphi + (\rho u)\cdot \nabla \varphi = \nabla \cdot F_{\varphi}.
\end{equation}
The convective term in this formulation is referred to as the \emph{advective form}. The \emph{skew-symmetric} form for the convective term is obtained by the arithmetic average of the divergent and the advective form:
\begin{equation} \label{eq:3.5}
	\frac{1}{2} \left( \rho \frac{\partial }{\partial t} \varphi + \frac{\partial }{\partial t} (\rho \varphi) \right) + \frac 1 2 \left( (\rho u)\cdot \nabla \varphi + \nabla \cdot (\rho u \varphi) \right) = \nabla \cdot F_{\varphi}.
\end{equation}
Multiplying \eqref{eq:3.5} with $\varphi$ yields
\begin{equation}
	\frac{\partial }{\partial t} \rho \varphi^2 + \nabla \cdot ( \rho u \varphi^2  ) = \varphi \nabla \cdot F_{\varphi}.
\end{equation}
Therefore, $\varphi^2$ is a conserved quantity for a flux-free $\varphi$. Since the divergence, the advective and the skew-symmetric forms are identical at the continuous level, then $\varphi^2$ is a conserved quantity for all forms. However, equivalence of these forms is not preserved through a general discretization scheme and, therefore, we do not expect $\varphi^2$ to be a conserved quantity at the discrete level. To motivate numerical advantages of the skew-symmetric form consider the operator 
\begin{equation}
	S_{\rho u}(\cdot) = \frac 1 2 ( [ \nabla \cdot \rho u ] + (\rho u)\cdot \nabla )(\cdot).
\end{equation}
With a proper set of boundary condition, this operator is a skew-adjoint operator with respect to the $L^2$ inner-product. Here, $[\cdot]$ indicates that the inside of brackets act as a differential operator. This skew-adjoint property is used in later sections to show the conservation of some quadratic quantities in \eqref{eq:3.1}. Similarly, we can define a skew-adjoint operator with respect to the time variable as
\begin{equation}
	S_{\rho,\partial_t} = \frac{1}{2} \left( \rho \frac{\partial}{\partial t} + [ \frac{\partial}{\partial t} \rho] \right).
\end{equation}
Here, the subscript $\partial t$ is to emphasize that $S_{\rho,\partial_t}$ is a differential operator with respect to $t$. A proper time and space integration of $S_{\rho u}$ and $S_{\rho,\partial_t}$, usually with centered discretization schemes, can preserve the skewness property.

Numerical time integration of \eqref{eq:3.5} can be challenging since the time differentiation of different variable is present. However, following derivations in \cite{morinishi2010skew}, one can rewrite \eqref{eq:3.5} as
\begin{equation} \label{eq:3.6}
	\sqrt{\rho } \frac{\partial }{\partial t} (\sqrt \rho \varphi ) + S_{\rho u}(\varphi) = \nabla \cdot F_{\varphi}.
\end{equation}
Time integration of this form is presented in the works of \cite{morinishi2010skew,reiss2014conservative}. Note that one can also generate a quasi-skew-symmetric form \cite{blaisdell1991numerical,morinishi2003dns} of \eqref{eq:3.1} as
\begin{equation} \label{eq:3.7}
	\frac{\partial }{\partial t} (\rho \varphi) + S_{\rho u}(\varphi) = \nabla \cdot F_{\varphi}.
\end{equation}
Even though this is not a fully skew-symmetric form (skew-symmetric only in space), the numerical stabilities of this form is significantly better than the divergence and advective form \cite{morinishi2010skew,blaisdell1991numerical,morinishi2003dns}. Note that the quasi-skew-symmetric form is identical to the skew-symmetric form in the incompressible limit.

\subsection{Incompressible Fluid} \label{sec:skew.2}
Consider the governing equations of an incompressible fluid with skew-symmetric convective term:
\begin{equation} \label{eq:3.8}
	\left\{
	\begin{aligned}
	&\nabla \cdot u = 0, \\
	&\frac{\partial}{\partial t} u + S_{u}(u) + \nabla p = \nabla \cdot \tau,
	\end{aligned}
	\right.
\end{equation}
defined on $\Omega$. Here, $p: \Omega \to \mathbb R^+$ is the pressure, $\tau: \Omega \to \mathbb R^{d\times d}$ is the viscous stress tensor, and $S_u = \frac 1 2 ([ \nabla \cdot u] + u\cdot \nabla)$. It is straight forward to check
\begin{equation} \label{eq:3.9}
	\frac{d}{dt} K + \nabla \cdot (Ku) + \nabla \cdot (pu)= \nabla \cdot (\tau u) - (\tau \nabla)\cdot u,
\end{equation}
where $K = \frac 1 2 \sum_{i=1}^d u_i^2 $ is the kinetic energy. Here we used 
\begin{equation} \label{eq:3.10}
	\begin{aligned}
	u\cdot \nabla p &= \nabla \cdot (up) - p\nabla \cdot u, \\
	u \cdot (\nabla \cdot \tau) &= \nabla \cdot (\tau u) - (\tau \nabla)\cdot u,
	\end{aligned} 
\end{equation}
and
\begin{equation} \label{eq:3.11}
	u\cdot S_{u}(u) = \nabla \cdot(Ku).
\end{equation}
The only non-conservative term in \eqref{eq:3.9} is $-(\tau \nabla)\cdot u$, which corresponds to dissipation of kinetic energy. Therefore, in the absence of the viscous terms, $K$ is a conserved quantity of the system, and $\frac d {dt} \int_{\Omega} K \ dx <0$ when $\tau\neq 0$. Note that as long as $\nabla \cdot u = 0$, as discussed in \Cref{sec:skew.1}, the divergence, the convective, and the skew-symmetric forms are identical for the incompressible fluid equation. Thus, kinetic energy is conserved for all forms. However, for a general discretization scheme, these forms are not identical, and often the conservation of kinetic energy, in the discrete sense, is violated.

The skew-symmetric discretization of \eqref{eq:3.8} is a centered scheme that exploits the skew-adjoint property of $S_u$, and ensures conservation of kinetic energy at the discrete level. We uniformly discretize $\Omega$ into $N$ points and denote by $\mathbf u \in \mathbb R^{N\times d}$, $\mathbf p \in \mathbb R^N$, and $T \in R^{N\times d\times d} $ the discrete representation of $u$, $p$, and $\tau$, respectively. Let $D_j$ be the centered finite difference matrix operator for $\partial / \partial x_j$, and for $j = 1,\dots,d$. The momentum equation in \eqref{eq:3.8} is then discretized as
\begin{equation} \label{eq:3.13}
	\frac{d}{dt}{\mathbf u}_i + S_{\mathbf u} \mathbf u_i + D_i \mathbf p = \sum_{j=1}^d D_j T_{ij}, \quad i=1,\dots,d,
\end{equation}
where $S_{\mathbf u}$ is the discretization of $S_{u}$ given by
\begin{equation} \label{eq:3.14}
	S_{\mathbf u} = \sum_{j=1}^d D_j U_j + U_j D_j,
\end{equation}
and $U_i$ contains components of $\mathbf u_i$ on its diagonal. We require $D_i$ to satisfy
\begin{enumerate}
	\item $D_i = -D_i^T$
	\item $D_i \mathbf 1 = \mathbf 0$, where $\mathbf 1$ and $\mathbf 0$ are vectors of ones and zeros, respectively.
\end{enumerate}
Condition 1 and 2 yield
\begin{equation} \label{eq:3.15}
	S_{\mathbf u} = -S_{\mathbf u}^T, \quad \mathbf 1^T S_{\mathbf u} \mathbf u_i = 0, \quad i=1,\dots,d.
\end{equation}
Conservation of momentum in the discrete sense reads
\begin{equation} \label{eq:3.16}
	\frac{d}{dt} \sum_{i=1}^d  \mathbf 1^T \mathbf u_i = \sum_{i=1}^d \left( - \mathbf 1^T S_{\mathbf u} \mathbf u_i - \mathbf 1^T D_i \mathbf p + \sum_{j=1}^d \mathbf 1^T D_j T_{ij}  \right) = 0.
\end{equation}
Similarly, using \eqref{eq:3.10}, it is verified that
\begin{equation} \label{eq:3.17}
\frac{d}{dt} \sum_{i=1}^d \left( \frac 1 2 \mathbf u_i^T \mathbf u_i \right) = - \sum_{i,j=1}^d T_{ij}D_j \mathbf u_i \leq 0.
\end{equation}

Conditions 1 and 2 for $D_i$ can be easily checked for a centered finite differences scheme on a periodic domain. For other types of boundaries, e.g., wall boundary and inflow/outflow, we refer the reader to \cite{morinishi1998fully,desjardins2008high} for construction of the proper discrete centered differentiation operator.

\subsection{Compressible Fluid} \label{sec:skew.3}
Consider the equation governing the evolution of a compressible fluid in a skew-symmetric form in one spacial dimension
\begin{equation} \label{eq:3.18}
\left\{
\begin{aligned}
	&\frac{\partial}{\partial t} \rho + \frac{\partial }{\partial x}(\rho u) = 0, \\ 
	& S_{\rho,\partial_t}(u)+ S_{\rho u}(u) + \frac{\partial }{\partial x} p = \frac{\partial }{\partial x} \tau, \\
	&\frac{\partial}{\partial t} \rho E + \frac{\partial}{\partial x}(u E + up) = \frac{\partial }{\partial x}(u\tau - \phi).
\end{aligned}
\right.
\end{equation}
Here $E= e + u^2/2$ is the total energy per unit mass, with $e = \frac{p}{\rho(\gamma - 1)}$ the internal energy, $\gamma$ the adiabatic gas index, and $\phi = -\lambda \frac{\partial T}{\partial x}$ is the heat flux, with $\lambda$ the heat conductivity. The rest of the variables are the same as those discussed in \Cref{sec:skew.2}. Following \cite{reiss2014conservative}, the evolution of the momentum equation reads
\begin{equation} \label{eq:3.19}
	\begin{aligned}
	\frac{\partial}{\partial t}(\frac{\rho u^2}{2}) + \frac{\partial }{\partial x}(\rho u \frac{u^2}{2}) &= \frac 1 2 u( \frac{d}{dt} \rho u + \rho \frac{d}{dt} u ) + \frac 1 2 u ( [ \frac{\partial}{\partial x} \rho u ] u + \rho u \frac{\partial }{\partial x} u ) \\
	& = - u \frac{\partial}{\partial x} p + u \frac{\partial}{\partial x} \tau.
	\end{aligned}
\end{equation}
Substituting this into the energy equation in \eqref{eq:3.18} while assuming a constant adiabatic index yields
\begin{equation} \label{eq:3.20}
	\frac{1}{\gamma -1} \frac{d}{dt} p + \frac{\gamma}{\gamma -1} \frac{\partial }{\partial x} up - u \frac{\partial }{\partial x}(p) = - u \frac{\partial}{\partial x} \tau + \frac{\partial }{\partial x}(u\tau - \phi).
\end{equation}

We discretize the real line, uniformly, into $N$ grid points and denote by $\mathbf r, \mathbf u, \mathbf p \in \mathbb R^{N}$, the discrete representations of $\rho$, $u$, and $p$, respectively. Using the matrix differentiation operator $D\in \mathbb R^{N\times N}$ (we omit the subscript ``$i$'' for the one dimensional case), introduced in \Cref{sec:skew.2}, we define the skew-symmetric matrix operator $S_{\mathbf r \mathbf u} = \frac 1 2 (DUR + RUD)$, where $R$ is the matrix that contains $r$ in its diagonal. Now, a semi-discretization of \eqref{eq:3.18} and \eqref{eq:3.20} takes the form
\begin{equation} \label{eq:3.21}
\left\{
\begin{aligned}
	& \frac{d}{dt} \mathbf r + DU\mathbf r = 0, \\
	& S_{\mathbf r,\partial_t} (\mathbf u) + S_{\mathbf r \mathbf u} \mathbf u + D \mathbf p = D T, \\
	&\frac{1}{\gamma -1} \frac{d}{dt} \mathbf p + \frac{\gamma}{\gamma -1} D U \mathbf p - UD\mathbf p = - UDT + D(UT - \mathbf \phi).
\end{aligned}
\right.
\end{equation}

Considering conditions 1 and 2 for $D$, discussed in \Cref{sec:skew.2}, it is easily verified that
\begin{equation} \label{eq:3.22}
	S_{\mathbf r \mathbf u}^T = - S_{\mathbf r \mathbf u}, \quad \mathbf 1^T S_{\mathbf r \mathbf u} \mathbf u = - \mathbf u^T DU \mathbf r.
\end{equation}
Conservation of mass yields
\begin{equation} \label{eq:3.23}
	\frac{d}{dt} (\mathbf 1^T \mathbf r) = - \mathbf 1^T DR\mathbf u = 0. 
\end{equation}
Furthermore, we recover conservation of momentum in the discrete sense as
\begin{equation} \label{eq:3.24}
\begin{aligned}
	\frac{d}{dt}(\mathbf r^T \mathbf u) &= \frac{1}{2} \frac{d}{dt}(\mathbf r^T \mathbf u) + \frac{1}{2} \left( \mathbf r^T \frac d{dt} \mathbf u +\mathbf u^T \frac{d}{dt} \mathbf r \right)\\
	&= \frac{1}{2}u^T \frac d{dt} \mathbf r + \mathbf 1^T S_{\mathbf r,\partial_t} (\mathbf u) \\
	&= -\frac 1 2 \mathbf u^T DU \mathbf r  - \frac 1 2 \mathbf 1^T S_{\mathbf r \mathbf u} \mathbf u - \mathbf 1^T D\mathbf p +  \mathbf 1^T D T = 0.
\end{aligned}
\end{equation}
Here we used \eqref{eq:3.22} and the mass and the momentum equation in \eqref{eq:3.21}. Similarly, for the conservation of the total energy, we have
\begin{equation} \label{eq:3.25}
\begin{aligned}
	\frac{d}{dt} \left( \frac{1}{\gamma - 1} \mathbf 1^T \mathbf p + \frac 1 2 \mathbf (R\mathbf u)^T \mathbf u  \right) &= \frac{d}{dt} \left( \frac{1}{\gamma - 1} \mathbf 1^T \mathbf p \right) + \frac 1 2 \mathbf u^T  S_{\mathbf r,\partial_t} (\mathbf u) = 0.
\end{aligned}
\end{equation}
In addition to the conservation of the total energy, skew-symmetric form of \eqref{eq:3.21} also conserves the evolutions of the kinetic energy:
\begin{equation} \label{eq:3.26}
\begin{aligned}
	\frac{d}{dt} ( \frac 1 2 \mathbf u^T R\mathbf u) = \frac 1 2 \mathbf u^T S_{\mathbf r,\partial_t} (\mathbf u) &= -\mathbf u ^T S_{\mathbf r \mathbf u} \mathbf u + \mathbf u^T D p + \mathbf u^T DT \\
	&= \mathbf u^T D p + \mathbf u^T DT.
\end{aligned}
\end{equation}
Here, we used the skew-symmetry of $S_{\mathbf r \mathbf u}$. Therefore, only the pressure and viscous terms contribute to a change in the level of kinetic energy.

We point out that there are other methods to obtain a skew-symmetric form for \eqref{eq:3.18}, that result in the conservation of other quantities. An entropy preserving skew-symmetric form can be found in \cite{sjogreen2010skew}. Furthermore, a fully quasi-skew-symmetric form for \eqref{eq:3.18}, where all quadratic fluxes are in a skew-symmetric form, is shown to have lowest aliasing error \cite{honein2004higher,honein2005numerical}

\subsection{Time integration}
Following steps in \cite{reiss2014conservative,morinishi2010skew} we can construct a fully discrete scheme for \eqref{sec:skew.3} as
\begin{equation} \label{eq:3.27}
	\left\{
	\begin{aligned}
	&\frac 1 2 \sqrt{\mathbf r} ^{n+1/2} \frac{\sqrt{\mathbf r}^{n+1} - \sqrt{\mathbf r}^{n}}{\Delta t} + DU^{n+1/2} \mathbf r^{n} = 0, \\
	& \sqrt{\mathbf r} ^{n+1/2}  \frac{\sqrt{ \mathbf R}^{n+1} u^{n+1} - \sqrt{\mathbf R}^{n}u^n}{\Delta t} + S_{\mathbf r^{n} \mathbf u^n} \mathbf u^{n+1/2}_\alpha + D \mathbf p^{n} = DT^{n}, \\
	& \frac 1 {\gamma -1} \frac{\mathbf p^{n+1} - \mathbf p^n}{\Delta t} + \frac{\gamma}{\gamma -1} D U^{n} \mathbf p - U^{n} D \mathbf p = - U^{n}D T^{n} + D (U^nT^n - \phi^n).
	\end{aligned}
	\right.
\end{equation}
Here, $\Delta t$ is the time discretization unit, superscript $n$ denotes evaluating a variable at $t = n\Delta t$, superscript $n+1/2$ denotes the arithmetic average of a variable evaluated at $t=n\Delta t$ and $t=(n+1)\Delta t$, the square root sign denotes element-wise application of square root, and 
\begin{equation}
	\mathbf u_{\alpha}^{n+1/2} = \frac{\sqrt{\mathbf R}^{n+1} \mathbf u^{n+1} + \sqrt{\mathbf R}^{n} \mathbf u^{n}}{2\sqrt{\mathbf r}^{n+1/2} }.
\end{equation}
It is discussed in \cite{reiss2014conservative} that this time discretization scheme preserves the symmetries expressed in \eqref{eq:3.17}, \eqref{eq:3.24}, \eqref{eq:3.25}, and \eqref{eq:3.26}. In the incompressible case, the method reduces to the implicit mid-point scheme \cite{hairer2006geometric}. For further information see \cite{reiss2014conservative,morinishi2010skew}.

### 2018-07-12 sections/4.mor_skew.tex
first section of results corrected

\section{Model Reduction of Fluid Flow} \label{sec:mor_skew}
Straight forward model reduction of \eqref{eq:3.8} and \eqref{eq:3.18} does not, in general, preserves symmetries and conservation laws that were presented in \Cref{sec:skew}. In this section we discuss how to exploit the discrete skew-symmetric structure of \eqref{eq:3.13} and \eqref{eq:3.21} to recover conservation of mass, momentum, and energy at the level of reduced system.

Let $V_{\mathbf r}$, $V_{\mathbf r \mathbf u}$, and $V_{\mathbf u_i}$ be the reduced bases for the snapshots of $\mathbf r$, $R \mathbf u$, and $\mathbf u_i$, respectively. For the one dimensional case, the subscript ``$i$'' is omitted and in case of an incompressible fluid, $V_{ \mathbf r}$ and $V_{\mathbf r \mathbf u}$ are not computed. For the purpose of simplicity, we assume that all bases have the size $k$. We seek to project $S_{\mathbf u}$ and $S_{\mathbf r \mathbf u}$ onto the reduced space, such that the projection preserves the skew-symmetry property. The projected operators, using a Galerkin projection, read
\begin{equation} \label{eq:4.1}
	S^r _{\mathbf u} = V_{ \mathbf u_i}^T S _{\mathbf u} V_{ \mathbf u_i}, \quad i=1,\dots,d,
\end{equation}
and
\begin{equation} \label{eq:4.2}
	S^r_{\mathbf r ,\partial_t} =V_{\mathbf r \mathbf u}^T  S_{\mathbf r ,\partial_t} V_{\mathbf u}, \quad S^r _{\mathbf r \mathbf u} = V_{\mathbf r \mathbf u}^T  S _{\mathbf r \mathbf u} V_{\mathbf u}.
\end{equation}
Note that $S^r_{\mathbf r ,\partial_t}$ is not computed explicitly. It is seen that the $S^r _{\mathbf u}$ is already in a skew-symmetric form. On the other hand, $S^r_{\mathbf r ,\partial_t}$ and $S^r _{\mathbf r \mathbf u}$ are not, in general, skew-adjoint and skew-symmetric, respectively. This can be ensured, however, by requiring $V_{\mathbf r \mathbf u} = V_{\mathbf u}$. We denote such a basis by $V_{\mathbf r \mathbf u, \mathbf u}$.Using \eqref{eq:4.1} and \eqref{eq:4.2}, a Galerkin projection of momentum equation in \eqref{eq:3.13} and governing equations for a compressible fluid in \eqref{eq:3.21} take the form
\begin{equation} \label{eq:4.3}
	\frac{d}{dt} {\mathbf u^r}_i + S^r_{\mathbf u} \mathbf u^r_i + V_{\mathbf u_i} ^T D_i \mathbf p = \sum_{j=1}^d V_{k_3, \mathbf u_i}^T D_j T_{ij}(V_{ \mathbf u_i} \mathbf u^r_i), \quad i=1,\dots,d,
\end{equation}
and
\begin{equation} \label{eq:4.4}
\left\{
\begin{aligned}
	& \frac{d}{dt} \mathbf r^r + \sum_{i=1}^k V^T_{\mathbf r}DU_iV_{\mathbf r}\mathbf r^r = 0, \\
	& S^r_{\mathbf r ,\partial_t} + S^r _{\mathbf r \mathbf u} \mathbf u^r + V_{\mathbf r \mathbf u, \mathbf u}^T D \mathbf V_{\mathbf p} \mathbf p^r = V_{\mathbf r \mathbf u, \mathbf u}^T D T, \\
	&\frac{1}{\gamma -1} \frac{d}{dt} \mathbf p^r + \frac{\gamma}{\gamma -1} \mathbf V_{\mathbf p}^T D U V_{\mathbf p} \mathbf p^r - \mathbf V_{\mathbf p}^T UD V_{\mathbf p} \mathbf p^r = - V_{\mathbf p}^T UDT + V_{\mathbf p}^T D(UT - \mathbf \phi).
\end{aligned}
\right.
\end{equation}
Note that in \eqref{eq:4.4}, dependency of $T$ on $V_{\mathbf r \mathbf u , \mathbf u}$ is not shown for abbreviation. In \eqref{eq:4.3} and \eqref{eq:4.4}, $D_i$ is always multiplied from left with a basis matrix or a diagonal matrix. Therefore, the telescoping sum discussed in condition 2 in \Cref{sec:skew.1} cannot be used to show conservation of mass and momentum. However, POD preserves linear properties of snapshots. To demonstrate, let the overscript ``\textasciitilde'' denote the representation of a reduced variable in the high fidelity space. A reduced variable, e.g. density, can be represented as a linear combination of some snapshots as $\mathbf r \approx \tilde{\mathbf r} = \sum_{i=1}^k c_i \mathbf r_i$, for some snapshots $\mathbf r_i$ and some coefficients $c_i \in \mathbb R$, for $i=1,\dots,k$. The conservation of mass, evaluated by $\tilde{\mathbf r}$, reads
\begin{equation} \label{eq:4.5}
	\frac{d}{dt} \mathbf 1^T \tilde {\mathbf r} = \sum_{i=1}^k c_i  \left( \mathbf 1^T \frac{d}{dt} \mathbf r_i \right) = - \sum_{i=1}^k c_i  \left( \mathbf 1^T DR_i\mathbf u_i \right) = 0.
\end{equation}
Here we used the fact that $\mathbf 1^T D = \mathbf 0^T$. Similarly, we recover conservation of momentum
\begin{equation} \label{eq:4.6}
\begin{aligned}
	\frac{d}{dt}(\tilde {\mathbf r}^T \tilde{\mathbf u}) &= \frac{1}{2} \frac{d}{dt}(\tilde{\mathbf r}^T \tilde{\mathbf u}) + \frac{1}{2} \left( \tilde{ \mathbf r }^T \frac d{dt} \tilde{ \mathbf u } + \tilde {\mathbf u}^T \frac{d}{dt} \tilde {\mathbf r} \right)\\
	&= \sum_{i,j=1}^k d_i c_j \left( \mathbf u_i^T \frac{d}{dt} \mathbf r_j + \left( \mathbf r_j^T \frac d{dt} \mathbf u_i +\mathbf u_i^T \frac{d}{dt} \mathbf r_j \right)\right) = 0.\\
\end{aligned}
\end{equation}
Here, $\tilde{\mathbf u} = \sum_{i=1}^k d_i \mathbf u_i$, for some snapshot $\mathbf u_i$ and coefficients $d_i \in \mathbb R$. Denoting by $\{ R \mathbf u\}^r$ the reduced representation of $R\mathbf u$ in basis $V_{\mathbf r \mathbf u , \mathbf u}$, the evolution of kinetic energy reads
\begin{equation} \label{eq:4.7}
	\begin{aligned}
	\frac{d}{dt}\left( \frac 1 2 \tilde{\mathbf u}^T \tilde{ R } \tilde {\mathbf u} \right) &= \frac{d}{dt}\left( \frac 1 2 {\mathbf u^r}^T V_{\mathbf r \mathbf u , \mathbf u}^T V_{\mathbf r \mathbf u , \mathbf u} \{ R \mathbf u\}^r \right) = \frac{d}{dt}\left( \frac 1 2 {\mathbf u^r}^T \{ R \mathbf u\}^r \right) \\
	&= \frac 1 2 \left( {\mathbf u^r}^T \frac{d}{dt} \{ R \mathbf u \}^r + \{ R \mathbf u \}^r \frac{d}{dt} \mathbf u^r \right) \\
	&= \frac 1 2 \left( {\mathbf u^r}^T V_{\mathbf r \mathbf u , \mathbf u}^T V_{\mathbf r \mathbf u , \mathbf u} \frac{d}{dt} \{ R \mathbf u \}^r + \{ R \mathbf u \}^r \frac{d}{dt} V_{\mathbf r \mathbf u , \mathbf u}^T V_{\mathbf r \mathbf u , \mathbf u} \mathbf u^r \right) \\
	&= {\mathbf u^r}^T S^r_{\mathbf r, \partial_t} \mathbf u^r = { \mathbf u^r }^T V_{\mathbf r \mathbf u , \mathbf u} D V_{\mathbf p} \mathbf P^r + { \mathbf u^r }^T V_{\mathbf r \mathbf u , \mathbf u}^T D T.
	\end{aligned}
\end{equation}
In the missing steps in the last line, the skew-symmetry of $S_{\mathbf r \mathbf u}^r$ is used. Note, that only the reduced pressure and the viscous term contribute to the evolution of kinetic energy. Furthermore, the quantity $ \frac 1 2 {\mathbf u^r}^T \{ R \mathbf u\}^r$ is the kinetic energy associated with the reduced system \eqref{eq:4.4} that approximates the kinetic energy of the high-fidelity system \eqref{eq:3.21} and is a quadratic form with respect to the reduced variables. Conservation of kinetic energy for \eqref{eq:4.3} follows similarly. With what discussed above, it is  straight forward to check that
\begin{equation} \label{eq:4.8}
	\frac{d}{dt} \left( \frac{1}{\gamma - 1} \mathbf 1^T \tilde{\mathbf p} + \frac{1}{2} \tilde{\mathbf u}^T \tilde R \tilde{\mathbf u} \right) = 0,
\end{equation}
i.e., the total energy is conserved. We can immediately recognize that $ \mathbf p^r /(\gamma - 1)$ is the internal energy of the reduced system. However, the total internal energy of \eqref{eq:4.4} is a weighted sum, $ b^T\mathbf p^r /(\gamma - 1)$, with $b = V_{\mathbf p}^T \mathbf 1$ which is an approximation of the total internal energy in \eqref{eq:3.21}. From \eqref{eq:4.5}, \eqref{eq:4.6}, \eqref{eq:4.7}, and \eqref{eq:4.8} we conclude the following proposition.
\begin{proposition}
	The loss in the mass, momentum and energy associated with model reduction in \eqref{eq:4.4} is constant in time, and therefore, bounded.
\end{proposition}

\subsection{Assembling Nonlinear Terms and Time Integration}
Nonlinear terms that appear in \eqref{eq:4.3} and \eqref{eq:4.4} are of quadratic nature. These terms can be evaluated exactly using a set of precomputed matrices as proposed in \cite{Benner2018}. As an example, consider
\begin{equation}
	S_{\mathbf u}^r = V^T_{\mathbf u} ( DU + UD ) V^T_{\mathbf u},
\end{equation}
for simplicity in one spacial dimension. We write $U$ as a linear combination of matrices as $U = \sum_{j=1}^k \mathbf u ^r_j U_j$, where $\mathbf u ^r_j$ is the $j$th component of $\mathbf u ^r$, and $U_j$ contains the $j$th column of $V_{\mathbf u}$ on its diagonal. It follows
\begin{equation}
	S_{\mathbf u}^r = \sum_{j=1}^k \mathbf u ^r_j \left( V^T_{\mathbf u} ( DU_j + U_jD ) V^T_{\mathbf u} \right),
\end{equation}
and the matrices $V^T_{\mathbf u} ( DU_j + U_jD ) V^T_{\mathbf u}$ can be computed prior to the time integration of the reduced system. However, the form of the fully discrete system in \eqref{eq:3.27} introduces cubic and even quartic terms. Although, in principle, the same method can be applied to assemble the nonlinear terms, however, the number of precomputed matrices can grow proportional to the order of nonlinear term.

To accelerate the assembly of the nonlinear terms that require a large number of precomputed matrices, we may approximately evaluate them using the discrete empirical interpolation method (DEIM). This approximation can affect the accuracy of conserved quantities in \eqref{eq:4.4}. Therefore, the accuracy of DEIM approximation should be chosen considerably higher than the one from POD.

To integrate \eqref{eq:4.4} in time, the fully discrete system \eqref{eq:3.27} is modified prior to model reduction, by dividing the mass and momentum equation with $\sqrt{\mathbf r}^{n+1}$. Note that since the new form is identical to \eqref{eq:3.27}, it does not affect the conserved quantities. Subsequently, a basis for $\sqrt{\mathbf r}$, denoted by $V_{\sqrt{\mathbf r}}$, is constructed. The nonlinear terms, are evaluated exactly using the quadratic expansion or approximated using the DEIM.

### 2018-07-12 sections/5.res.tex
first section of results corrected

--- 2018-07-12 sections/5.res.tex
@@
 
-\subsection{The incompressible Euler Equation}
-\subsubsection{2D vortex merging problem}
-Consider the $2D$ of the incompressible Euler equation \eqref{eq:3.8} on the square $[0,2\pi]^2$, provided with periodic boundary conditions.
-To treat spatial derivatives, we use Fourier spectral methods, which are equivalent to a centered finite differences scheme using as differentiation stencil the entire domain.
+\subsection{Vortex Merging}
+Consider the $2D$ incompressible Euler equation, \eqref{eq:3.8} with no viscous term, on a square domain $\Omega = [0,2\pi]^2$, provided with periodic boundary conditions.
+Spatial derivatives are discretized using a Fourier spectral method, which in centered differential operators in the Fourier space.
 To capture the fine details characterizing the solution, $256\times 256$ modes have been adopted.
-The initial condition is given in terms of the vorticity distribution $\mathbf{\omega}$.
+The initial condition is given in terms of the vorticity distribution $\mathbf{\omega} = \nabla \times u$ {\commnet \{ check this \}}.
+
 We consider the evolution of three different vortices, and the initial structure is given by
@@
 \end{equation}
-In \eqref{eqn:initial_cond_vort}, $(x,y)$ represent the spatial coordinates, $\left( x_i, y_i\right)$ the center of the $i$-th vortex and $\alpha_i$ its maximum amplitude.
-In our example, we consider three vortices positioned close to the center of the domain
+In \eqref{eqn:initial_cond_vort}, $(x,y)$ represents the spatial coordinates, $\left( x_i, y_i\right)$ is the center of the $i$th vortex, $\alpha_i$ its maximum amplitude, and $\beta$ controls the effective radius of the vortex.
+In this example, the center of three vortices are positioned at
 \begin{equation}
@@
 \end{equation}
-two of them having positive spin $\left( \alpha_{1,2} = \pi \right)$ and the last one rotating in the opposite direction $\left( \alpha_3 = -0.5\pi \right)$.
-The coefficient $\beta$, for all the vortices, is set to $\frac{1}{\pi}$.
-The considered triangular arrangement of vortices, is an effective initial condition for the representation of merging processes: in practice, mergers are often caused by fast-moving dipoles running into another vortex.
-The numerical challenge raised by this setting is the formation of thin vorticity filaments: the forces developed during the merging process drain vorticity out of the main structures into long, narrow and spiral-shaped strips of intense vorticity \cite{filaments_vort}.
-Given the absence of natural dissipation characterizing the Euler equation, the correct preservation of this delicate structures is necessary for an energy preserving, and consequently stable, reduced models.
-To have initial conditions in terms of velocity components and pressure, we define first as stream-function $\Psi$ the solution of the problem $\nabla \Psi = \omega$, and then the initial velocity is given by the curl of $\Psi$.
-To solve the stream-function problem, we need that the integral of $\omega$ is null: to satisfy this requirement we set $\omega_0 = 0.038$.
-The pressure is recovered by solving the related Poisson pressure equation.
-We use the implicit midpoint scheme as time integrator to preserve the kinetic energy of the initial condition.
-Having a skew-symmetric nonlinearity is of the essence: in Figure \ref{fig:unstable_full_models}, we show that formulations that are not skew symmetric lead to unstable solutions, characterized by a sudden change in the conserved quantity.
-The merging phenomenon is simulated for a total of $18$s using a temporal step $\Delta t=0.004$s: the same setting is adopted for simulations of reduced systems.
+close to the center of the domain, of which, two have positive spins with $\alpha_1 = \alpha_2 = \pi$ and the other rotates in the opposite direction with $\alpha_3 = -0.5\pi$.
+The effective radius of all the vortices is set to $\beta = 1 / \pi$.
+This arrangement of vortices is an effective initial condition for the process of merging vortices.
+This phenomenon is often a result of fast-moving dipoles {\commnet \{ what is a dipole?\}} facing another vortex {\commnet \{ ref \}}.
+The forces developed in the merging process transfers the vorticity from the initial configuration, into long, narrow, and spiral-shaped strips of intense vorticity \cite{filaments_vort}.
+The formation of such thin vorticity filaments in the fluid, can pose numerical challenges.
+
+In the context of MOR, conservation of energy and stability is crucial for capturing fined structures, mentioned above.
+In the absence of natural dissipation, characterizing the Euler equation, straight forward application of MOR techniques is often unstable.
+
+To define the initial conditions in terms of the velocity components $\omega$ and the pressure $p$, we define a stream-function $\Psi$, the solution to the equation 
+\begin{equation} \label{eq:5.1}
+	\nabla \Psi = \omega.
+\end{equation}
+The initial velocity is then given by $\nabla \times \Psi$.
+To solve the stream-function problem \eqref{eq:5.1}, we require $\int_{\Omega} \omega \ dx= 0$ {\commnet \{ check this \}}.
+It is easily verified that this requirement implies $\omega_0 = 0.038$.
+The pressure is recovered by solving the related Poisson pressure equation {\commnet \{ write the equation here \}}.
+The implicit midpoint scheme, to mimic the time integration scheme presented in \eqref{eq:3.27}, is considered to integrate in time.
+The merging phenomenon is simulated for a total of $18$ time units using a temporal step $\Delta t=0.004$.
+
+\Cref{fig:unstable_full_models} illustrates the evolution of the kinetic energy for the advective, divergence, and the skew-symmetric form of the high-fidelity system.
+It is observed that only the skew-symmetric form preserves the kinetic energy, confirming the results in \Cref{sec:skew.2}.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+\begin{figure}[t]
   \centering
@@
   \end{tikzpicture}
-  \caption{Evolution of the quadratic invariant $K(t)$ for the solution to Euler equation considering three different formulations (skew-symmetric, divergent and convective forms).}
+  \caption{Conservation of the kinetic energy $K$ for the advective, divergence and the skew-symmetric formulations. {\commnet \{ please change Divergent to Divergence in the legend \}} }
   \label{fig:unstable_full_models}
 \end{figure}
-Time is the only parameter considered in the reduction and $5000$ uniformly sampled snapshots are stored.
-A useful information regarding system reducibility is given by the singular value behaviour and in particular by the relative information content, reported in Figure \ref{fig:RIC}.
-Taking the first $35$ POD modes allows to maintain more than $99\%$ of the energy of the high fidelity solution: this suggest that, given the stability of the reduction procedure, we should expect an accurate reduction if a similar number of basis functions is used.
-Nevertheless, also smaller sets of basis functions are considered in our simulations to study the behaviour and stability of the reduced system in underrepresented scenarios.
+A total of $5000$ temporal snapshots is used to construct a reduced basis, following the process discussed in \Cref{sec:mor}.
+The decay of the singular values, as an indication of the reducibility of the problem, is presented in \Cref{fig:RIC}.
+The first $35$ POD modes corresponds to over $99\%$ of the {\commnet \{ kinetic?
+\}} energy of the high fidelity solution.
+This suggests that an accurate reduced system can be constructed using a small number of basis vectors.
+To illustrate the effectiveness of the method, smaller bases are also considered.
+
+For a qualitative analysis, in Figure \ref{fig:snap_solution_incompressible_Euler}, four snapshots at different time frames are shown for the high fidelity system and reduced system with $k=17$ and $k=35$ modes.
+It is seen that the overall dynamics of the problem, and in particular the formation and development of vorticity filaments, are correctly represented, even with a moderate number of basis vectors.
+Although small details are not captured by the reduced system with a small number of basis vectors, the position and the spreading of the vortices are comparable.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%% Snapshots of merging process %%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[t]
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_2.png}\hspace{1em}
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_2.png}\hspace{1em}
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_2.png}\\
+
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_3.png}\hspace{1em}
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_3.png}\hspace{1em}
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_3.png}\\
+
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_4.png}\hspace{1em}
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_4.png}\hspace{1em}
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_4.png}\\
+
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_5.png}\hspace{1em}
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_5.png}\hspace{1em}
+\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_5.png}
+
+\caption{Snapshots of the high-fidelity system and the reduced system at $t=\left\{ 4,8,12,18 \right\}$.
+From left to right: the snapshots of the reduced model with $k=17$, $k=35$ and the high fidelity solution.}
+\label{fig:snap_solution_incompressible_Euler}
+\end{figure}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+\begin{figure}[t]
 \centering
@@
 \end{tikzpicture}
-\caption{Singular values decay of the snapshot matrix related to POD algorithms for the velocity components of the solution to the incompressible Euler problem.}
+\caption{The decay of the singular values for the merging vortices problem. {\commnet \{please put this figure and figure 1 into a single figure (Left and right to each other)\} } }
 \label{fig:RIC}
 \end{figure}
-In Figure \ref{fig:approx_error_incompressible_Euler} we show that the error with respect to the high fidelity solution can be reduced, as expected, by increasing the number of basis and an arbitrary accuracy can be achieved at the cost of dealing with a more computationally expensive problem to be solved.
+\Cref{fig:approx_error_incompressible_Euler} shows the 2-norm error between the high-fidelity solution and the approximated solution.
+It is seen that the error decreases, consistently, as the number of basis vectors increase.
+Furthermore, the accuracy is maintained over the period of time integration.
 
-In Figure \ref{fig:energy_error_incompressible_Euler} we compare the quadratic invariant related to the high fidelity solution with the solution to the reduced models.
-As proved in section \ref{sec:skew.2}, the energy is preserved through the entire simulation for reduced models and it converges to the correct value as we enrich the approximating solution space.
+The conservation of the kinetic energy is presented in \Cref{fig:energy_error_incompressible_Euler}.
+It is seen that even for a small number of basis vectors, where the solution is not well approximated, the kinetic energy is conserved.
+Furthermore, it is observed that the error in the kinetic energy, due to MOR, is constant in time.
+This helps with the robustness of the reduced system over long time-integration.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
+\begin{figure}[t]
 \centering
@@
 \label{fig:energy_approx_err}
-\caption{(\protect\subref{fig:approx_error_incompressible_Euler}) Evolution of $L_2(t)$ error between the high fidelity and the reduced velocity for the Euler incompressible problem, with $k$ being the number of basis considered.
-(\protect\subref{fig:energy_error_incompressible_Euler}) Conservation of the kinetic energy for the solutions of the reduced problem for different values of $k$.}
-\end{figure}
-For a qualitative analysis, in Figure \ref{fig:snap_solution_incompressible_Euler}, four snapshots at different time frames are shown for the high fidelity solution and for different reduced solutions.
-The dynamic of the solution, in particular the formation and development of vorticity filaments, is correctly represented even with a moderate number of basis functions.
-With fewer bases, even though small details are not captured by the POD models, the positions and spreadings of the vorticity masses match.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%% Snapshots of merging process %%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[h!]
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_2.png}\hspace{1em}
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_2.png}\hspace{1em}
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_2.png}\\
-
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_3.png}\hspace{1em}
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_3.png}\hspace{1em}
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_3.png}\\
-
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_4.png}\hspace{1em}
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_4.png}\hspace{1em}
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_4.png}\\
-
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_5.png}\hspace{1em}
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_5.png}\hspace{1em}
-\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_5.png}
-
-\caption{Solutions of the three-vortices merging problem at $t=\left\{ 4,8,12,18 \right\}$.
-From left to right we have the solution of the reduced model with $k=17$, $k=35$ and the high fidelity solution.}
-\label{fig:snap_solution_incompressible_Euler}
+\caption{(\protect\subref{fig:approx_error_incompressible_Euler}) Evolution of 2-norm error in velocity, between the high-fidelity system and the reduced system.
+(\protect\subref{fig:energy_error_incompressible_Euler}) Conservation of the kinetic energy.
+{\commnet \{ in fig a $y$ axis: $\| u - \tilde u \|_2$ \} \{ in fig b $|k - \tilde K|$ \}}  }
 \end{figure}
@@
 \subsubsection{2D Kelvin-Helmholtz instability}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[xlabel=$t$,
-                 ylabel=$e(t)$,
-                 label style={font=\large},
-                 legend pos=outer north east,
-                 legend style={font=\large},
-                 legend entries={$k=200$,$k=300$,$k=400$,$k=500$,$k=600$},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 cycle list name=exotic]
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_200.txt};  
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_300.txt};      
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_400.txt}; 
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_500.txt};      
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_600.txt};               
-    \end{semilogyaxis}%  
-  \end{tikzpicture}
-\end{subfigure}
-\caption{Evolution in time of the error  between the high fidelity solution of the Kelvin-Helmoltz and the reduced solution for different number of basis $k$.
-As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
-\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%% Singular values KH problem %%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
     \begin{semilogyaxis}[xlabel=$t$,
-                 ylabel=$e(t)$,
+                 ylabel=$e(t)$
                  label style={font=\large},
@@
 \caption{Evolution in time of the error  between the high fidelity solution of the 1D compressible Euler and the reduced solution for different number of basis $k$.
-As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2+\|\mathbf{p}-\mathbf{p}^r\|^2}$.}
+As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2\|\mathbf{p}-\mathbf{p}^r\|^2}$}.
 \end{figure}

### 2018-07-12 sections/5.res.tex

@@
 \subsubsection{2D Kelvin-Helmholtz instability}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%% Singular values KH problem %%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[xlabel=$t$,
+                 ylabel=$e(t)$,
+                 label style={font=\large},
+                 legend pos=outer north east,
+                 legend style={font=\large},
+                 legend entries={$k=200$,$k=300$,$k=400$,$k=500$,$k=600$},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 cycle list name=exotic]
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_200.txt};  
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_300.txt};      
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_400.txt}; 
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_500.txt};      
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_600.txt};               
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+\end{subfigure}
+\caption{Evolution in time of the error  between the high fidelity solution of the Kelvin-Helmoltz and the reduced solution for different number of basis $k$.
+As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[ylabel = $\left|\mathbf{1}^T(\mathbf{r}-\mathbf{r}^r)(t)\right|$,
+                 xlabel=$t$,
+                 label style={font=\large},
+                 legend pos=north east,
+                 legend entries={$k=200$ ,$k=300$, $k=400$,$k=500$,$k=600$},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 cycle list name=exotic]
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_200.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_300.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_400.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_500.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_600.txt};
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+  \caption{}
+  \label{mass_error_KH}
+  \end{subfigure}\hfill
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[ylabel = $\left|(\mathbf{r}^{T}\mathbf{u}-\mathbf{r}^{rT}\mathbf{u}^{r})(t)\right|$,
+                 xlabel=$t$,
+                 label style={font=\large},
+                 legend pos=north east,
+%                 legend entries={$k=200$ Conv,$k=201$ Conv},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 cycle list name=exotic]
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_200.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_300.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_400.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_500.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_600.txt};
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+  \caption{}
+  \label{momentum_error_KH}
+  \end{subfigure}
+
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[ylabel = $\left| \dfrac{1}{2}\left( \mathbf{u}^{rT}\mathbf{R}^r\mathbf{u}^r-\mathbf{u}^{T}\mathbf{R}\mathbf{u}\right)\right|$,
+                 xlabel=$t$,
+                 label style={font=\large},
+                 legend pos=north east,
+%                 legend entries={$k=200$ Conv,$k=201$ Conv},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 cycle list name=exotic]
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_200.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_300.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_400.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_500.txt};
+                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_600.txt};
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+   \caption{}
+  \label{energy_error_KH}
+  \end{subfigure}
+\caption{Comparison between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%% Snapshots of KH %%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}[h!]
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_307.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_307.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_307.png}\\
+
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_461.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_461.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_461.png}\\
+
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_614.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_614.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_614.png}\\
+
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_768.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_768.png}\hspace{1em}
+\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_768.png}
+
+\caption{Solutions of the Kelvin-Helmholtz problem at $t=\left\{ 0.4, 0.6, 0.8, 1 \right\}$.
+From left to right we have the solution of the reduced model with $k=200$, $k=500$ and the high fidelity solution.}
+\label{fig:snap_solution_incompressible_Euler}
+\end{figure}
 

### 2018-07-13 sections/5.res.tex
Upload corrections of Incompressible results

@@
 To capture the fine details characterizing the solution, $256\times 256$ modes have been adopted.
-The initial condition is given in terms of the vorticity distribution $\mathbf{\omega} = \nabla \times u$ {\commnet \{ check this \}}.
+The initial condition is given in terms of the vorticity distribution $\mathbf{\omega} = \nabla \times u$.
 
@@
 This arrangement of vortices is an effective initial condition for the process of merging vortices.
-This phenomenon is often a result of fast-moving dipoles {\commnet \{ what is a dipole?\}} facing another vortex {\commnet \{ ref \}}.
+This phenomenon is often a result of fast-moving dipoles of vortices with the same spin facing another vortex \cite{filaments_vort2} of opposite spin.
 The forces developed in the merging process transfers the vorticity from the initial configuration, into long, narrow, and spiral-shaped strips of intense vorticity \cite{filaments_vort}.
@@
 The initial velocity is then given by $\nabla \times \Psi$.
-To solve the stream-function problem \eqref{eq:5.1}, we require $\int_{\Omega} \omega \ dx= 0$ {\commnet \{ check this \}}.
+To solve the stream-function problem \eqref{eq:5.1}, we require $\int_{\Omega} \omega \ dx= 0$.
 It is easily verified that this requirement implies $\omega_0 = 0.038$.
-The pressure is recovered by solving the related Poisson pressure equation {\commnet \{ write the equation here \}}.
+The pressure is recovered by solving the related Poisson pressure equation
+\begin{equation*}
+\Delta p = - \nabla \cdot S_{u}(u),
+\end{equation*}
+obtained by applying the divergence operator to \eqref{eq:3.8} and using the incompressibility condition.
  The implicit midpoint scheme, to mimic the time integration scheme presented in \eqref{eq:3.27}, is considered to integrate in time.
@@
 
-\Cref{fig:unstable_full_models} illustrates the evolution of the kinetic energy for the advective, divergence, and the skew-symmetric form of the high-fidelity system.
+\Cref{compare_different_models} illustrates the evolution of the kinetic energy for the advective, divergence, and the skew-symmetric form of the high-fidelity system.
 It is observed that only the skew-symmetric form preserves the kinetic energy, confirming the results in \Cref{sec:skew.2}.
@@
   \centering
-  \begin{tikzpicture}[scale=0.5452]
+  \begin{subfigure}[]{0.47\linewidth}
+  \begin{tikzpicture}[scale=0.58]
     \begin{axis}[ylabel=$E_K(t)$,
@@
                  legend pos=south west,
-                 legend entries={Skew Symmetric form, Divergent form, Advective form},
-                 legend style={font=\large},
-                 width=0.7\linewidth, 
-                 height=0.5\linewidth,
+                 legend entries={Skew Symmetric form, Divergence form, Advective form},
+                 legend style={font=\large},
+                 width=1.4\linewidth, 
+                 height=1\linewidth,
                  minor x tick num=1,
@@
   \end{tikzpicture}
-  \caption{Conservation of the kinetic energy $K$ for the advective, divergence and the skew-symmetric formulations. {\commnet \{ please change Divergent to Divergence in the legend \}} }
+\caption{}
+\label{compare_different_models}
+\end{subfigure}
+  \begin{subfigure}[]{0.47\linewidth}
+\begin{tikzpicture}[scale=0.58]
+    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
+                 xlabel=Basis POD,
+                 label style={font=\large},
+                 %legend pos=north east,
+                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 ymin=0,
+                 ymax = 2,
+                 samples = 100]
+                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = s] {./data/Incompressible_Euler/Singular_values/sv.txt};
+    \end{semilogyaxis}
+\end{tikzpicture}
+\caption{}
+\label{singular_values_decay}
+\end{subfigure}
+  \caption{(\protect\subref{compare_different_models}) Conservation of the kinetic energy $K$ for the advective, divergence and the skew-symmetric formulations.
+(\protect\subref{singular_values_decay}) The decay of the singular values for the merging vortices problem.
+}
   \label{fig:unstable_full_models}
@@
 A total of $5000$ temporal snapshots is used to construct a reduced basis, following the process discussed in \Cref{sec:mor}.
-The decay of the singular values, as an indication of the reducibility of the problem, is presented in \Cref{fig:RIC}.
-The first $35$ POD modes corresponds to over $99\%$ of the {\commnet \{ kinetic?
-\}} energy of the high fidelity solution.
+The decay of the singular values, as an indication of the reducibility of the problem, is presented in \Cref{singular_values_decay}.
+The first $35$ POD modes corresponds to over $99\%$ of the modes energy of the high fidelity solution.
 This suggests that an accurate reduced system can be constructed using a small number of basis vectors.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}[t]
-\centering
-\begin{tikzpicture}[scale=0.5452]
-    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
-                 xlabel=Basis ,
-                 label style={font=\large},
-                 %legend pos=north east,
-                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=0.7\linewidth, 
-                 height=0.5\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=0,
-                 ymax = 2,
-                 samples = 100]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = s] {./data/Incompressible_Euler/Singular_values/sv.txt};
-    \end{semilogyaxis}
-\end{tikzpicture}
-\caption{The decay of the singular values for the merging vortices problem. {\commnet \{please put this figure and figure 1 into a single figure (Left and right to each other)\} } }
-\label{fig:RIC}
-\end{figure}
 \Cref{fig:approx_error_incompressible_Euler} shows the 2-norm error between the high-fidelity solution and the approximated solution.
@@
 \begin{tikzpicture}[scale=0.58]
-    \begin{semilogyaxis}[ylabel = $\left | \mathbf{v}(t)-\mathbf{v}^r(t) \right |^2$,
+    \begin{semilogyaxis}[ylabel = $\| \mathbf{u}-\tilde{\mathbf{u}}\|_2$,
                  xlabel=$t$,
@@
 \begin{tikzpicture}[scale=0.58]
-    \begin{axis}[ylabel = $|K(t)-K_r^{r}(t)|$,
+    \begin{axis}[ylabel = $|K-\tilde{K}|$,
                  xlabel=$t$,
@@
 \caption{(\protect\subref{fig:approx_error_incompressible_Euler}) Evolution of 2-norm error in velocity, between the high-fidelity system and the reduced system.
-(\protect\subref{fig:energy_error_incompressible_Euler}) Conservation of the kinetic energy.
-{\commnet \{ in fig a $y$ axis: $\| u - \tilde u \|_2$ \} \{ in fig b $|k - \tilde K|$ \}}  }
+(\protect\subref{fig:energy_error_incompressible_Euler}) Conservation of the kinetic energy.}
 \end{figure}

### 2018-07-13 sections/5.res.tex
Start comments Kelvin Helmholtz

@@
 \subsubsection{2D Kelvin-Helmholtz instability}
+Consider the 2D case of the compressible Euler equations \eqref{eq:3.18} ... .
+In this test case we consider the flows of different layers of an heterogenous fluid in relative horizontal motion.
+If the heterogeneity considered consists in a stratification of different density layers, the fluid develops, at the interface between two separated layers, an hydrodynamic instability called Kelvin-Helmholtz instability \cite{HHS}.
+As a result of  the different tangential velocities,  Given the considered geometrical setting and the absence of external forces, this phenomenon is induced only by the initial condition.
+In our test cases we consider three different layers,
+\begin{equation*}
+dasdasd
+\end{equation*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2018-07-13 sections/5.res.tex
tex file for CVRC is now separated

--- 2018-07-12 sections/5.res.tex
@@
 \end{figure}
-
-\subsection{Continuous Variable Resonance Combustor}
-
-CVRC is a model rocket combustor designed and operated at Purdue University (Indiana, U.S.) to investigate combustion instabilities \cite{yu2008combustion}.
-This setup is called the Continuously Variable Resonance Combustor (CVRC) because the length of the oxidizer injector can be varied continuously, allowing for a detailed investigation of the coupling between acoustics and combustion in the chamber \cite{garby2013simulations}.
-The 2D/3D high-fidelity simulations of CVRC are expensive.
-Thus to get a fast analysis tool, a quasi-1D model has been proposed by Smith et al.
-\cite{smith2008computational} and further developed by Frezzotti et al.
-\cite{frezzotti2015determination,frezzotti2017numerical,frezzotti2018quasi}.
-
-The CVRC consists of three parts: oxidizer post, combustion chamber and exit nozzle, as shown in Fig.
-\ref{fig:radius}.
-The oxidizer is injected from the left end of the oxidizer post and meets the fuel that is injected through an annular ring around the oxidizer injector, at the back-step.
-The combustion happens in a region around the back-step.
-The combustion products flow through the chamber and exit the system from the nozzle.
-Both the injector and the nozzle are operated at choked condition during the experiment.
-The length of the oxidizer post $L_{op}$ of the CVRC can be varied continuously, leading to different behavior of the combustion stability.
-In this paper, we will focus on the case with $L_{op}= 14.0$ cm, in which the combustion is unstable.
-
-The geometry parameters of the quasi-1D CVRC with a oxidizer post length  $L_{op}= 14.0$ cm are shown in Table \ref{tab:geometry_parameters}.
-The back-step and the converging part of the nozzle are sinusoidally contoured to avoid discontinuity of the radius that will invalidate the quasi-1D governing equations presented in the next subsection.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.8\linewidth]{pic/radius}
-	\caption{Geometry of quasi-1D CVRC model.}
-	\label{fig:radius}
-\end{figure}
-
-\begin{table} [h]
-	\centering
-	\caption{Geometry parameters of the quasi-1D CVRC with an oxidizer post length $L_{op}=14$ cm.}
-	\centering
-	\begin{tabular}{c c c c c c }
-		\toprule
-		\centering
-		\multirow{2}{*}{Section} &
-		\multicolumn{2}{c}{Oxidizer post} &
-		\multirow{2}{*}{Chamber} &
-		\multicolumn{2}{c}{Nozzle} \\
-		\cmidrule(lr){2-3} \cmidrule(lr){5-6}
-		& injector & back-step & & converging part & diverging part\\
-		\midrule
-		Length (cm) & 12.99 & 1.01 & 38.1 & 1.27 & 3.4 \\
-		Radius (cm) & 1.02  & $1.02 \sim 2.25$ & 2.25 & $2.25 \sim 1.04$ & $1.04 \sim 1.95$ \\
-		\bottomrule
-		\label{tab:geometry_parameters}
-	\end{tabular} 
-\end{table}
-
-The fuel is pure gaseous methane.
-The oxidizer is a mixture of 42\% oxygen and 58\% water (per unit mass).
-The oxidizer is injected in the oxidizer post at a temperature $T_{ox}=1030$ K so that both water and oxygen are in the gaseous phase.
-The operating conditions are listed in Table \ref{tab:operating-conditions}.
-
-\begin{table} [h]
-	\centering
-	\caption{CVRC operating conditions.}
-	\centering
-	\begin{tabular}{l l l}
-		\toprule
-		\centering
-		Parameter & Unit & Value \\
-		\midrule
-		Fuel mass flow rate, $\dot{m}_{f}$ & kg/s & 0.027   \\
-		Fuel temperature, $T_{f}$ & K & 300   \\
-		Oxidizer mass flow rate, $\dot{m}_{ox}$ & kg/s & 0.32   \\
-		Oxidizer temperature, $T_{ox}$ & K & 1030   \\
-		$O_2$ mass fraction in oxidizer, $Y_{O_2}$ & -- & 42.4\%   \\
-		$H_2O$ mass fraction in oxidizer, $Y_{H_2O}$ & -- & 57.6\%   \\
-		Mean chamber pressure & MPa & 1.34 \\
-		Equivalence ratio, $E_r$ & -- & 0.8 \\
-		\bottomrule
-		\label{tab:operating-conditions}
-	\end{tabular} 
-\end{table}
-
-For the combustion, we consider the one-step reaction model
-\begin{equation*}\label{eq:combustion}
-CH_4 + 2O_2 \rightarrow CO_2 + 2H_2O
-\end{equation*}
-We assume that the fuel reacts instantaneously to form products, allowing us to neglect intermediate species and finite reaction rates.
-As the equivalence ratio is less than one, there is oxidizer left after the combustion.
-Therefore, only two species need to be considered: oxidizer and combustion products.
-
-The governing equations that describe the conservation of mass, momentum, and energy of the quasi-1D CVRC flow, are the quasi-1D unsteady Euler equations for multiple species, expressed in conservative form as
-\begin{equation*}\label{eq:quasi-1D-equation}
-\frac{\partial \mathbf{u}}{\partial t} + \frac{\partial \mathbf{f}}{\partial x} = \mathbf{s}_A + \mathbf{s}_f + \mathbf{s}_q.
-\end{equation*}
-The conserved variable vector $\mathbf{u}$ and the convective flux vector $\mathbf{f}$ are
-\begin{equation*}\label{eq:CVRC-u-f}
-\mathbf{u}= \left( \begin{gathered}
-\rho A  \\
-\rho uA  \\
-\rho EA  \\
-\rho Y_{ox} A \\
-\end{gathered} \right), 
-\mathbf{f} = \left( \begin{gathered}
-\rho uA  \\
-\left(\rho u^2 + p\right)A  \\
-\left(\rho E + p\right)uA  \\
-\rho uY_{ox} A \\
-\end{gathered} \right),
-\end{equation*}
-where $\rho$ is the density, $u$ is the velocity, $p$ is the pressure, $E$ is the total energy, $Y_{ox}$ is the mass fraction of oxidizer, and $A=A(x)$ is the cross section area of the duct.
-The pressure $p$ can be computed using the conserved variables as
-\begin{equation*}\label{eq:total-engery}
-E = \frac{p}{\rho (\gamma - 1)} + \frac{u^2}{2} - C_p T_{ref},
-\end{equation*}
-where $T_{ref}$ is the reference temperature and is set as 298.15 K in this paper.
-The temperature $T$ is recovered from the equation of state $p = \rho R T$.
-The gas properties  $C_p$, $R$ and $\gamma$ are computed as $C_p= \sum C_{pi}Y_i$, $R=\sum R_iY_i$ and $ \gamma= C_p/(C_p-R)$, respectively.
-
-The source terms are
-\begin{equation*}\label{eq:source-terms}
-\mathbf{s}_A = \left( \begin{gathered}
-0  \\
-p \frac{dA}{dx}  \\
-0  \\
-0 \\
-\end{gathered} \right), 
-\mathbf{s}_f = \left( \begin{gathered}
-{\dot \omega}_f  \\
-{\dot \omega}_f u  \\
-{\dot \omega}_f \left(h_{0}^{f} + \Delta h_{0}^{rel} \right)  \\
-{\dot \omega}_{ox} \\
-\end{gathered} \right), 
-{\mathbf{s}_q} = \left( \begin{gathered}
-0  \\
-0  \\
-q'  \\
-0 \\
-\end{gathered} \right),
-\end{equation*}
-where $\dot{\omega}_f$ is the depletion rate of the fuel, $\dot{\omega}_{ox}$ is the depletion rate of the oxidizer, $h_0^f$ is the total enthalpy of the fuel, $\Delta h_{0}^{rel}$ is the heat of reaction per unit mass of fuel and $q'$ is the unsteady heat release term.
-$\mathbf{s}_A$ accounts for area variations, $\mathbf{s}_f$ and $\mathbf{s}_q$ are related to the combustion.
-$\mathbf{s}_f$ represents the addition of the fuel and its combustion with the oxidizer, which in turn results in the creation of the combustion products.
-The depletion rate of the fuel is
-\begin{equation}\label{eq:wf}
-\dot{\omega}_{f}= \frac{k_f \dot{m}_f Y_{ox} \left(1+sin\xi\right)}{l_f-l_s},
-\end{equation} 
-where
-\begin{equation*}\label{eq:xi}
-\xi= -\frac{\pi}{2} + 2\pi\frac{x-l_s}{l_f-l_s}, \hspace{0.5cm} \forall \hspace{0.2cm} l_s < x < l_f.
-\end{equation*}
-The setting of the fuel injection restricts the combustion to the region $l_s < x < l_f$.
-The reaction constant $k_f$ is selected to insure that the fuel is consumed within the specified combustion zone.
-The depletion rate of the oxidizer is computed by
-\begin{equation*}\label{eq:wox}
-\dot{\omega}_{ox} = C_{o/f} \dot{\omega}_f,
-\end{equation*}
-where $C_{o/f}$ is the oxidizer-to-fuel ratio.
-
-The unsteady heat release term $q'$, also called the combustion response function, models the coupling between acoustics and combustion.
-In this paper, we use the combustion response function designed by Frezzotti et al.
-\cite{frezzotti2017numerical,frezzotti2018quasi}, which is a function of the velocity, sampled at specific abscissa $\hat{x}$ that is almost coincident with the antinode of the first longitudinal modal shape, with a certain time lag $\tau$, i.e.,
-\begin{equation}\label{eq:response-function}
-q'\left( x,t\right) = \alpha g\left(x\right)  A\left(x\right) \left[ u\left( \hat{x},t-\tau \right) - \bar{u}\left( \hat{x} \right) \right].
-\end{equation}
-Here $\bar{u}$ is the time averaged velocity, estimated with the steady-state quasi-1D model assuming $q'=0$, and $g(x)$ is a Gaussian distribution  
-\begin{equation*}\label{eq:gx}
-g\left(x\right)= \frac{e^{-\frac{\left(x-\mu\right)^2}{2\sigma^2}}}{\sqrt{2\pi\sigma^2}},
-\end{equation*}
-where $\mu$ is the mean and $\sigma$ is the standard deviation. The amount of heat release due to velocity oscillations is controlled by the parameter $\alpha$.
-
-The boundary conditions for the quasi-1D CVRC flow include the fixed mass flow rate and the stagnation temperature at the head-end of the oxidizer injector, and the supersonic outflow at the exit of the nozzle.
-
-Prior to unsteady simulation, the quasi-1D CVRC needs to be excited, which can be achieved by adding a perturbation to the steady-state solution.
-The perturbation is added by forcing the mass flow rate with a multi-sine signal
-\begin{equation}\label{eq:multisine}
-\dot{m}_{ox} \left(t\right)= \dot{m}_{ox,0} \left[1 + \delta\sum_{k=1}^{K}  sin\left(2\pi k\Delta f t\right) \right],
-\end{equation}
-where $\dot{m}_{ox,0}$ is the oxidizer mass flow rate in Table \ref{tab:operating-conditions}, $\Delta f$ is the frequency resolution and $K$ is the number of frequencies.
-In this paper, $\Delta f = 50 $ Hz and $K=140$, resulting in a minimal frequency of 50 Hz and a maximal frequency of 7000 Hz.
-$\delta$ is required to be small to control the amplitude of the perturbation and is set as 0.1\%.
-
-The procedure of the unsteady simulation of the quasi-1D CVRC flow includes three steps:
-\begin{enumerate}[(1)]
-	\item  Compute the steady-state solution by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $ and $q'=0$.
-	\item  Excite the system by adding a perturbation to the oxidizer mass flow rate according to (\ref{eq:multisine}) and setting $q'=0$.
-	\item  Perform the unsteady simulation by turning on the combustion response function $q'$ in (\ref{eq:response-function}) and turning off the oxidizer mass flow rate perturbation by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $.
-\end{enumerate}
-
-A high-fidelity quasi-1D CVRC flow solver is built by employing the MUSCL reconstruction \cite{delis1998tvd}, the Lax-Friedrichs flux \cite{shu1988efficient} and the strong stability preserving, three-stage Runge-Kutta (SSP RK3) time stepping \cite{jiang1996efficient}.

### 2018-07-13 sections/5.res_part2.tex
the file for CVRC is added

\subsection{Continuous Variable Resonance Combustor}

CVRC is a model rocket combustor designed and operated at Purdue University (Indiana, U.S.) to investigate combustion instabilities \cite{yu2008combustion}. This setup is called the Continuously Variable Resonance Combustor (CVRC) because the length of the oxidizer injector can be varied continuously, allowing for a detailed investigation of the coupling between acoustics and combustion in the chamber \cite{garby2013simulations}. The 2D/3D high-fidelity simulations of CVRC are expensive. Thus to get a fast analysis tool, a quasi-1D model has been proposed by Smith et al. \cite{smith2008computational} and further developed by Frezzotti et al. \cite{frezzotti2015determination,frezzotti2017numerical,frezzotti2018quasi}.

The CVRC consists of three parts: oxidizer post, combustion chamber and exit nozzle, as shown in Fig. \ref{fig:radius}. The oxidizer is injected from the left end of the oxidizer post and meets the fuel that is injected through an annular ring around the oxidizer injector, at the back-step. The combustion happens in a region around the back-step. The combustion products flow through the chamber and exit the system from the nozzle.  Both the injector and the nozzle are operated at choked condition during the experiment. The length of the oxidizer post $L_{op}$ of the CVRC can be varied continuously, leading to different behavior of the combustion stability. In this paper, we will focus on the case with $L_{op}= 14.0$ cm, in which the combustion is unstable.

The geometry parameters of the quasi-1D CVRC with a oxidizer post length  $L_{op}= 14.0$ cm are shown in Table \ref{tab:geometry_parameters}.  The back-step and the converging part of the nozzle are sinusoidally contoured to avoid discontinuity of the radius that will invalidate the quasi-1D governing equations presented in the next subsection.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{pic/radius}
	\caption{Geometry of quasi-1D CVRC model.}
	\label{fig:radius}
\end{figure}

\begin{table} [h]
	\centering
	\caption{Geometry parameters of the quasi-1D CVRC with an oxidizer post length $L_{op}=14$ cm.}
	\centering
	\begin{tabular}{c c c c c c }
		\toprule
		\centering
		\multirow{2}{*}{Section} &
		\multicolumn{2}{c}{Oxidizer post} &
		\multirow{2}{*}{Chamber} &
		\multicolumn{2}{c}{Nozzle} \\
		\cmidrule(lr){2-3} \cmidrule(lr){5-6}
		& injector & back-step & & converging part & diverging part\\
		\midrule
		Length (cm) & 12.99 & 1.01 & 38.1 & 1.27 & 3.4 \\
		Radius (cm) & 1.02  & $1.02 \sim 2.25$ & 2.25 & $2.25 \sim 1.04$ & $1.04 \sim 1.95$ \\
		\bottomrule
		\label{tab:geometry_parameters}
	\end{tabular} 
\end{table}

The fuel is pure gaseous methane. The oxidizer is a mixture of 42\% oxygen and 58\% water (per unit mass). The oxidizer is injected in the oxidizer post at a temperature $T_{ox}=1030$ K so that both water and oxygen are in the gaseous phase. The operating conditions are listed in Table \ref{tab:operating-conditions}.

\begin{table} [h]
	\centering
	\caption{CVRC operating conditions.}
	\centering
	\begin{tabular}{l l l}
		\toprule
		\centering
		Parameter & Unit & Value \\
		\midrule
		Fuel mass flow rate, $\dot{m}_{f}$ & kg/s & 0.027   \\
		Fuel temperature, $T_{f}$ & K & 300   \\
		Oxidizer mass flow rate, $\dot{m}_{ox}$ & kg/s & 0.32   \\
		Oxidizer temperature, $T_{ox}$ & K & 1030   \\
		$O_2$ mass fraction in oxidizer, $Y_{O_2}$ & -- & 42.4\%   \\
		$H_2O$ mass fraction in oxidizer, $Y_{H_2O}$ & -- & 57.6\%   \\
		Mean chamber pressure & MPa & 1.34 \\
		Equivalence ratio, $E_r$ & -- & 0.8 \\
		\bottomrule
		\label{tab:operating-conditions}
	\end{tabular} 
\end{table}

For the combustion, we consider the one-step reaction model
\begin{equation*}\label{eq:combustion}
CH_4 + 2O_2 \rightarrow CO_2 + 2H_2O
\end{equation*}
We assume that the fuel reacts instantaneously to form products, allowing us to neglect intermediate species and finite reaction rates. As the equivalence ratio is less than one, there is oxidizer left after the combustion. Therefore, only two species need to be considered: oxidizer and combustion products.

The governing equations that describe the conservation of mass, momentum, and energy of the quasi-1D CVRC flow, are the quasi-1D unsteady Euler equations for multiple species, expressed in conservative form as
\begin{equation*}\label{eq:quasi-1D-equation}
\frac{\partial \mathbf{u}}{\partial t} + \frac{\partial \mathbf{f}}{\partial x} = \mathbf{s}_A + \mathbf{s}_f + \mathbf{s}_q.
\end{equation*}
The conserved variable vector $\mathbf{u}$ and the convective flux vector $\mathbf{f}$ are
\begin{equation*}\label{eq:CVRC-u-f}
\mathbf{u}= \left( \begin{gathered}
\rho A  \\
\rho uA  \\
\rho EA  \\
\rho Y_{ox} A \\
\end{gathered} \right), 
\mathbf{f} = \left( \begin{gathered}
\rho uA  \\
\left(\rho u^2 + p\right)A  \\
\left(\rho E + p\right)uA  \\
\rho uY_{ox} A \\
\end{gathered} \right),
\end{equation*}
where $\rho$ is the density, $u$ is the velocity, $p$ is the pressure, $E$ is the total energy, $Y_{ox}$ is the mass fraction of oxidizer, and $A=A(x)$ is the cross section area of the duct. The pressure $p$ can be computed using the conserved variables as
\begin{equation*}\label{eq:total-engery}
E = \frac{p}{\rho (\gamma - 1)} + \frac{u^2}{2} - C_p T_{ref},
\end{equation*}
where $T_{ref}$ is the reference temperature and is set as 298.15 K in this paper. The temperature $T$ is recovered from the equation of state $p = \rho R T$. The gas properties  $C_p$, $R$ and $\gamma$ are computed as $C_p= \sum C_{pi}Y_i$, $R=\sum R_iY_i$ and $ \gamma= C_p/(C_p-R)$, respectively.

The source terms are
\begin{equation*}\label{eq:source-terms}
\mathbf{s}_A = \left( \begin{gathered}
0  \\
p \frac{dA}{dx}  \\
0  \\
0 \\
\end{gathered} \right), 
\mathbf{s}_f = \left( \begin{gathered}
{\dot \omega}_f  \\
{\dot \omega}_f u  \\
{\dot \omega}_f \left(h_{0}^{f} + \Delta h_{0}^{rel} \right)  \\
{\dot \omega}_{ox} \\
\end{gathered} \right), 
{\mathbf{s}_q} = \left( \begin{gathered}
0  \\
0  \\
q'  \\
0 \\
\end{gathered} \right),
\end{equation*}
where $\dot{\omega}_f$ is the depletion rate of the fuel, $\dot{\omega}_{ox}$ is the depletion rate of the oxidizer, $h_0^f$ is the total enthalpy of the fuel, $\Delta h_{0}^{rel}$ is the heat of reaction per unit mass of fuel and $q'$ is the unsteady heat release term. $\mathbf{s}_A$ accounts for area variations, $\mathbf{s}_f$ and $\mathbf{s}_q$ are related to the combustion. $\mathbf{s}_f$ represents the addition of the fuel and its combustion with the oxidizer, which in turn results in the creation of the combustion products. The depletion rate of the fuel is
\begin{equation}\label{eq:wf}
\dot{\omega}_{f}= \frac{k_f \dot{m}_f Y_{ox} \left(1+sin\xi\right)}{l_f-l_s},
\end{equation} 
where
\begin{equation*}\label{eq:xi}
\xi= -\frac{\pi}{2} + 2\pi\frac{x-l_s}{l_f-l_s}, \hspace{0.5cm} \forall \hspace{0.2cm} l_s < x < l_f.
\end{equation*}
The setting of the fuel injection restricts the combustion to the region $l_s < x < l_f$. The reaction constant $k_f$ is selected to insure that the fuel is consumed within the specified combustion zone. The depletion rate of the oxidizer is computed by 
\begin{equation*}\label{eq:wox}
\dot{\omega}_{ox} = C_{o/f} \dot{\omega}_f,
\end{equation*}
where $C_{o/f}$ is the oxidizer-to-fuel ratio.

The unsteady heat release term $q'$, also called the combustion response function, models the coupling between acoustics and combustion. In this paper, we use the combustion response function designed by Frezzotti et al. \cite{frezzotti2017numerical,frezzotti2018quasi}, which is a function of the velocity, sampled at specific abscissa $\hat{x}$ that is almost coincident with the antinode of the first longitudinal modal shape, with a certain time lag $\tau$, i.e.,
\begin{equation}\label{eq:response-function}
q'\left( x,t\right) = \alpha g\left(x\right)  A\left(x\right) \left[ u\left( \hat{x},t-\tau \right) - \bar{u}\left( \hat{x} \right) \right].
\end{equation}
Here $\bar{u}$ is the time averaged velocity, estimated with the steady-state quasi-1D model assuming $q'=0$, and $g(x)$ is a Gaussian distribution  
\begin{equation*}\label{eq:gx}
g\left(x\right)= \frac{e^{-\frac{\left(x-\mu\right)^2}{2\sigma^2}}}{\sqrt{2\pi\sigma^2}},
\end{equation*}
where $\mu$ is the mean and $\sigma$ is the standard deviation. The amount of heat release due to velocity oscillations is controlled by the parameter $\alpha$.

The boundary conditions for the quasi-1D CVRC flow include the fixed mass flow rate and the stagnation temperature at the head-end of the oxidizer injector, and the supersonic outflow at the exit of the nozzle.

Prior to unsteady simulation, the quasi-1D CVRC needs to be excited, which can be achieved by adding a perturbation to the steady-state solution. The perturbation is added by forcing the mass flow rate with a multi-sine signal
\begin{equation}\label{eq:multisine}
\dot{m}_{ox} \left(t\right)= \dot{m}_{ox,0} \left[1 + \delta\sum_{k=1}^{K}  sin\left(2\pi k\Delta f t\right) \right],
\end{equation}
where $\dot{m}_{ox,0}$ is the oxidizer mass flow rate in Table \ref{tab:operating-conditions}, $\Delta f$ is the frequency resolution and $K$ is the number of frequencies. In this paper, $\Delta f = 50 $ Hz and $K=140$, resulting in a minimal frequency of 50 Hz and a maximal frequency of 7000 Hz. $\delta$ is required to be small to control the amplitude of the perturbation and is set as 0.1\%.

The procedure of the unsteady simulation of the quasi-1D CVRC flow includes three steps:
\begin{enumerate}[(1)]
	\item  Compute the steady-state solution by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $ and $q'=0$.
	\item  Excite the system by adding a perturbation to the oxidizer mass flow rate according to (\ref{eq:multisine}) and setting $q'=0$.
	\item  Perform the unsteady simulation by turning on the combustion response function $q'$ in (\ref{eq:response-function}) and turning off the oxidizer mass flow rate perturbation by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $.	
\end{enumerate}

A high-fidelity quasi-1D CVRC flow solver is built by employing the MUSCL reconstruction \cite{delis1998tvd}, the Lax-Friedrichs flux \cite{shu1988efficient} and the strong stability preserving, three-stage Runge-Kutta (SSP RK3) time stepping \cite{jiang1996efficient}.

Note that the right hand side in \eqref{?} suggests that, in general, mass, momentum, and energy is not conserved. Furthermore, the complex coupling of the variables in \eqref{?} prohibits the application of complex and implicit time integration schemes. Therefore, a quasi-skew-symmetric form, introduced in \eqref{eq:3.7}, is considered for \eqref{?}. This allows us to benefit from stability properties of skew-symmetric forms while using an explicit time integration scheme.

Introduction of an artificial viscosity is essential for a robust and long time-integration of \eqref{?}. Common discretization schemes for \eqref{?} are often dissipative, e.g. the Lax-Friedrich scheme used in \cite{Wang:255719}. Since the skew-symmetric discretization is non-dissipative, we modify \eqref{} to write
\begin{equation} \label{}
	\frac{\partial }{\partial t} v + \frac{\partial }{\partial x} F = s_A + s_f + s_q + d, \quad d = (0,\frac{\partial }{\partial x} \tau,0,0)^T,
\end{equation}
with $\tau = \mu \partial (u A)/ \partial x$, and $\mu = 6\times 10^{-5}$. The three-stage Runge-Kutta (SSP RK3) is used to then integrate

### 2018-07-13 sections/5.res.tex

@@
                  legend pos=south west,
-                 legend entries={Skew Symmetric form, Divergent form, Advective form},
+                 legend entries={Skew Symmetric form, Divergence form, Advective form},
                  legend style={font=\large},
-                 width=0.7\linewidth, 
-                 height=0.5\linewidth,
+                 width=1.4\linewidth, 
+                 height=1\linewidth,
                  minor x tick num=1,

### 2018-07-13 sections/5.res.tex
Update comments on KH example

@@
 \subsubsection{2D Kelvin-Helmholtz instability}
-Consider the 2D case of the compressible Euler equations \eqref{eq:3.18} ... .
-In this test case we consider the flows of different layers of an heterogenous fluid in relative horizontal motion.
+Consider the 2D case of the compressible Euler equations \eqref{eq:3.18} in the periodic square box $[0,1]^2$.
+Spatial derivatives, differently from the incompressible example, are numerically approximated by means of a centered finite difference scheme of fourth order, using 256 nodes per side.
+
+In this test case we consider the flows of different layers of an heterogenous fluid in relative vertical motion.
 If the heterogeneity considered consists in a stratification of different density layers, the fluid develops, at the interface between two separated layers, an hydrodynamic instability called Kelvin-Helmholtz instability \cite{HHS}.
-As a result of  the different tangential velocities,  Given the considered geometrical setting and the absence of external forces, this phenomenon is induced only by the initial condition.
+Given the considered geometrical setting and the absence of external forces, this phenomenon is induced only by the initial condition.
 In our test cases we consider three different layers,
 \begin{equation*}
-dasdasd
+\begin{cases}
+& \mathbf{r} = 
+\begin{cases}
+& 2, \text{ if } 0.25<y<0.75,\\
+& 1, \text{ otherwise },
+\end{cases}
+\\
+& \mathbf{u}_x = a \sin(4\pi y) \left( e^{-\dfrac{(y-0.25)^2}{2\sigma^2}} + e^{-\dfrac{(y-0.75)^2}{2\sigma^2}} \right)\\
+& \mathbf{u}_y = 
+\begin{cases}
+& 0.5, \text{ if } 0.25<y<0.75,\\
+& -0.5, \text{ otherwise },
+\end{cases}
+\\
+& \mathbf{p} = 2.5\\
+\end{cases}
 \end{equation*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+with $a=0.1$ and $\sigma=5\sqrt{2}\cdot 10^{-3}$.
+The initial condition on $\mathbf{u}_x$ represents a small perturbation in the normal direction with respect to the layer interfaces at $y=0.25$ and $y=0.75$.
+From the theory, we expect the shear stress at the interfaces to induce the formation of vortices that rolls up into spirals.
+To capture these delicate structures and considering the discontinuous initial data, we introduce numerical viscosity in the original formulation of the compressible Euler equations.
+The dissipation coefficient considered is based on the derivative-based model described in \cite{artificial_dissipation} while for the reduced model we filter out the last $5\%$ of POD modes every 10 iterations.
+
+The time marching method adopted for the discretization of the time derivatives for the complete and reduced models is the scheme proposed by Morinishi \eqref{eq:3.27}.
+The final time considered is $T=1s$ with a time step $\Delta t =5 \cdot 10^{-4}$.
+
+In \Cref{fig:error_decay_KH} we show that the solution to the skew-symmetric reduced models are stable and the accuracy in the approximation of the high fidelity solution increases with the dimension of the set of basis functions considered.
+From \Cref{fig:snap_solution_KH}, where snapshots of the high fidelity and reduced solutions at different time steps are shown, we notice that even in the case considered,  the reduced solution is not easily distinguis
 \begin{figure}
@@
 As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
+\label{fig:error_decay_KH}
 \end{figure}
 
+In \Cref{fig:conservation_DEIM} 
 \begin{figure}
@@
 \caption{Comparison between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
+\label{fig:conservation_DEIM}
 \end{figure}
@@
 From left to right we have the solution of the reduced model with $k=200$, $k=500$ and the high fidelity solution.}
-\label{fig:snap_solution_incompressible_Euler}
+\label{fig:snap_solution_KH}
 \end{figure}

### 2018-07-13 sections/5.res.tex
Finish comment KH and complete comment on 1D Euler example.

@@
 In \Cref{fig:error_decay_KH} we show that the solution to the skew-symmetric reduced models are stable and the accuracy in the approximation of the high fidelity solution increases with the dimension of the set of basis functions considered.
-From \Cref{fig:snap_solution_KH}, where snapshots of the high fidelity and reduced solutions at different time steps are shown, we notice that even in the case considered,  the reduced solution is not easily distinguis
+From \Cref{fig:snap_solution_KH}, where snapshots of the high fidelity and reduced solutions at different time steps are shown, we notice that even in the less accurate case considered,  the reduced solution is not easily distinguishable from the high fidelity solution.
 \begin{figure}
@@
 
-In \Cref{fig:conservation_DEIM} 
+In \Cref{fig:conservation_DEIM}  we show that the considered invariants of the system converges to the related invariatns of the high fidelity solution.
 \begin{figure}
@@
 \subsubsection{1D Shock problem}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%% Singular values 1D problem %%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\begin{tikzpicture}[scale=0.5452]
-    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
-                 xlabel=Basis,
-                 label style={font=\large},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=0.7\linewidth, 
-                 height=0.5\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=0,
-                 ymax = 2,
-                 samples = 100]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = n, y = sing_values] {./data/Compressible_Euler/1D/Singular_values/sv.txt};
-    \end{semilogyaxis}
-\end{tikzpicture}
-\caption{Singular values decay of the snapshot matrix related to POD algorithms for the 1D compressible Euler problem.}
-\end{figure}
+One of the most challenging aspects of model order reduction of combustion problems is the development 
+and propagation of shocks in the solution, starting from the simple steady state scenario.
+Before proceeding with the reduction of  such a problem, we focus on a much simpler case to assess the capability of the skew-symmetric formulation to handle moving discontinuities in combination to the reduced basis approach.
+We consider the 1D compressible Euler equation with periodic boundaries on the domain $[0,1]$.
+The initial conditions are given by
+\begin{equation*}
+\begin{cases}
+& \mathbf{r} = 0.5+0.2 \cos(2\pi x),\\
+& \mathbf{u} = 1.5,\\
+& \mathbf{p} = 0.5+0.2 \sin(2\pi x).\\
+\end{cases}
+\end{equation*}
+The domain is discretized using $2000$ nodes and spatial derivatives are approximated using a second order centered finite differences scheme.
+We simulate $T=0.3$s of the dynamic of the system, using Morinishi time integrator.
+Artificial viscosity is added, only to the pressure equation, with a constant diffusion coefficient equals to $\mu = 0.5 \cdot 10^{-4}$.
+First we consider a comparison between different formulations of the compressible Euler equation.
+In   \Cref{fig:energy_pres_1D}, we show the behaviour of the conserved quantities mass, total momentum and total energy, for the reduced solution of the skew-symmetric, divergence and advective formulations, while in \Cref{fig:snaps_1D_Euler} we show snapshots of the solution.
+The skew-symmetric formulation is the only one preserving these invariants, while other formulations are unstable.
+Moreover we notice that for unstable formulations, the more basis functions we use, the sooner the reduced solutions blow up.
+On the contrary,  for the stable formulation, increasing the number of basis leads to a more accurate representation, as shown in \Cref{error_behaviour_1D}.
+However, the introduction of the artificial diffusion  slightly affects the conservation properties of the algorithms, as can be seen in   \Cref{conservation_1D_focus}.
 
+For this problem we estimate the effect of the DEIM procedure on the accuracy and on the conservation of invariants for the solution of the reduced problem.
+First we notice, from \Cref{fig:singular_values_decay_1D}, that the space spanned by the snapshots of nonlinearity is larger than the space spanned by the solution snapshots.
+Hence, we expect that to reach the same accuracy of standard POD with the DEIM approach, more basis will be required.
+This conclusion is numerically justified by a direct comparison of the approximation error (\Cref{error_DEIM}) and of the total energy of the system (\Cref{energy_DEIM}) at the last time step.
+The number of POD basis has been fixed to $204$ while the number of DEIM basis adopted for the simulation varies in the interval  $[204,500]$.
+Even though the interpolatory procedure have an impact on the quality of the reduction, the reduced solution remains an accurate representation of the high fidelity solution, preserving stability and the boundedness of the conserved quantities.
+By increasing the number of DEIM basis,  the error is dominated by the POD approximation error.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
                  legend pos=north east,
-                 legend entries={$k=102$ Conv,$k=201$ Conv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
+                 legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
                  legend style={font=\large},
@@
 (\protect\subref{conservation_1D_focus}) Focus on the conserved quantity in case of stable reduction using the skew-symmetric formulation.}
+  \label{fig:energy_pres_1D}
 \end{figure}
@@
 As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2+\|\mathbf{p}-\mathbf{p}^r\|^2}$.}
+\label{error_behaviour_1D}
 \end{figure}
@@
 Results for the advective formulation are not showed here because the related reduced solutions are unstable after few time steps.}
+\label{fig:snaps_1D_Euler}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%% Singular values 1D problem %%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\begin{tikzpicture}[scale=0.5452]
+    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
+                 xlabel=Basis,
+                 label style={font=\large},
+                 legend style={font=\large},
+                 legend entries = {POD,DEIM},
+                 grid=both,
+                 ticks=both,
+                 width=0.7\linewidth, 
+                 height=0.5\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 samples = 100]
+                 \addplot[color=black,style=solid,style=ultra thick]  table[x = n, y = sing_values] {./data/Compressible_Euler/1D/Singular_values/sv.txt};
+                 \addplot[color=black,style=dashed,style=ultra thick]  table[x = n, y = sv] {./data/Compressible_Euler/1D/Singular_values/sv_DEIM.txt};
+    \end{semilogyaxis}
+\end{tikzpicture}
+\caption{Singular values decay of the snapshot matrix related to POD and DEim algorithms for the 1D compressible Euler problem.}
+\label{fig:singular_values_decay_1D}
 \end{figure}

### 2018-07-13 sections/5.res_part2.tex

@@
 The governing equations that describe the conservation of mass, momentum, and energy of the quasi-1D CVRC flow, are the quasi-1D unsteady Euler equations for multiple species, expressed in conservative form as
-\begin{equation*}\label{eq:quasi-1D-equation}
-\frac{\partial \mathbf{u}}{\partial t} + \frac{\partial \mathbf{f}}{\partial x} = \mathbf{s}_A + \mathbf{s}_f + \mathbf{s}_q.
-\end{equation*}
-The conserved variable vector $\mathbf{u}$ and the convective flux vector $\mathbf{f}$ are
-\begin{equation*}\label{eq:CVRC-u-f}
-\mathbf{u}= \left( \begin{gathered}
+\begin{equation}\label{eq:5p2.1}
+\frac{\partial }{\partial t} v + \frac{\partial }{\partial x} F_v = s_A + s_f + s_q.
+\end{equation}
+The conserved variable vector $v$ and the convective flux vector $F$ are
+\begin{equation}\label{eq:5p2.2}
+v= \left( \begin{gathered}
 \rho A  \\
@@
 \end{gathered} \right), 
-\mathbf{f} = \left( \begin{gathered}
+F = \left( \begin{gathered}
 \rho uA  \\
@@
 \end{gathered} \right),
-\end{equation*}
+\end{equation}
 where $\rho$ is the density, $u$ is the velocity, $p$ is the pressure, $E$ is the total energy, $Y_{ox}$ is the mass fraction of oxidizer, and $A=A(x)$ is the cross section area of the duct.
 The pressure $p$ can be computed using the conserved variables as
-\begin{equation*}\label{eq:total-engery}
+\begin{equation}\label{eq:total-engery}
 E = \frac{p}{\rho (\gamma - 1)} + \frac{u^2}{2} - C_p T_{ref},
-\end{equation*}
+\end{equation}
 where $T_{ref}$ is the reference temperature and is set as 298.15 K in this paper.
@@
 The source terms are
-\begin{equation*}\label{eq:source-terms}
-\mathbf{s}_A = \left( \begin{gathered}
+\begin{equation} \label{eq:5p2.3}
+s_A = \left( \begin{gathered}
 0  \\
@@
 \end{gathered} \right), 
-\mathbf{s}_f = \left( \begin{gathered}
+s_f = \left( \begin{gathered}
 {\dot \omega}_f  \\
@@
 \end{gathered} \right), 
-{\mathbf{s}_q} = \left( \begin{gathered}
+{s_q} = \left( \begin{gathered}
 0  \\
@@
 \end{gathered} \right),
-\end{equation*}
+\end{equation}
 where $\dot{\omega}_f$ is the depletion rate of the fuel, $\dot{\omega}_{ox}$ is the depletion rate of the oxidizer, $h_0^f$ is the total enthalpy of the fuel, $\Delta h_{0}^{rel}$ is the heat of reaction per unit mass of fuel and $q'$ is the unsteady heat release term.
-$\mathbf{s}_A$ accounts for area variations, $\mathbf{s}_f$ and $\mathbf{s}_q$ are related to the combustion.
-$\mathbf{s}_f$ represents the addition of the fuel and its combustion with the oxidizer, which in turn results in the creation of the combustion products.
+$s_A$ accounts for area variations, $s_f$ and $s_q$ are related to the combustion.
+$s_f$ represents the addition of the fuel and its combustion with the oxidizer, which in turn results in the creation of the combustion products.
 The depletion rate of the fuel is
-\begin{equation}\label{eq:wf}
+\begin{equation}\label{eq:5p2.4}
 \dot{\omega}_{f}= \frac{k_f \dot{m}_f Y_{ox} \left(1+sin\xi\right)}{l_f-l_s},
@@
 where
-\begin{equation*}\label{eq:xi}
+\begin{equation}\label{eq:5p2.5}
 \xi= -\frac{\pi}{2} + 2\pi\frac{x-l_s}{l_f-l_s}, \hspace{0.5cm} \forall \hspace{0.2cm} l_s < x < l_f.
-\end{equation*}
+\end{equation}
 The setting of the fuel injection restricts the combustion to the region $l_s < x < l_f$.
@@
 The depletion rate of the oxidizer is computed by
-\begin{equation*}\label{eq:wox}
+\begin{equation}\label{eq:5p2.6}
 \dot{\omega}_{ox} = C_{o/f} \dot{\omega}_f,
-\end{equation*}
+\end{equation}
 where $C_{o/f}$ is the oxidizer-to-fuel ratio.
@@
 In this paper, we use the combustion response function designed by Frezzotti et al.
-\cite{frezzotti2017numerical,frezzotti2018quasi}, which is a function of the velocity, sampled at specific abscissa $\hat{x}$ that is almost coincident with the antinode of the first longitudinal modal shape, with a certain time lag $\tau$, i.e.,
-\begin{equation}\label{eq:response-function}
-q'\left( x,t\right) = \alpha g\left(x\right)  A\left(x\right) \left[ u\left( \hat{x},t-\tau \right) - \bar{u}\left( \hat{x} \right) \right].
+\cite{frezzotti2017numerical,frezzotti2018quasi}, which is a function of the velocity, sampled at specific abscissa $\hat{x}$ that is almost coincident with the antinode of the first longitudinal modal shape, with a certain time lag $t_0$, i.e.,
+\begin{equation}\label{eq:5p2.7}
+q'\left( x,t\right) = \alpha g\left(x\right)  A\left(x\right) \left[ u\left( \hat{x},t-t_0 \right) - \bar{u}\left( \hat{x} \right) \right].
 \end{equation}
 Here $\bar{u}$ is the time averaged velocity, estimated with the steady-state quasi-1D model assuming $q'=0$, and $g(x)$ is a Gaussian distribution  
-\begin{equation*}\label{eq:gx}
+\begin{equation}\label{eq:5p2.8}
 g\left(x\right)= \frac{e^{-\frac{\left(x-\mu\right)^2}{2\sigma^2}}}{\sqrt{2\pi\sigma^2}},
-\end{equation*}
+\end{equation}
 where $\mu$ is the mean and $\sigma$ is the standard deviation. The amount of heat release due to velocity oscillations is controlled by the parameter $\alpha$.
@@
 The perturbation is added by forcing the mass flow rate with a multi-sine signal
-\begin{equation}\label{eq:multisine}
+\begin{equation}\label{eq:5p2.9}
 \dot{m}_{ox} \left(t\right)= \dot{m}_{ox,0} \left[1 + \delta\sum_{k=1}^{K}  sin\left(2\pi k\Delta f t\right) \right],
@@
 The procedure of the unsteady simulation of the quasi-1D CVRC flow includes three steps:
-\begin{enumerate}[(1)]
+\begin{enumerate}
 	\item  Compute the steady-state solution by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $ and $q'=0$.
-	\item  Excite the system by adding a perturbation to the oxidizer mass flow rate according to (\ref{eq:multisine}) and setting $q'=0$.
-	\item  Perform the unsteady simulation by turning on the combustion response function $q'$ in (\ref{eq:response-function}) and turning off the oxidizer mass flow rate perturbation by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $.
+	\item  Excite the system by adding a perturbation to the oxidizer mass flow rate according to (\ref{eq:5p2.7}) and setting $q'=0$.
+	\item  Perform the unsteady simulation by turning on the combustion response function $q'$ in (\ref{eq:5p2.3}) and turning off the oxidizer mass flow rate perturbation by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $.
 \end{enumerate}
 
-A high-fidelity quasi-1D CVRC flow solver is built by employing the MUSCL reconstruction \cite{delis1998tvd}, the Lax-Friedrichs flux \cite{shu1988efficient} and the strong stability preserving, three-stage Runge-Kutta (SSP RK3) time stepping \cite{jiang1996efficient}.
-
-Note that the right hand side in \eqref{?} suggests that, in general, mass, momentum, and energy is not conserved.
-Furthermore, the complex coupling of the variables in \eqref{?} prohibits the application of complex and implicit time integration schemes.
-Therefore, a quasi-skew-symmetric form, introduced in \eqref{eq:3.7}, is considered for \eqref{?}.
+Note that the right hand side in \eqref{eq:5p2.3} suggests that, in general, mass, momentum, and energy is not conserved.
+Furthermore, the complex coupling of the variables in \eqref{eq:5p2.3} prohibits the application of complex and implicit time integration schemes.
+Therefore, a quasi-skew-symmetric form, introduced in \eqref{eq:3.7}, is considered for \eqref{eq:5p2.3}.
 This allows us to benefit from stability properties of skew-symmetric forms while using an explicit time integration scheme.
 
-Introduction of an artificial viscosity is essential for a robust and long time-integration of \eqref{?}.
-Common discretization schemes for \eqref{?} are often dissipative, e.g.
+Introduction of an artificial viscosity is essential for a robust and long time-integration of \eqref{eq:5p2.3}.
+Common discretization schemes for \eqref{eq:5p2.3} are often dissipative, e.g.
 the Lax-Friedrich scheme used in \cite{Wang:255719}.
-Since the skew-symmetric discretization is non-dissipative, we modify \eqref{} to write
-\begin{equation} \label{}
+Since the skew-symmetric discretization is non-dissipative, we modify \ref{eq:5p2.3} to write
+\begin{equation} \label{eq:5p2.10} 
 	\frac{\partial }{\partial t} v + \frac{\partial }{\partial x} F = s_A + s_f + s_q + d, \quad d = (0,\frac{\partial }{\partial x} \tau,0,0)^T,
 \end{equation}
-with $\tau = \mu \partial (u A)/ \partial x$, and $\mu = 6\times 10^{-5}$. The three-stage Runge-Kutta (SSP RK3) is used to then integrate
+with $\tau = \mu \partial (u A)/ \partial x$, and $\mu = 6\times 10^{-5}$.
+This type of artificial viscosity is chosen due to its simplicity.
+This, however, can be replaced with a more moderate and sophisticated method.
+The three-stage Runge-Kutta (SSP RK3) \cite{jiang1996efficient} is used to then integrate \eqref{eq:5p2.10} in time.
+The pressure profile for the steady state, with $q'=0$, and the pressure oscillatory mode in the unsteady phase is presented in \Cref{fig:5p2.2a}.
+We report that the added viscous term affects the level of pressure in the steady state and the aplitude of oscilations in the unsteady mode, compared to \cite{Wang:255719}.
+
+\begin{figure}[t]
+\centering
+\begin{subfigure}[]{0.47\linewidth}
+	\includegraphics[width=\textwidth]{./pic/init_pressure}
+	\caption{} \label{fig:5p2.2a}
+\end{subfigure}
+\begin{subfigure}[]{0.47\linewidth}
+	\includegraphics[width=\textwidth]{./pic/init_osc}
+	\caption{} \label{fig:5p2.2b}
+\end{subfigure} \\
+\begin{subfigure}[]{0.47\linewidth}
+	\includegraphics[width=\textwidth]{./pic/p_error}
+	\caption{} \label{fig:5p2.2c}
+\end{subfigure}
+\begin{subfigure}[]{0.47\linewidth}
+	\includegraphics[width=\textwidth]{./pic/rom_freq}
+	\caption{} \label{fig:5p2.2d}
+\end{subfigure}
+\caption{(a) Pressure profile of the steady state.
+(b) Oscillatory mode of pressure located at $x=0.36$ for the unsteady flow.
+(c) Relative error between the high-fidelity and approximated pressure.
+(d) Approximation of the oscillations.
+}
+\label{fig:5p2.2}
+\end{figure}
+
+The discontinuities that are involved in the solution \eqref{eq:5p2.10} suggests that a, relatively, large basis is required to resolve fine strucutres in the solution.
+In this paper, a POD basis is generated with $k=200$, $k=300$ and $k=400$ number of basis vectors.
+To avoid basis changes in reduced system, only one POD basis is considered for $\rho$, $\rho u$ $\rho E$ and $\rho Y_{ox}$.
+The explicit SSP RK3 is then used to integrated the reduced system in time, for the unsteady system.
+The source terms are evaluated in the high-fidelity space and then projected onto the reduced space.
+However, in principle, the DEIM can be applied to accelerate this evaluation.
+
+\Cref{fig:5p2.2c} shows the approximation error of the pressure, due to MOR.
+It is observed that the approximation is coherently enhanced as the number of basis vectors are increase.
+Furthermore, the approximated solution maintains high accuracy over a relatively long time-integration.
+The oscilations of pressure is demostrated in \Cref{fig:5p2.2d}.
+It is seen that the overall behaviour of pressure is well approximated using the reduced system.
+Similar results are obtained for a POD basis with higher number of modes.
+
+We note that the discrete form of \eqref{eq:5p2.10} is not in the full skew-symmetric form. Nontheless, the quisi-skew-symmetric discretization provides a remarkable stability preservation.

### 2018-07-15 sections/5.res.tex
first draft finished

--- 2018-07-13 sections/5.res.tex
@@
 
-\subsection{Vortex Merging}
-Consider the $2D$ incompressible Euler equation, \eqref{eq:3.8} with no viscous term, on a square domain $\Omega = [0,2\pi]^2$, provided with periodic boundary conditions.
+\subsection{Vortex Merging} \label{sec:res.1}
+Consider the 2-dimensional incompressible Euler equation \eqref{eq:3.8} , without any viscous terms, on a square domain $\Omega = [0,2\pi]^2$, with periodic boundary conditions.
 Spatial derivatives are discretized using a Fourier spectral method, which in centered differential operators in the Fourier space.
@@
 
-\subsection{The Compressible Euler Equation}
-\subsubsection{2D Kelvin-Helmholtz instability}
-Consider the 2D case of the compressible Euler equations \eqref{eq:3.18} ... .
-In this test case we consider the flows of different layers of an heterogenous fluid in relative horizontal motion.
-If the heterogeneity considered consists in a stratification of different density layers, the fluid develops, at the interface between two separated layers, an hydrodynamic instability called Kelvin-Helmholtz instability \cite{HHS}.
-As a result of  the different tangential velocities,  Given the considered geometrical setting and the absence of external forces, this phenomenon is induced only by the initial condition.
-In our test cases we consider three different layers,
+\subsection{2D Kelvin-Helmholtz instability}
+Consider a 2-dimensional compressible Euler equation \eqref{eq:3.18} in a periodic square box $[0,1]^2$.
+Unlike the incompressible example in \Cref{sec:res.1} a centered finite difference scheme of fourth order are used to discretize \eqref{eq:3.18}.
+The physical domain is discretized into a grid of $256\times 256$ nodes.
+
+The initial velocity field is given by
 \begin{equation*}
-dasdasd
+\begin{cases}
+& \mathbf{r} = 
+\begin{cases}
+& 2, \text{ if } 0.25<y<0.75,\\
+& 1, \text{ otherwise },
+\end{cases}
+\\
+& \mathbf{u}_x = a \sin(4\pi y) \left( e^{-\dfrac{(y-0.25)^2}{2\sigma^2}} + e^{-\dfrac{(y-0.75)^2}{2\sigma^2}} \right)\\
+& \mathbf{u}_y = 
+\begin{cases}
+& 0.5, \text{ if } 0.25<y<0.75,\\
+& -0.5, \text{ otherwise },
+\end{cases},
+\\
+& \mathbf{p} = 2.5,\\
+\end{cases}
 \end{equation*}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
+where $a=0.1$ and $\sigma=5\sqrt{2}\cdot 10^{-3}$.
+This corresponds to contacting streams of fluid with different densities.
+For specific choices of parameters describing the jets, fine structures and vortices emerges at the interface between the streams.
+Such instability is referred to as the Kelvin-Helmholtz instability \cite{HHS}.
+
+As centered finite difference schemes are dissipation free, resolving the discontinuous initial data requires application of an artificial viscosity.
+In the high-fidelity model, the method discussed in \cite{artificial_dissipation} is used as an artificial viscosity.
+However, at the level of the reduced system, this is replaced with a low pass filter over the expansion coefficients of POD basis vectors.
+
+The fully discrete skew-symmetric form \eqref{eq:3.27} is used as a time marching scheme with $\Delta t = 5 \cdot 10^{-4}$, the time step, over a period of $1$ time unit.
+
+\Cref{fig:error_decay_KH} illustrates that the accuracy of the method is consistently increase as higher number of POD basis modes are considered.
+Furthermore, the skew-symmetric form preserves the accuracy over the period of time integration.
+It is observed from \Cref{fig:snap_solution_KH} that all features of the flow are correctly represented in the reduced system, even with a low number of basis vectors.
+
+\begin{figure}[t]
 \centering
@@
 As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
+\label{fig:error_decay_KH}
 \end{figure}
 
+Conservation mass, momentum and energy is presented in \Cref{fig:conservation_DEIM}.
+The accuracy of the method in approximating these invariants is enhanced when the size of the basis is increased.
+Furthermore, \Cref{energy_error_KH} shows how the kinetic energy associated with the reduced system mimic the kinetic energy of the high-fidelity system.
+This ensures the correct evolution of kinetic energy, and thus, the internal energy.
+
+This helps with the correct distribution of the energy and ensures 
 \begin{figure}
@@
 From left to right we have the solution of the reduced model with $k=200$, $k=500$ and the high fidelity solution.}
-\label{fig:snap_solution_incompressible_Euler}
+\label{fig:snap_solution_KH}
 \end{figure}
 
-\subsubsection{1D Shock problem}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%% Singular values 1D problem %%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centering
-\begin{tikzpicture}[scale=0.5452]
-    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
-                 xlabel=Basis,
-                 label style={font=\large},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=0.7\linewidth, 
-                 height=0.5\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=0,
-                 ymax = 2,
-                 samples = 100]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = n, y = sing_values] {./data/Compressible_Euler/1D/Singular_values/sv.txt};
-    \end{semilogyaxis}
-\end{tikzpicture}
-\caption{Singular values decay of the snapshot matrix related to POD algorithms for the 1D compressible Euler problem.}
-\end{figure}
+\subsection{1D Shock problem}
+In this section we study the 1-dimensional compressible Euler problem, \eqref{eq:3.18} without viscous terms, with a steady state discontinuous solution.
+This is in preparation for \Cref{sec:5.res.4}, where development and propagation of shock waves is expected.
+Here we asses how the skew-symmetric form for \eqref{eq:3.18} can recover moving discontinuities at the level of reduced system.
+Consider a periodic boundary conditions on $\Omega = [0,1]$ with the initial condition`
+\begin{equation*}
+\begin{cases}
+& \mathbf{r} = 0.5+0.2 \cos(2\pi x),\\
+& \mathbf{u} = 1.5,\\
+& \mathbf{p} = 0.5+0.2 \sin(2\pi x).\\
+\end{cases}
+\end{equation*}
+The domain is discretized into $N=2000$ nodes and centered finite differences scheme are used to assemble the discrete Euler equation in skew-symmetric form, as discussed in \Cref{sec:skew.3}.
+
+The fully discrete skew-symmetric form \eqref{eq:3.27} is used for time integration over a time interval $[0,0.3]$.
+To resolve the discontinuous solution we consider an artificial viscosity with $\tau = \mu \partial u / \partial x$, where $\mu = 0.5 \cdot 10^{-4}$.
+
+\Cref{fig:energy_pres_1D} shows the conservation of conserved quantities for the high-fidelity and reduced system.
+Here, the high-fidelity model is also considered in the divergence and advective form to be compared with the skew-symmetric form.
+It is observed the reduced systems that are not in skew-symmetric form violate conservation of mass, momentum, and energy.
+Even as the high-fidelity systems in divergence and advective forms are stable, the constructed reduced system is unstable, even with very high number of basis vectors.
+On the other hand, it is seen that the skew-symmetric forms yield a stable and conservative reduce system.
+Note that the loss in the energy associated with the skew-symmetric form, seen in \Cref{conservation_1D_focus}, is due to the application of an artificial viscosity.
+
+As discussed in \Cref{sec:mor_skew}, the DEIM approximation for evaluating nonlinear components of \eqref{eq:3.18} can affect the conservative properties of the skew-symmetric form.
+\Cref{fig:singular_values_decay_1D} shows the decay of the singular values of the nonlinear snapshots.
+It is observed that the decay of these snapshots is significantly slower than the temporal snapshots of \eqref{eq:3.18}.
+This indicates that to maintain the accuracy of the reduced system, the DEIM basis should be chosen richer than the POD basis.
+\Cref{error_DEIM} and \Cref{energy_DEIM} present the error and the conservation of total energy when the DEIM is used to approximate the nonlinear term.
+It is observed that the conservation of energy is recovered once DEIM approximates the nonlinear terms with enough accuracy.
 

### 2018-07-15 sections/5.res_part2.tex
first draft finished

@@
-\subsection{Continuous Variable Resonance Combustor}
+\subsection{Continuous Variable Resonance Combustor} \label{sec:5.res.4}
 
@@
 
-The discontinuities that are involved in the solution \eqref{eq:5p2.10} suggests that a, relatively, large basis is required to resolve fine strucutres in the solution.
+The discontinuities that appear in the solution of \eqref{eq:5p2.10} suggests that a, relatively, large basis is required to resolve fine strucutres in the solution.
 In this paper, a POD basis is generated with $k=200$, $k=300$ and $k=400$ number of basis vectors.

### 2018-07-15 sections/6.con.tex
first draft finished

\section{Conclusions} \label{sec:con}

Conservation of nonlinear invariants are not, in general, guaranteed with conventional model reduction techniques. The violation of such invariants often result in a qualitatively wrong or unstable reduce system, even when the high-fidelity system is stable. This is particularly important for fluid flow, where conservation of the energy, as a nonlinear invariant of the system, is crucial for a correct numerical evaluation.

In this paper, we discuss that conservative properties of the skew-symmetric form for fluid flow can naturally be extended to the reduced system. Conventional MOR techniques preserves the skew-symmetry of differential operator which result in conservation of quadratic invariants at the level of reduced system. Furthermore, we see that the reduced system, also, contains quadratic invariants with respect to the reduced variables that approximates the invariants of the high-fidelity system. This results in construction of a physically meaningful reduced system, rather than a mere couple systems of differential equations.

Numerical experiments of the incompressible and compressible Euler equation confirms conservation of mass, momentum and energy for the model reduction with the skew-symmetric discretization. It is seen that when a non-skew-symmetric form, e.g. divergence form or advective form, is considered, MOR does not necessarily yield a stable reduced system. On the other hand the skew-symmetric form consistently yields a robust reduced system over long time-integration, even if when the reduce space does not represent the high-fidelity solution accurately.

Finally, a MOR of a quasi-skew-symmetric form for the CVRC model is presented. Although this model is not in a full skew-symmetric form and am explicit Runge-Kutta method used for time-integration, we still recover remarkable stability preservation.

### 2018-07-16 sections/5.res.tex
Update Nicolo corrections

@@
 \end{subfigure}
-  \caption{(\protect\subref{compare_different_models}) Conservation of the kinetic energy $K$ for the advective, divergence and the skew-symmetric formulations.
-(\protect\subref{singular_values_decay}) The decay of the singular values for the merging vortices problem.
+  \caption{(\protect\subref{compare_different_models}) The kinetic energy $K$ for the advective, divergence and the skew-symmetric formulations.
+(\protect\subref{singular_values_decay}) The decay of the singular values for the vortex merging.
 }
@@
 \caption{Snapshots of the high-fidelity system and the reduced system at $t=\left\{ 4,8,12,18 \right\}$.
-From left to right: the snapshots of the reduced model with $k=17$, $k=35$ and the high fidelity solution.}
+From left to right: the solution of the reduced model with $k=17$, $k=35$ and the high fidelity solution.}
 \label{fig:snap_solution_incompressible_Euler}
@@
 \label{fig:energy_approx_err}
-\caption{(\protect\subref{fig:approx_error_incompressible_Euler}) Evolution of 2-norm error in velocity, between the high-fidelity system and the reduced system.
+\caption{(\protect\subref{fig:approx_error_incompressible_Euler}) Evolution of $L_2$ error in velocity, between the high-fidelity system and the reduced system.
 (\protect\subref{fig:energy_error_incompressible_Euler}) Conservation of the kinetic energy.}
@@
 \caption{Evolution in time of the error  between the high fidelity solution of the Kelvin-Helmoltz and the reduced solution for different number of basis $k$.
-As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
+As error measure we use $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
 \label{fig:error_decay_KH}
@@
   \end{subfigure}
-\caption{Comparison between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
+\caption{Difference between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
 \label{fig:conservation_DEIM}
@@
 \caption{Solutions of the Kelvin-Helmholtz problem at $t=\left\{ 0.4, 0.6, 0.8, 1 \right\}$.
-From left to right we have the solution of the reduced model with $k=200$, $k=500$ and the high fidelity solution.}
+From left to right we show the solution of the reduced model with $k=200$, $k=500$ and the high fidelity solution.}
 \label{fig:snap_solution_KH}
@@
 Note that the loss in the energy associated with the skew-symmetric form, seen in \Cref{conservation_1D_focus}, is due to the application of an artificial viscosity.
+Enriching the basis chosen for the  POD approximation leads to more accurate reduced solutions, as shown in \Cref{error_behaviour_1D}.
+In the same Figure, we observe that even though the reduced model manages to capture the discontinuity developed after half time units have been simulated, the accuracy is reduced of
+$2$ orders of magnitude.
+In \Cref{fig:snaps_1D_Euler}, snapshots of the reduced solution for different formulations are reported, showing the development of instabilities for non skew-symmetric formulations.
 
@@
 It is observed that the conservation of energy is recovered once DEIM approximates the nonlinear terms with enough accuracy.
+While straightforward POD reduction does not offer a significative speed up if compared to the solution of the original high-dimensional nonlinear system of equations, with the DEIM treatment of nonlinearity solvers of the reduced models are of the order of tens faster than high fidelity solvers.
 
@@
   \caption{(\protect\subref{conservation_1D})  Evolution of the three conserved quantities for the reduced solution of the compressible Euler equation (mass, total momentum and total energy).
-The divergent, advective and skew-symmetric formulations have been considered and $k=102,204$ basis are used for the reduction.
-(\protect\subref{conservation_1D_focus}) Focus on the conserved quantity in case of stable reduction using the skew-symmetric formulation.}
+The divergent, advective and skew-symmetric formulations have been considered and $k=102,204$ basis are used in the reduced model.
+(\protect\subref{conservation_1D_focus}) Evolution of the conserved quantity for a stable reduced model using the skew-symmetric formulation.}
   \label{fig:energy_pres_1D}
@@
 \caption{Qualitative comparison between different formulations for the reduced model in terms of density (\protect\subref{density_reduction_1D})  and pressure(\protect\subref{pressure_reduction_1D}) at $t=0.1,0.3$ and $1$s.
-Results for the advective formulation are not showed here because the related reduced solutions are unstable after few time steps.}
+Results for the advective formulation are not showed here because the related reduced solutions are unstable after a few time steps.}
 \label{fig:snaps_1D_Euler}
@@
 \end{tikzpicture}
-\caption{Singular values decay of the snapshot matrix related to POD and DEim algorithms for the 1D compressible Euler problem.}
+\caption{Decay of the singular values of the snapshot matrix related to POD and DEIM algorithms for the 1D compressible Euler problem.}
 \label{fig:singular_values_decay_1D}

### 2018-07-17 paper.tex
tex file for CVRC is now separated
first draft finished
first corrections added

@@
 
-\title*{Conservative Model Order Reduction of Fluid Flow}
+\title*{Conservative Model Order Reduction for Fluid Flow}
 % Use \titlerunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\author{Bababk Maboudi Afkham, Nicol\`o Ripamonti, Qian Wang, Jan S. Hesthaven and Karen E. Willcox}
+\author{Babak Maboudi Afkham, Nicol\`o Ripamonti, Qian Wang, Jan S. Hesthaven and Karen E. Willcox}
 % Use \authorrunning{Short Title} for an abbreviated version of
@@
 However, MOR of hyperbolic equations remains a challenge.
-Symmetries and conservation laws, which are a distinctive feature of such systems, are often destroyed over the course of conventional MOR techniques.
-This often result in a perturbed, and often unstable reduced system.
-The importance of the conservation of energy is well-known in a correct numerical integration of fluid flow.
-In this paper, we discuss a model reduction routine, that exploits skew-symmetry of conservative and centered discretization schemes, to recover conservation of energy at the level of reduced system.
+Symmetries and conservation laws, which are a distinctive feature of such systems, are often destroyed by conventional MOR techniques which result in a perturbed, and often unstable reduced system.
+The importance of conservation of energy is well-known for a correct numerical integration of fluid flow.
+In this paper, we discuss model reduction, that exploits skew-symmetry of conservative and centered discretization schemes, to recover conservation of energy at the level of the reduced system.
 Moreover, we argue that the reduced system, constructed with the new method, can be identified by a reduced energy that mimics the energy of the high-fidelity system.
-Therefore, the loss in energy, associated with model reduction, remains constant in time.
-This results in an, overall, correct evolution of the fluid and ensures robustness of the reduced system.
-We evaluate the performance of the proposed method through numerical simulation of various fluid flows, and also in a numerical simulation of continuous variable resonance combustor model.}
+Therefore, the loss in energy, associated with the model reduction, remains constant in time.
+This results in an, overall, correct evolution of the fluid that ensures robustness of the reduced system.
+We evaluate the performance of the proposed method through numerical simulation of various fluid flows, and through a numerical simulation of a continuous variable resonance combustor model.}
 
@@
 \input{./sections/5.res.tex}
+\input{./sections/5.res_part2.tex}
 \input{./sections/6.con.tex}

### 2018-07-17 sections/1.intro.tex
first corrections added

@@
 Model order reduction (MOR), and in particular reduced basis (RB) methods, has emerged as a powerful approach to cope with the complex and computationally intensive models in engineering and science.
-Such techniques, construct a reduced ordered representation for the state of a model which accurately approximates the configuration of the system.
-The evaluation of the this representation is, then, possible with considerable acceleration.
+Such techniques construct a reduced ordered representation for the state of a model which accurately approximates the configuration of the system.
+The evaluation of this representation is then possible with considerable acceleration.
 
 Although RB methods are successful in reducing the computational complexity of models with elliptic and parabolic partial differential equations (PDEs), MOR of systems of hyperbolic equations, or models with strong advective terms, remains a challenge.
-Often, such models arise from a set of invariants and conservation laws.
-Such symmetries are violated over the course of MOR which result in a qualitatively wrong, and sometimes unstable, solution.
+Often, such models arise from a set of invariants and conservation laws, some of which are violated by MOR which result in a qualitatively wrong, and sometimes unstable, solution.
 
@@
 Structure preservation can recover a physically meaningful reduced model, rather than a pure algebraic coupling of equations.
-This enforces robustness and can help with the stability of reduced model.
-A non-exhaustive list of recent works on structure preserving MOR is as follows.
+This enforces robustness and can help with the stability of the reduced model.
 Preserving time-symmetries of Lagrangian, Hamiltonian, and port-Hamiltonian systems can be found in the works of \cite{Carlberg:2014ky,doi:10.1137/140978922,doi:10.1137/17M1111991,1705.00498,beattie2011structure,chaturantabut2016structure,gugercin2012structure}.
-Conserving the inf-sup stability, in the context of finite element methods, can be found in the works of \cite{farhat2015structure,ballarin2015supremizer}.
+Conserving inf-sup stability, in the context of finite element methods, can be found in \cite{farhat2015structure,ballarin2015supremizer}.
 Furthermore, a flux preserving model reduction for finite volume methods is presented in \cite{carlberg2018conservative}.
 
-Large scale simulation of fluid flows appear in a wide range of disciplines and industries.
-Therefore, MOR of fluid flows, specially when advective terms are dominant, is of a high importance.
+Large scale simulations of fluid flows arise in a wide range of disciplines and industries.
+Therefore, MOR of fluid flows, specially when advective terms are dominant, is important.
 It is well known that conservation of the energy, specially kinetic energy, is essential for a qualitatively correct numerical integration of fluid flows.
-Conventional model reduction techniques often violates conservation of mass, momentum \cite{carlberg2018conservative}, or energy in fluid flows which result in an unstable reduced system, specially over long time-integration.
+Conventional model reduction techniques often violates conservation of mass, momentum \cite{carlberg2018conservative}, or energy in fluid flows which result in an unstable reduced system, in particular for long time-integration.
 The method discussed in \cite{carlberg2018conservative} conserves the mass and momentum for a finite volume discretization scheme.
@@
 
-Skew-symmetric forms for fluid flows are centered time and space discretization schemes, typically using a finite differences discretization method, that recovers time-symmetries of a fluid at the discrete level.
+Skew-symmetric formulation of fluid flows construct a skew-symmetric differential operator, acting on the momentum vector field, that ensures conservation of quadratic invariants, such as energy.
+Combined wirh centered time and space discretization schemes, typically a finite differences discretization method, they recover time-symmetries of a fluid at the discrete level.
 Such discretization schemes are studies comprehensively over the past few decades and can be found in the works of \cite{morinishi2010skew,morinishi1998fully,desjardins2008high,reiss2014conservative,reiss2014conservative} and the references therein.
-These schemes construct a skew-symmetric differential operator, acting on the momentum vector field, that ensures conservation quadratic invariants, such as energy.
 
-In this paper we discuss how to preserve skew-symmetry of differential operators at the level of reduced system.
+In this paper we discuss how to preserve skew-symmetry of the differential operators at the level of the reduced system.
 This results in conservation of quadratic invariants.
 Furthermore, we show that the reduced system, as a system of coupled differential equations, contains quadratic invariants and an associated energy which approximates the energy of the high-fidelity system.
-Therefore, a proper time stepping scheme can preserve the reduced representation of the energy, and therefore, the loss in energy due to model reduction remains constant in time.
+Therefore, a proper time stepping scheme preserves the reduced representation of the energy, and therefore, the loss in energy due to model reduction remains constant in time.
 
 The rest of this paper is organized as follows.
-In \Cref{sec:mor} we summarize the theory on MOR and introduce proper orthogonal decomposition (POD) as a conventional RB method.
+In \Cref{sec:mor} we summarize the theory on MOR and introduce the proper orthogonal decomposition (POD) as a conventional RB method.
 We discuss skew-symmetric and conservatives methods for compressible and incompressible fluid flows in \Cref{sec:skew}.
 Conservative and energy-preserving model reduction of fluid flows is discussed in \Cref{sec:mor_skew}.
-We evaluate the performance of the method, in numerical simulations of incompressible and compressible fluid flow in \Cref{sec:res}.
+We evaluate the performance of the method through numerical simulations of incompressible and compressible fluid flow in \Cref{sec:res}.
 We also apply the method to construct a reduced system for the continuous variable resonance combustor, a one dimensional reaction-diffusion model for a rocket engine.

### 2018-07-17 sections/4.mor_skew.tex
further corrections added

@@
 \section{Model Reduction of Fluid Flow} \label{sec:mor_skew}
-Straight forward model reduction of \eqref{eq:3.8} and \eqref{eq:3.18} does not, in general, preserves symmetries and conservation laws that were presented in \Cref{sec:skew}.
-In this section we discuss how to exploit the discrete skew-symmetric structure of \eqref{eq:3.13} and \eqref{eq:3.21} to recover conservation of mass, momentum, and energy at the level of reduced system.
+A straight-forward model reduction of \eqref{eq:3.8} and \eqref{eq:3.18} does not, in general, preserve symmetries and conservation laws, presented in \Cref{sec:skew}.
+In this section we discuss how to exploit the discrete skew-symmetric structure of \eqref{eq:3.13} and \eqref{eq:3.21} to recover conservation of mass, momentum, and energy at the level of the reduced system.
 
 Let $V_{\mathbf r}$, $V_{\mathbf r \mathbf u}$, and $V_{\mathbf u_i}$ be the reduced bases for the snapshots of $\mathbf r$, $R \mathbf u$, and $\mathbf u_i$, respectively.
-For the one dimensional case, the subscript ``$i$'' is omitted and in case of an incompressible fluid, $V_{ \mathbf r}$ and $V_{\mathbf r \mathbf u}$ are not computed.
+For the one dimensional case, the subscript ``$i$'' is omitted and for an incompressible fluid, $V_{ \mathbf r}$ and $V_{\mathbf r \mathbf u}$ are not computed.
 For the purpose of simplicity, we assume that all bases have the size $k$.
-We seek to project $S_{\mathbf u}$ and $S_{\mathbf r \mathbf u}$ onto the reduced space, such that the projection preserves the skew-symmetry property.
+We seek to project $S_{\mathbf u}$ and $S_{\mathbf r \mathbf u}$ onto the reduced space, such that the projection preserves the skew-symmetric property.
 The projected operators, using a Galerkin projection, read
@@
 Note that $S^r_{\mathbf r ,\partial_t}$ is not computed explicitly.
-It is seen that the $S^r _{\mathbf u}$ is already in a skew-symmetric form.
+It is clear that $S^r _{\mathbf u}$ is already in a skew-symmetric form.
 On the other hand, $S^r_{\mathbf r ,\partial_t}$ and $S^r _{\mathbf r \mathbf u}$ are not, in general, skew-adjoint and skew-symmetric, respectively.
 This can be ensured, however, by requiring $V_{\mathbf r \mathbf u} = V_{\mathbf u}$.
-We denote such a basis by $V_{\mathbf r \mathbf u, \mathbf u}$.Using \eqref{eq:4.1} and \eqref{eq:4.2}, a Galerkin projection of momentum equation in \eqref{eq:3.13} and governing equations for a compressible fluid in \eqref{eq:3.21} take the form
+We denote such a basis by $V_{\mathbf r \mathbf u, \mathbf u}$.Using \eqref{eq:4.1} and \eqref{eq:4.2}, a Galerkin projection of the momentum equation in \eqref{eq:3.13} and the governing equations for a compressible fluid in \eqref{eq:3.21} take the form
 \begin{equation} \label{eq:4.3}
@@
 	& \frac{d}{dt} \mathbf r^r + \sum_{i=1}^k V^T_{\mathbf r}DU_iV_{\mathbf r}\mathbf r^r = 0, \\
-	& S^r_{\mathbf r ,\partial_t} + S^r _{\mathbf r \mathbf u} \mathbf u^r + V_{\mathbf r \mathbf u, \mathbf u}^T D \mathbf V_{\mathbf p} \mathbf p^r = V_{\mathbf r \mathbf u, \mathbf u}^T D T, \\
-	&\frac{1}{\gamma -1} \frac{d}{dt} \mathbf p^r + \frac{\gamma}{\gamma -1} \mathbf V_{\mathbf p}^T D U V_{\mathbf p} \mathbf p^r - \mathbf V_{\mathbf p}^T UD V_{\mathbf p} \mathbf p^r = - V_{\mathbf p}^T UDT + V_{\mathbf p}^T D(UT - \mathbf \phi).
+	& S^r_{\mathbf r ,\partial_t} + S^r _{\mathbf r \mathbf u} \mathbf u^r + V_{\mathbf r \mathbf u, \mathbf u}^T D V_{\mathbf p} \mathbf p^r = V_{\mathbf r \mathbf u, \mathbf u}^T D T, \\
+	&\frac{1}{\gamma -1} \frac{d}{dt} \mathbf p^r + \frac{\gamma}{\gamma -1} V_{\mathbf p}^T D U V_{\mathbf p} \mathbf p^r - V_{\mathbf p}^T UD V_{\mathbf p} \mathbf p^r = - V_{\mathbf p}^T UDT + V_{\mathbf p}^T D(UT - \mathbf \phi).
 \end{aligned}
@@
 Note that in \eqref{eq:4.4}, dependency of $T$ on $V_{\mathbf r \mathbf u , \mathbf u}$ is not shown for abbreviation.
-In \eqref{eq:4.3} and \eqref{eq:4.4}, $D_i$ is always multiplied from left with a basis matrix or a diagonal matrix.
-Therefore, the telescoping sum discussed in condition 2 in \Cref{sec:skew.1} cannot be used to show conservation of mass and momentum.
+In \eqref{eq:4.3} and \eqref{eq:4.4}, $D_i$ is always multiplied from the left with a basis matrix or a diagonal matrix.
+Therefore, the telescoping sum, discussed in Condition 2 in \Cref{sec:skew.1}, cannot be used to show conservation of mass and momentum.
 However, POD preserves linear properties of snapshots.
-To demonstrate, let the overscript ``\textasciitilde'' denote the representation of a reduced variable in the high fidelity space.
+To demonstrate this, let the overscript ``\textasciitilde'' denote the representation of a reduced variable in the high fidelity space.
 A reduced variable, e.g.
 density, can be represented as a linear combination of some snapshots as $\mathbf r \approx \tilde{\mathbf r} = \sum_{i=1}^k c_i \mathbf r_i$, for some snapshots $\mathbf r_i$ and some coefficients $c_i \in \mathbb R$, for $i=1,\dots,k$.
-The conservation of mass, evaluated by $\tilde{\mathbf r}$, reads
+Conservation of mass, evaluated by $\tilde{\mathbf r}$, reads
 \begin{equation} \label{eq:4.5}
-	\frac{d}{dt} \mathbf 1^T \tilde {\mathbf r} = \sum_{i=1}^k c_i  \left( \mathbf 1^T \frac{d}{dt} \mathbf r_i \right) = - \sum_{i=1}^k c_i  \left( \mathbf 1^T DR_i\mathbf u_i \right) = 0.
+	\frac{d}{dt} \mathbf 1^T \tilde {\mathbf r} = \sum_{i=1}^k c_i  \left( \mathbf 1^T \frac{d}{dt} \mathbf r_i \right) = - \sum_{i=1}^k c_i  \left( \mathbf 1^T DR_i\mathbf u_i \right) = 0,
 \end{equation}
-Here we used the fact that $\mathbf 1^T D = \mathbf 0^T$. Similarly, we recover conservation of momentum
+where we used the fact that $\mathbf 1^T D = \mathbf 0^T$. Similarly, we recover conservation of momentum
 \begin{equation} \label{eq:4.6}
@@
 Here, $\tilde{\mathbf u} = \sum_{i=1}^k d_i \mathbf u_i$, for some snapshot $\mathbf u_i$ and coefficients $d_i \in \mathbb R$.
-Denoting by $\{ R \mathbf u\}^r$ the reduced representation of $R\mathbf u$ in basis $V_{\mathbf r \mathbf u , \mathbf u}$, the evolution of kinetic energy reads
+Denoting by $\{ R \mathbf u\}^r$ the reduced representation of $R\mathbf u$ in basis $V_{\mathbf r \mathbf u , \mathbf u}$, the evolution of kinetic energy is expressed as
 \begin{equation} \label{eq:4.7}
@@
 \end{equation}
-In the missing steps in the last line, the skew-symmetry of $S_{\mathbf r \mathbf u}^r$ is used.
+In the missing steps in the last line, skew-symmetry of $S_{\mathbf r \mathbf u}^r$ is used.
 Note, that only the reduced pressure and the viscous term contribute to the evolution of kinetic energy.
-Furthermore, the quantity $ \frac 1 2 {\mathbf u^r}^T \{ R \mathbf u\}^r$ is the kinetic energy associated with the reduced system \eqref{eq:4.4} that approximates the kinetic energy of the high-fidelity system \eqref{eq:3.21} and is a quadratic form with respect to the reduced variables.
+Furthermore, the quantity $ \frac 1 2 {\mathbf u^r}^T \{ R \mathbf u\}^r$ is the kinetic energy associated with the reduced system \eqref{eq:4.4}, approximating the kinetic energy of the high-fidelity system \eqref{eq:3.21} and is a quadratic form with respect to the reduced variables.
 Conservation of kinetic energy for \eqref{eq:4.3} follows similarly.
-With what discussed above, it is  straight forward to check that
+It is  straight-forward to check that
 \begin{equation} \label{eq:4.8}
@@
 i.e., the total energy is conserved.
-We can immediately recognize that $ \mathbf p^r /(\gamma - 1)$ is the internal energy of the reduced system.
+We immediately recognize that $ \mathbf p^r /(\gamma - 1)$ is the internal energy of the reduced system.
 However, the total internal energy of \eqref{eq:4.4} is a weighted sum, $ b^T\mathbf p^r /(\gamma - 1)$, with $b = V_{\mathbf p}^T \mathbf 1$ which is an approximation of the total internal energy in \eqref{eq:3.21}.
@@
 \begin{proposition}
-	The loss in the mass, momentum and energy associated with model reduction in \eqref{eq:4.4} is constant in time, and therefore, bounded.
+	The loss in the mass, momentum and energy associated with the model reduction in \eqref{eq:4.4} is constant in time, and therefore, bounded.
 \end{proposition}
@@
 \begin{equation}
-	S_{\mathbf u}^r = V^T_{\mathbf u} ( DU + UD ) V^T_{\mathbf u},
+	S_{\mathbf u}^r = V^T_{\mathbf u} ( DU + UD ) V^T_{\mathbf u}.
 \end{equation}
-for simplicity in one spacial dimension.
 We write $U$ as a linear combination of matrices as $U = \sum_{j=1}^k \mathbf u ^r_j U_j$, where $\mathbf u ^r_j$ is the $j$th component of $\mathbf u ^r$, and $U_j$ contains the $j$th column of $V_{\mathbf u}$ on its diagonal.
@@
 \begin{equation}
-	S_{\mathbf u}^r = \sum_{j=1}^k \mathbf u ^r_j \left( V^T_{\mathbf u} ( DU_j + U_jD ) V^T_{\mathbf u} \right),
+	S_{\mathbf u}^r = \sum_{j=1}^k \mathbf u ^r_j \left( V^T_{\mathbf u} ( DU_j + U_jD ) V^T_{\mathbf u} \right).
 \end{equation}
-and the matrices $V^T_{\mathbf u} ( DU_j + U_jD ) V^T_{\mathbf u}$ can be computed prior to the time integration of the reduced system.
+The matrices $V^T_{\mathbf u} ( DU_j + U_jD ) V^T_{\mathbf u}$ can be computed prior to the time integration of the reduced system.
 However, the form of the fully discrete system in \eqref{eq:3.27} introduces cubic and even quartic terms.
-Although, in principle, the same method can be applied to assemble the nonlinear terms, however, the number of precomputed matrices can grow proportional to the order of nonlinear term.
+In principle, the same method can be applied to assemble the nonlinear terms.
+However, the number of precomputed matrices grows proportional to the order of the nonlinear term.
 
-To accelerate the assembly of the nonlinear terms that require a large number of precomputed matrices, we may approximately evaluate them using the discrete empirical interpolation method (DEIM).
+To accelerate assembly of the nonlinear terms we may approximately evaluate them using the discrete empirical interpolation method (DEIM).
 This approximation can affect the accuracy of conserved quantities in \eqref{eq:4.4}.
-Therefore, the accuracy of DEIM approximation should be chosen considerably higher than the one from POD.
+Therefore, the accuracy of the DEIM approximation must be chosen higher than the one of POD.
 
@@
 Subsequently, a basis for $\sqrt{\mathbf r}$, denoted by $V_{\sqrt{\mathbf r}}$, is constructed.
-The nonlinear terms, are evaluated exactly using the quadratic expansion or approximated using the DEIM.
+The nonlinear terms are evaluated exactly using the quadratic expansion or approximated using the DEIM.

### 2018-07-17 sections/5.res.tex
further corrections added

@@
 \subsection{Vortex Merging} \label{sec:res.1}
-Consider the 2-dimensional incompressible Euler equation \eqref{eq:3.8} , without any viscous terms, on a square domain $\Omega = [0,2\pi]^2$, with periodic boundary conditions.
-Spatial derivatives are discretized using a Fourier spectral method, which in centered differential operators in the Fourier space.
-To capture the fine details characterizing the solution, $256\times 256$ modes have been adopted.
-The initial condition is given in terms of the vorticity distribution $\mathbf{\omega} = \nabla \times u$.
-
-We consider the evolution of three different vortices, and the initial structure is given by
+Consider the 2-dimensional incompressible Euler equation \eqref{eq:3.8} on a square domain $\Omega = [0,2\pi]^2$, with periodic boundary conditions.
+Spatial derivatives are discretized using a Fourier spectral method.
+To capture the fine details characterizing the solution, $256\times 256$ modes is used.
+We consider the evolution of three vortices, with the initial structure given by
 \begin{equation}\label{eqn:initial_cond_vort}
@@
 \end{equation}
-In \eqref{eqn:initial_cond_vort}, $(x,y)$ represents the spatial coordinates, $\left( x_i, y_i\right)$ is the center of the $i$th vortex, $\alpha_i$ its maximum amplitude, and $\beta$ controls the effective radius of the vortex.
-In this example, the center of three vortices are positioned at
+Here, $\omega = \nabla \times u$ is the vorticity, $(x,y)$ represents the spatial coordinates, $\left( x_i, y_i\right)$ is the center of the $i$th vortex, $\alpha_i$ its maximum amplitude, and $\beta$ controls the effective radius of the vortex.
+In this example, the center of three vortices are
 \begin{equation}
@@
 \end{equation}
-close to the center of the domain, of which, two have positive spins with $\alpha_1 = \alpha_2 = \pi$ and the other rotates in the opposite direction with $\alpha_3 = -0.5\pi$.
+close to the center of the domain.
+Two of the vortices have a positive spin with $\alpha_1 = \alpha_2 = \pi$ and the third rotates in the opposite direction with $\alpha_3 = -0.5\pi$.
 The effective radius of all the vortices is set to $\beta = 1 / \pi$.
-This arrangement of vortices is an effective initial condition for the process of merging vortices.
+This arrangement of vortices is an interesting initial condition to study the process of vortex merging.
 This phenomenon is often a result of fast-moving dipoles of vortices with the same spin facing another vortex \cite{filaments_vort2} of opposite spin.
-The forces developed in the merging process transfers the vorticity from the initial configuration, into long, narrow, and spiral-shaped strips of intense vorticity \cite{filaments_vort}.
-The formation of such thin vorticity filaments in the fluid, can pose numerical challenges.
+The merging process transfers the vorticity from the initial configuration into long, narrow, and spiral-shaped strips of intense vorticity \cite{filaments_vort}.
+The formation of such thin vorticity filaments in the fluid may pose numerical challenges, due to aliasing.
 
-In the context of MOR, conservation of energy and stability is crucial for capturing fined structures, mentioned above.
-In the absence of natural dissipation, characterizing the Euler equation, straight forward application of MOR techniques is often unstable.
+In the context of MOR, conservation of energy and stability is crucial to capturing fine structures.
+With the absence of natural dissipation, straight forward application of MOR techniques for the Euler equation is often unstable.
 
-To define the initial conditions in terms of the velocity components $\omega$ and the pressure $p$, we define a stream-function $\Psi$, the solution to the equation 
+To define the initial conditions in terms of the velocity components $u$ and the pressure $p$, we define a stream-function $\Psi$, the solution to the equation 
 \begin{equation} \label{eq:5.1}
-	\nabla \Psi = \omega.
+	- \Delta \Psi = \omega.
 \end{equation}
@@
 obtained by applying the divergence operator to \eqref{eq:3.8} and using the incompressibility condition.
- The implicit midpoint scheme, to mimic the time integration scheme presented in \eqref{eq:3.27}, is considered to integrate in time.
+ The implicit midpoint scheme, to mimic the time integration scheme presented in \eqref{eq:3.27}, is used to integrate in time.
 The merging phenomenon is simulated for a total of $18$ time units using a temporal step $\Delta t=0.004$.
@@
 \Cref{compare_different_models} illustrates the evolution of the kinetic energy for the advective, divergence, and the skew-symmetric form of the high-fidelity system.
-It is observed that only the skew-symmetric form preserves the kinetic energy, confirming the results in \Cref{sec:skew.2}.
+It is observed that only the skew-symmetric form preserves the kinetic energy, confirming the discussion in \Cref{sec:skew.2}.
 
@@
 A total of $5000$ temporal snapshots is used to construct a reduced basis, following the process discussed in \Cref{sec:mor}.
-The decay of the singular values, as an indication of the reducibility of the problem, is presented in \Cref{singular_values_decay}.
-The first $35$ POD modes corresponds to over $99\%$ of the modes energy of the high fidelity solution.
+The decay of the singular values, used as an indication of the reducibility of the problem, is presented in \Cref{singular_values_decay}.
+The first $35$ POD modes corresponds to over $99\%$ of the modes of the high fidelity solution.
 This suggests that an accurate reduced system can be constructed using a small number of basis vectors.
@@
 
-For a qualitative analysis, in Figure \ref{fig:snap_solution_incompressible_Euler}, four snapshots at different time frames are shown for the high fidelity system and reduced system with $k=17$ and $k=35$ modes.
-It is seen that the overall dynamics of the problem, and in particular the formation and development of vorticity filaments, are correctly represented, even with a moderate number of basis vectors.
+For a qualitative analysis, in Figure \ref{fig:snap_solution_incompressible_Euler}, four solutions at different times are shown for the high fidelity system and the reduced system with $k=17$ and $k=35$ modes.
+The overall dynamics of the problem, and in particular the formation and development of vorticity filaments, are correctly represented, even with a moderate number of basis vectors.
 Although small details are not captured by the reduced system with a small number of basis vectors, the position and the spreading of the vortices are comparable.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\Cref{fig:approx_error_incompressible_Euler} shows the 2-norm error between the high-fidelity solution and the approximated solution.
-It is seen that the error decreases, consistently, as the number of basis vectors increase.
+\Cref{fig:approx_error_incompressible_Euler} shows the $L^2$ error between the high-fidelity solution and the reduced solution.
+The error decreases, consistently, as the number of basis vectors increases.
 Furthermore, the accuracy is maintained over the period of time integration.
@@
 The conservation of the kinetic energy is presented in \Cref{fig:energy_error_incompressible_Euler}.
-It is seen that even for a small number of basis vectors, where the solution is not well approximated, the kinetic energy is conserved.
-Furthermore, it is observed that the error in the kinetic energy, due to MOR, is constant in time.
-This helps with the robustness of the reduced system over long time-integration.
+Even for a small number of basis vectors, where the solution is not well approximated, the kinetic energy remains constant.
+Furthermore, the error in the kinetic energy, due to MOR, is constant in time.
+This is central for the robustness of the reduced system during long time-integration.
 
@@
 \subsection{2D Kelvin-Helmholtz instability}
-Consider a 2-dimensional compressible Euler equation \eqref{eq:3.18} in a periodic square box $[0,1]^2$.
-Unlike the incompressible example in \Cref{sec:res.1} a centered finite difference scheme of fourth order are used to discretize \eqref{eq:3.18}.
+Consider the 2-dimensional compressible Euler equation \eqref{eq:3.18} in a periodic square box $[0,1]^2$.
+Unlike the incompressible example in \Cref{sec:res.1}, a centered finite difference scheme of fourth order is used to discretize \eqref{eq:3.18}.
 The physical domain is discretized into a grid of $256\times 256$ nodes.
@@
 \\
-& \mathbf{u}_x = a \sin(4\pi y) \left( e^{-\dfrac{(y-0.25)^2}{2\sigma^2}} + e^{-\dfrac{(y-0.75)^2}{2\sigma^2}} \right)\\
+& \mathbf{u}_x = a \sin(4\pi y) \left( e^{-\dfrac{(y-0.25)^2}{2\sigma^2}} + e^{-\dfrac{(y-0.75)^2}{2\sigma^2}} \right),\\
 & \mathbf{u}_y = 
@@
 For specific choices of parameters describing the jets, fine structures and vortices emerges at the interface between the streams.
-Such instability is referred to as the Kelvin-Helmholtz instability \cite{HHS}.
+Such an instability is referred to as the Kelvin-Helmholtz instability \cite{HHS}.
 
-As centered finite difference schemes are dissipation free, resolving the discontinuous initial data requires application of an artificial viscosity.
+As centered schemes are often dissipation free, resolving the discontinuous initial data requires some artificial viscosity.
 In the high-fidelity model, the method discussed in \cite{artificial_dissipation} is used as an artificial viscosity.
-However, at the level of the reduced system, this is replaced with a low pass filter over the expansion coefficients of POD basis vectors.
+However, at the level of the reduced system, this is replaced with a low pass filter on the expansion coefficients of POD basis vectors.
 
-The fully discrete skew-symmetric form \eqref{eq:3.27} is used as a time marching scheme with $\Delta t = 5 \cdot 10^{-4}$, the time step, over a period of $1$ time unit.
+The fully discrete skew-symmetric form \eqref{eq:3.27} is used as a time marching scheme with $\Delta t = 5 \cdot 10^{-4}$ over a period of $1$ time unit.
 
-\Cref{fig:error_decay_KH} illustrates that the accuracy of the method is consistently increase as higher number of POD basis modes are considered.
+\Cref{fig:error_decay_KH} illustrates that the accuracy of the method consistently improves as a higher number of POD basis modes are considered.
 Furthermore, the skew-symmetric form preserves the accuracy over the period of time integration.
-It is observed from \Cref{fig:snap_solution_KH} that all features of the flow are correctly represented in the reduced system, even with a low number of basis vectors.
+It is observed in \Cref{fig:snap_solution_KH} that all features of the flow are correctly represented in the reduced system, even with a low number of basis vectors.
 
@@
 
-Conservation mass, momentum and energy is presented in \Cref{fig:conservation_DEIM}.
-The accuracy of the method in approximating these invariants is enhanced when the size of the basis is increased.
+Conservation of mass, momentum and energy is presented in \Cref{fig:conservation_DEIM}.
+The accuracy of the method in approximating these invariants improves as the size of the basis is increased.
 Furthermore, \Cref{energy_error_KH} shows how the kinetic energy associated with the reduced system mimic the kinetic energy of the high-fidelity system.
-This ensures the correct evolution of kinetic energy, and thus, the internal energy.
+This helps to ensure the correct evolution of kinetic energy, and thus, the internal energy.
 
-This helps with the correct distribution of the energy and ensures 
 \begin{figure}
@@
 In this section we study the 1-dimensional compressible Euler problem, \eqref{eq:3.18} without viscous terms, with a steady state discontinuous solution.
-This is in preparation for \Cref{sec:5.res.4}, where development and propagation of shock waves is expected.
-Here we asses how the skew-symmetric form for \eqref{eq:3.18} can recover moving discontinuities at the level of reduced system.
-Consider a periodic boundary conditions on $\Omega = [0,1]$ with the initial condition`
+This is in preparation for \Cref{sec:5.res.4}, where development and propagation of shock waves is discussed.
+Here we asses how the skew-symmetric form of \eqref{eq:3.18} can recover moving discontinuities at the level of the reduced system.
+Consider a periodic boundary conditions on $\Omega = [0,1]$ with the initial condition
 \begin{equation*}
@@
 \end{equation*}
-The domain is discretized into $N=2000$ nodes and centered finite differences scheme are used to assemble the discrete Euler equation in skew-symmetric form, as discussed in \Cref{sec:skew.3}.
+The domain is discretized into $N=2000$ nodes and a centered finite differences scheme are used to assemble the discrete Euler equation in skew-symmetric form, as discussed in \Cref{sec:skew.3}.
 
 The fully discrete skew-symmetric form \eqref{eq:3.27} is used for time integration over a time interval $[0,0.3]$.
-To resolve the discontinuous solution we consider an artificial viscosity with $\tau = \mu \partial u / \partial x$, where $\mu = 0.5 \cdot 10^{-4}$.
+To resolve the discontinuous solution we use an artificial viscosity with $\tau = \mu \partial u / \partial x$, where $\mu = 0.5 \cdot 10^{-4}$.
 
-\Cref{fig:energy_pres_1D} shows the conservation of conserved quantities for the high-fidelity and reduced system.
-Here, the high-fidelity model is also considered in the divergence and advective form to be compared with the skew-symmetric form.
-It is observed the reduced systems that are not in skew-symmetric form violate conservation of mass, momentum, and energy.
-Even as the high-fidelity systems in divergence and advective forms are stable, the constructed reduced system is unstable, even with very high number of basis vectors.
-On the other hand, it is seen that the skew-symmetric forms yield a stable and conservative reduce system.
-Note that the loss in the energy associated with the skew-symmetric form, seen in \Cref{conservation_1D_focus}, is due to the application of an artificial viscosity.
-Enriching the basis chosen for the  POD approximation leads to more accurate reduced solutions, as shown in \Cref{error_behaviour_1D}.
-In the same Figure, we observe that even though the reduced model manages to capture the discontinuity developed after half time units have been simulated, the accuracy is reduced of
-$2$ orders of magnitude.
-In \Cref{fig:snaps_1D_Euler}, snapshots of the reduced solution for different formulations are reported, showing the development of instabilities for non skew-symmetric formulations.
+		\Cref{fig:energy_pres_1D} shows the evolution of conserved quantities for the high-fidelity and reduced system.
+Here, the high-fidelity model is also considered in the divergence and advective form in addition to the skew-symmetric form.
+It is clear than when the reduced systems is not in skew-symmetric form, it violates conservation of mass, momentum, and energy.
+Even while the high-fidelity systems in divergence and advective forms are stable, the constructed reduced system is unstable, independent on the number of basis vectors.
+On the other hand, the skew-symmetric form yields a stable and conservative reduce system.
+Note that the loss in the energy associated with the skew-symmetric form, illustrated in \Cref{conservation_1D_focus}, is due to the application of an artificial viscosity.
 
-As discussed in \Cref{sec:mor_skew}, the DEIM approximation for evaluating nonlinear components of \eqref{eq:3.18} can affect the conservative properties of the skew-symmetric form.
+\Cref{error_behaviour_1D} shows the total error, when the reduced system captures a discontinuous solution at $t=0.16$.
+It is observed that the formation of a discontinuity affects the accuracy of the method.
+This is expected as a sharp gradient is approximated by a relatively few POD modes.
+However, the method remains robust and stable during the period of time integration.
+
+In \Cref{fig:snaps_1D_Euler} we compare the numerical artifacts of different formulations of the Euler equation.
+The advective formulation is not presented since it does not yield a stable reduced system.
+It is observed that the reduced system based on the skew-symmetric formulation accurately represent the overall behavior of the high-fidelity solution.
+On the other hand, a Gibbs-type error \cite{thompson1992fourier} appears near sharp gradients, for the reduced system based on the divergence form of the Euler equation.
+The well-representation of the skew-symmetric form is due the low aliasing error property.
+
+As discussed in \Cref{sec:mor_skew}, the DEIM approximation needed for efficient evaluation of the nonlinear components of \eqref{eq:3.18}, can affect the conservation properties of the skew-symmetric form.
 \Cref{fig:singular_values_decay_1D} shows the decay of the singular values of the nonlinear snapshots.
-It is observed that the decay of these snapshots is significantly slower than the temporal snapshots of \eqref{eq:3.18}.
+The decay of these snapshots is significantly slower than the temporal snapshots of \eqref{eq:3.18}.
 This indicates that to maintain the accuracy of the reduced system, the DEIM basis should be chosen richer than the POD basis.
 \Cref{error_DEIM} and \Cref{energy_DEIM} present the error and the conservation of total energy when the DEIM is used to approximate the nonlinear term.
-It is observed that the conservation of energy is recovered once DEIM approximates the nonlinear terms with enough accuracy.
+The conservation of energy is recovered once DEIM approximates the nonlinear terms with enough accuracy.
 While straightforward POD reduction does not offer a significative speed up if compared to the solution of the original high-dimensional nonlinear system of equations, with the DEIM treatment of nonlinearity solvers of the reduced models are of the order of tens faster than high fidelity solvers.

### 2018-07-17 sections/5.res.tex
Update remaining figures Nicolo

--- 2018-07-16 sections/5.res.tex
@@
   \begin{tikzpicture}[scale=0.58]
-    \begin{axis}[ylabel=$E_K(t)$,
+    \begin{axis}[ylabel=$K$,
                  xlabel=$t$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=south west,
@@
                  xlabel=Basis POD,
-                 label style={font=\large},
+                 label style={font=\Large},
                  %legend pos=north east,
@@
                  xlabel=$t$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend style={font=\large},
@@
                  xlabel=$t$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=south west,
@@
                  ylabel=$e(t)$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=outer north east,
@@
   \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[ylabel = $\left|\mathbf{1}^T(\mathbf{r}-\mathbf{r}^r)(t)\right|$,
+    \begin{semilogyaxis}[ylabel = error in mass,
                  xlabel=$t$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=north east,
@@
   \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[ylabel = $\left|(\mathbf{r}^{T}\mathbf{u}-\mathbf{r}^{rT}\mathbf{u}^{r})(t)\right|$,
+    \begin{semilogyaxis}[ylabel = error in total momentum,
                  xlabel=$t$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=north east,
@@
   \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[ylabel = $\left| \dfrac{1}{2}\left( \mathbf{u}^{rT}\mathbf{R}^r\mathbf{u}^r-\mathbf{u}^{T}\mathbf{R}\mathbf{u}\right)\right|$,
+    \begin{semilogyaxis}[ylabel = error in total energy,
                  xlabel=$t$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=north east,
@@
                  xlabel=$t$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=north east,
@@
     \begin{axis}[xlabel=$t$,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=south west,
@@
                  xlabel=Basis,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend style={font=\large},
@@
                  scale only axis,
-                 samples = 100]
+                 samples = 100,
+                 xtick = {400, 800, 1200, 1600}]
                  \addplot[color=black,style=solid,style=ultra thick]  table[x = n, y = sing_values] {./data/Compressible_Euler/1D/Singular_values/sv.txt};
@@
                  xlabel=Basis DEIM,
-                 label style={font=\large},
+                 label style={font=\Large},
                  legend pos=north east,
@@
                  height=1\linewidth,
-                 minor x tick num=1,
+%                 minor x tick num=1,
                  minor y tick num=2,	
+                 xticklabel style={font = \large},
 %                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},

### 2018-07-17 sections/5.res_part2.tex
Update remaining figures Nicolo

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%% Combustor images %%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
 \centering
-	\includegraphics[width=0.8\linewidth]{pic/radius}
+\begin{tikzpicture}[]
+    \begin{axis}[width=12cm,
+                 height=4cm,
+                 ylabel = $r(m)$,
+                 xlabel=$x(m)$,
+                 yticklabel style={
+                  /pgf/number format/fixed,
+                  /pgf/number format/precision=5,
+                  style = {font=\normalsize}
+                  },
+                 xticklabel style={
+                  style = {font=\normalsize}
+                  },
+%                 label style={font=\large},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=0.7\linewidth, 
+%                 height=0.5\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 scaled y ticks = false,
+%                 enlargelimits=false,
+%                 samples = 100,
+                 ymax = 0.04]
+                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = radius] {./data/Combustor/radius_combustor.txt};
+                \node[pin=100:{injector}] at (-0.05,0.01) {};
+                \node[pin=93:{back-step}] at (0.001,0.015) {};
+                \node[pin=90:{chamber}] at (0.2,0.023) {};
+                \node[pin=80:{nozzle}] at (0.4,0.015) {};
+    \end{axis}
+\end{tikzpicture}
 \caption{Geometry of quasi-1D CVRC model.}
@@
 The three-stage Runge-Kutta (SSP RK3) \cite{jiang1996efficient} is used to then integrate \eqref{eq:5p2.10} in time.
-The pressure profile for the steady state, with $q'=0$, and the pressure oscillatory mode in the unsteady phase is presented in \Cref{fig:5p2.2a}.
+The pressure profile for the steady state, with $q'=0$, and the pressure oscillatory mode in the unsteady phase is presented in \Cref{steady_state}.
 We report that the added viscous term affects the level of pressure in the steady state and the aplitude of oscilations in the unsteady mode, compared to \cite{Wang:255719}.
 
-\begin{figure}[t]
-\centering
-\begin{subfigure}[]{0.47\linewidth}
-	\includegraphics[width=\textwidth]{./pic/init_pressure}
-	\caption{} \label{fig:5p2.2a}
-\end{subfigure}
-\begin{subfigure}[]{0.47\linewidth}
-	\includegraphics[width=\textwidth]{./pic/init_osc}
-	\caption{} \label{fig:5p2.2b}
-\end{subfigure} \\
-\begin{subfigure}[]{0.47\linewidth}
-	\includegraphics[width=\textwidth]{./pic/p_error}
-	\caption{} \label{fig:5p2.2c}
-\end{subfigure}
-\begin{subfigure}[]{0.47\linewidth}
-	\includegraphics[width=\textwidth]{./pic/rom_freq}
-	\caption{} \label{fig:5p2.2d}
-\end{subfigure}
-\caption{(a) Pressure profile of the steady state.
+%\begin{figure}[t]
+%\centering
+%\begin{subfigure}[]{0.47\linewidth}
+%	\includegraphics[width=\textwidth]{./pic/init_pressure}
+%	\caption{} \label{fig:5p2.2a}
+%\end{subfigure}
+%\begin{subfigure}[]{0.47\linewidth}
+%	\includegraphics[width=\textwidth]{./pic/init_osc}
+%	\caption{} \label{fig:5p2.2b}
+%\end{subfigure} \\
+%\begin{subfigure}[]{0.47\linewidth}
+%	\includegraphics[width=\textwidth]{./pic/p_error}
+%	\caption{} \label{fig:5p2.2c}
+%\end{subfigure}
+%\begin{subfigure}[]{0.47\linewidth}
+%	\includegraphics[width=\textwidth]{./pic/rom_freq}
+%	\caption{} \label{fig:5p2.2d}
+%\end{subfigure}
+%\caption{(a) Pressure profile of the steady state.
 (b) Oscillatory mode of pressure located at $x=0.36$ for the unsteady flow.
@@
 }
+%\label{fig:5p2.2}
+%\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%% Combustor %%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  % Pressure steady
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{axis}[ylabel = pressure $p$,
+                 xlabel=$x$,
+                 label style={font=\Large},
+                 legend pos=north east,
+                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+%                 ymin=0,
+                 ymax = 1500000,
+                 samples = 100]
+                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = x, y = pressure] {./data/Combustor/pressure_steady_state.txt};
+    \end{axis}%  
+  \end{tikzpicture}
+  \caption{}
+  \label{steady_state}
+  \end{subfigure}\hfill% 
+  % Pressure oscilaltions
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{axis}[ylabel = pressure $p$,
+                 xlabel=$t$,
+                 label style={font=\Large},
+                 legend pos=north east,
+                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 scaled y ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 ymin=0,
+%                 samples = 100,
+                 xmax = 0.06,
+                 ymin = 1360000,
+                 ymax = 1460000,
+                 tick label style={/pgf/number format/fixed} ]
+                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = pressure] {./data/Combustor/ciao.txt};
+    \end{axis}%  
+  \end{tikzpicture}
+  \caption{}
+  \label{oscill_pressure}
+  \end{subfigure}
+
+% Total momentum
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{semilogyaxis}[ylabel = $\| p-\tilde{p}\|_2$,
+                 xlabel=$t$,
+                 label style={font=\Large},
+                 legend pos=south east,
+                 legend entries={$k=200$,$k=300$,$k=300$},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 scaled y ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 samples = 300,
+                 ymin = 0.000001,
+                 ymax = 0.0001]
+                 \addplot[color=red,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_200.txt};
+                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_300.txt};
+                 \addplot[color=black!50!green,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_400.txt};
+    \end{semilogyaxis}%  
+  \end{tikzpicture}
+  \caption{}
+  \label{error_growth_comb}
+  \end{subfigure}\hfill% 
+  % Pressure reduction  
+  \begin{subfigure}[]{0.48\linewidth}
+  \begin{tikzpicture}[scale=0.55]
+    \begin{axis}[ylabel = pressure $p$,
+                 xlabel=$t$,
+                 label style={font=\Large},
+                 legend pos=north east,
+                 legend entries={High fidelity,  POD with $k=200$},
+                 legend style={font=\large},
+                 grid=both,
+                 ticks=both,
+                 width=1.4\linewidth, 
+                 height=1.0\linewidth,
+                 minor x tick num=1,
+                 minor y tick num=2,	
+                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+                 scaled x ticks = true,
+                 enlargelimits=false,
+                 scale only axis,
+                 xmin = 0.9,
+                 xmax = 0.98,
+                 ymin = 1390000,
+                 ymax = 1450000,
+                 tick label style={/pgf/number format/fixed} ]
+                 \addplot[color=green,style=solid,style=ultra thick]  table[x = t, y = pressure] {./data/Combustor/full.txt};
+                 \addplot[color=black,style=dashed,style=thick]  table[x = t, y = pressure] {./data/Combustor/red.txt};
+    \end{axis}%  
+  \end{tikzpicture}
+  \caption{}
+  \label{oscill_focus}
+  \end{subfigure}
+  \caption{(\protect\subref{steady_state}) Pressure profile of the steady state.
+(\protect\subref{oscill_pressure}) Oscillatory mode of pressure located at $x=0.36$ for the unsteady flow.
+(\protect\subref{error_growth_comb}) Relative error between the high-fidelity and approximated pressure.
+(\protect\subref{oscill_focus}) Approximation of the oscillations.}
   \label{fig:5p2.2}
@@
 
-The discontinuities that appear in the solution of \eqref{eq:5p2.10} suggests that a, relatively, large basis is required to resolve fine strucutres in the solution.
+The discontinuities that appear in the solution of \eqref{eq:5p2.10} suggests that a, relatively, large basis is required to resolve fine structures in the solution.
 In this paper, a POD basis is generated with $k=200$, $k=300$ and $k=400$ number of basis vectors.
@@
 
-\Cref{fig:5p2.2c} shows the approximation error of the pressure, due to MOR.
+\Cref{error_growth_comb} shows the approximation error of the pressure, due to MOR.
 It is observed that the approximation is coherently enhanced as the number of basis vectors are increase.
 Furthermore, the approximated solution maintains high accuracy over a relatively long time-integration.
-The oscilations of pressure is demostrated in \Cref{fig:5p2.2d}.
+The oscilations of pressure is demostrated in \Cref{oscill_focus}.
 It is seen that the overall behaviour of pressure is well approximated using the reduced system.

### 2018-07-17 sections/2.mor.tex

@@
 When $\mathcal M_u$ has a low-dimensional representation, it is referred to as \emph{reducible}.
-Assume that $\mathcal M_u$ can be well approximated by $k$-dimensional linear subspace $\mathcal V_k$, with $k\ll n$ and let $E_k = \{ v_1,\dots,v_k \}$ be the basis vectors for $\mathcal V_k$ and $V_k$ the basis matrix that contains these vectors in its columns.
-A reduced basis (RB) method assumes that $u \approx \tilde u = V_k v$, where $v$ is the expansion coefficients of $\tilde u$ in the basis $E_k$.
+Assume that $\mathcal M_u$ can be well approximated by a $k$-dimensional linear subspace $\mathcal V_k$, with $k\ll n$ and let $E_k = \{ v_1,\dots,v_k \}$ be the basis vectors for $\mathcal V_k$ and $V_k$ the basis matrix that contains these vectors in its columns.
+A reduced basis (RB) method assumes that $u \approx \tilde u = V_k v$, where $v\in \mathbb R^{k}$ is the expansion coefficients of $\tilde u$ in the basis $V_k$.
 Substituting this into \eqref{eq:1} yields
@@
 One can construct a projection operator $P_{\mathcal V_{k},\mathcal W_k}$ that projects elements of $\mathbb R^{n}$ onto $\mathcal V_k$, orthogonal to $\mathcal W_k$ as $P_{\mathcal V_{k},\mathcal W_k} = V_k(W_k^TV_k)^{-1}W_k^T$, where $W_k$ is the basis matrix that contains the basis vectors of $\mathcal W_k$ in its columns and $W_k^TV_k$ is assumed to be invertible.
-With this projection, \eqref{eq:1} reduces to
+With this projection, \eqref{eq:1} reduces to the $k$-dimensional problem
 \begin{equation} \label{eq:4}
@@
 When we require $W_k=V_k$, then \eqref{eq:4} is referred to as the \emph{Galerkin} projection of \eqref{eq:1} onto $\mathcal V_k$.
-Since \eqref{eq:4} has a smaller size, as compared to \eqref{eq:1}, one can expect accelerated evaluation.
+Since \eqref{eq:4} has a smaller size, as compared to \eqref{eq:1}, one can expect an accelerated evaluation.
 To numerically identify the best possible subspace $\mathcal V_{k}$ we first discretize the solution manifold to obtain
@@
 \end{equation}
-Members of $M_{u}^{\Delta}$ are referred to as \emph{snapshots} of \eqref{eq:1}.
-One can obtain these snapshots by applying a time-integration scheme, e.g.
-the Runge-Kutta methods, to \eqref{eq:1} to obtain $\tilde {\mathcal M}_{u}^{\Delta}$ an approximation to $\mathcal M_{u}^{\Delta}$.
-Throughout this paper, we assume that we can choose $\tilde{\mathcal M}_{u}^{\Delta}$ arbitrary close to $\mathcal M_{u}^{\Delta}$, therefore, by an abuse of notation, we may drop the overscript ``\textasciitilde''.
+Members of $\mathcal M_{u}^{\Delta}$ are referred to as \emph{snapshots} of \eqref{eq:1}.
+One can obtain these snapshots by applying a time-integration scheme, e.g., the Runge-Kutta methods, to \eqref{eq:1} to obtain $\tilde {\mathcal M}_{u}^{\Delta}$ as an approximation to $\mathcal M_{u}^{\Delta}$.
+Throughout this paper, we assume that we can choose $\tilde{\mathcal M}_{u}^{\Delta}$ arbitrary close to $\mathcal M_{u}^{\Delta}$.
+By an abuse of notation, we drop the overscript ``\textasciitilde''.
 For a Galerkin projection, the best possible basis $V_k$ is the one that minimizes the collective projection error \cite{hesthaven2015certified}, i.e., the solution to the minimization problem
@@
 Note that the constraint in \eqref{eq:6} requires $V_k$ to be orthonormal.
-The basis matrix $V_k$ that solves the minimization problem \eqref{eq:6} is referred to as the \emph{proper orthogonal decomposition} (POD) of $S$ of size $k$ \cite{hesthaven2015certified}, and according to the Schmidt-Mirsky theorem, can be constructed using the left singular vectors of $S$ as
+The basis matrix $V_k$ that solves the minimization problem \eqref{eq:6} is referred to as the \emph{proper orthogonal decomposition} (POD) of $S$ of size $k$ \cite{hesthaven2015certified} and, according to the Schmidt-Mirsky theorem, can be constructed using the left singular vectors of $S$ as
 \begin{equation}
@@
 
-Often MOR is studied in the parametric setting, where the vector $u,u_0$, and the right hand side function $f$ of \eqref{eq:1} are of the form $u(t;\mu)$, $u_0(\mu)$, and $f(t,u;\mu)$, respectively.
+Model order reduction is often studied in the parametric setting, where the vector $u,u_0$, and the right hand side function $f$ of \eqref{eq:1} are of the form $u(t;\mu)$, $u_0(\mu)$, and $f(t,u;\mu)$, respectively.
 Here $\mu$ belongs to $\mathbb P$, a closed subset of $\mathbb R^d$.
-In this case, the reduced system can approximate the quantities of interest at an accelerated rate.
+In this case, the reduced system can recover quantities of interest at low cost.
 Since the nature of time, as a parameter, is different from other spacial and physical parameters, in this paper we solely focus on $t$ as the parameter.
-Nevertheless, it is straight forward to extend the results of this paper to the parameter setting by using POD in time and parameter space, or by using the POD-greedy \cite{haasdonk2013convergence,hesthaven2015certified,quarteroni2015reduced} method to generate a basis $V_k$.
+Nevertheless, it is straight forward to extend the results of this paper to the parameter setting by using POD in time and parametric space, or by using the POD-greedy \cite{haasdonk2013convergence,hesthaven2015certified,quarteroni2015reduced} method to generate a basis $V_k$.
 
-Since the approximated solution $\tilde u$ is a linear combination of the POD basis vectors, $\tilde u$ inherits linear properties of these basis vectors.
+Since the approximate solution $\tilde u$ is a linear combination of the POD basis vectors, $\tilde u$ inherits linear properties of these basis vectors.
 However, when the solution $u$ to \eqref{eq:1} satisfies some nonlinear invariants, there is no guarantee that, in general, $\tilde u$ also satisfy such invariants \cite{doi:10.1137/140959602,doi:10.1137/140978922,doi:10.1137/17M1111991,MaboudiAfkham2018}.
-This results in a qualitatively wrong and often unstable solution.
+This results in a qualitatively wrong and often unstable solution to \eqref{eq:4}.
 In the later sections, we discuss how the skew-symmetric formulation of the fluid flow allows conservation of quadratic invariants, e.g.

### 2018-07-17 sections/3.skew.tex

@@
 
-In this section we summarize the conservative properties of skew-symmetric forms and discretization schemes, following, closely, the works of \cite{morinishi2010skew,morinishi1998fully,reiss2014conservative}.
+In this section we summarize the conservation properties of skew-symmetric forms and discretization schemes, following, closely, the works of \cite{morinishi2010skew,morinishi1998fully,reiss2014conservative}.
 
 \subsection{Conservation Laws} \label{sec:skew.1}
-Transport of conserved quantities, in the context of fluid flows, can be formulated as
+In the context of fluid flows, transport of conserved quantities, can be expressed as
 \begin{equation} \label{eq:3.1}
@@
 in case where $\Omega$ is periodic and $\varphi$ is flux-free, the quantity $(\rho \varphi)$ is conserved.
-Therefore, the form \eqref{eq:3.1} is referred to the \emph{conservative form} and the convective term in \eqref{eq:3.1} is referred to as the \emph{divergence form}.
+Therefore, \eqref{eq:3.1} is referred to as the \emph{conservative form} and the convective term in \eqref{eq:3.1} is referred to as the \emph{divergence form}.
 However, using the \emph{continuity equation}
@@
 The convective term in this formulation is referred to as the \emph{advective form}.
-The \emph{skew-symmetric} form for the convective term is obtained by the arithmetic average of the divergent and the advective form:
+The \emph{skew-symmetric} form of the convective term is obtained by the arithmetic average of the divergent and the advective form:
 \begin{equation} \label{eq:3.5}
@@
 Therefore, $\varphi^2$ is a conserved quantity for a flux-free $\varphi$.
-Since the divergence, the advective and the skew-symmetric forms are identical at the continuous level, then $\varphi^2$ is a conserved quantity for all forms.
-However, equivalence of these forms is not preserved through a general discretization scheme and, therefore, we do not expect $\varphi^2$ to be a conserved quantity at the discrete level.
+Since the divergence, the advective and the skew-symmetric forms are identical at the continuous level, $\varphi^2$ is a conserved quantity for all forms.
+However, the equivalence of these forms is not preserved through a general discretization scheme and we can not expect $\varphi^2$ to be a conserved quantity at the discrete level.
 To motivate numerical advantages of the skew-symmetric form consider the operator
@@
 \end{equation}
-With a proper set of boundary condition, this operator is a skew-adjoint operator with respect to the $L^2$ inner-product.
-Here, $[\cdot]$ indicates that the inside of brackets act as a differential operator.
-This skew-adjoint property is used in later sections to show the conservation of some quadratic quantities in \eqref{eq:3.1}.
+With a proper set of boundary condition, this operator is a skew-adjoint operator on $L^2$.
+Here, $[\cdot]$ indicates that the inside of the brackets act as a differential operator.
+This skew-adjoint property is used later to show the conservation of some quadratic quantities in \eqref{eq:3.1}.
 Similarly, we can define a skew-adjoint operator with respect to the time variable as
@@
 Here, the subscript $\partial t$ is to emphasize that $S_{\rho,\partial_t}$ is a differential operator with respect to $t$.
-A proper time and space integration of $S_{\rho u}$ and $S_{\rho,\partial_t}$, usually with centered discretization schemes, can preserve the skewness property.
+A proper time and space discretization of $S_{\rho u}$ and $S_{\rho,\partial_t}$ can preserve the skewness property.
 
-Numerical time integration of \eqref{eq:3.5} can be challenging since the time differentiation of different variable is present.
-However, following derivations in \cite{morinishi2010skew}, one can rewrite \eqref{eq:3.5} as
+Numerical time integration of \eqref{eq:3.5} can be challenging since the time differentiation of different variables is present. Following \cite{morinishi2010skew}, we rewrite \eqref{eq:3.5} as
 \begin{equation} \label{eq:3.6}
@@
 \end{equation}
-Time integration of this form is presented in the works of \cite{morinishi2010skew,reiss2014conservative}.
+Time integration of this form is presented in \cite{morinishi2010skew,reiss2014conservative}.
 Note that one can also generate a quasi-skew-symmetric form \cite{blaisdell1991numerical,morinishi2003dns} of \eqref{eq:3.1} as
@@
 \end{equation}
-Even though this is not a fully skew-symmetric form (skew-symmetric only in space), the numerical stabilities of this form is significantly better than the divergence and advective form \cite{morinishi2010skew,blaisdell1991numerical,morinishi2003dns}.
-Note that the quasi-skew-symmetric form is identical to the skew-symmetric form in the incompressible limit.
+Even though this is not a fully skew-symmetric form (skew-symmetric only in space), the numerical stability of this form is significantly better than the divergence and advective form \cite{morinishi2010skew,blaisdell1991numerical,morinishi2003dns}.
+Note that this quasi-skew-symmetric form is identical to the skew-symmetric form in the incompressible limit.
 
@@
 \end{equation}
-where $K = \frac 1 2 \sum_{i=1}^d u_i^2 $ is the kinetic energy. Here we used 
-\begin{equation} \label{eq:3.10}
-	\begin{aligned}
-	u\cdot \nabla p &= \nabla \cdot (up) - p\nabla \cdot u, \\
-	u \cdot (\nabla \cdot \tau) &= \nabla \cdot (\tau u) - (\tau \nabla)\cdot u,
-	\end{aligned} 
-\end{equation}
-and
+where $K = \frac 1 2 \sum_{i=1}^d u_i^2 $ is the kinetic energy and we used 
 \begin{equation} \label{eq:3.11}
@@
 Thus, kinetic energy is conserved for all forms.
-However, for a general discretization scheme, these forms are not identical, and often the conservation of kinetic energy, in the discrete sense, is violated.
+However, for a general discretization scheme, these forms are not identical and often conservation of kinetic energy (in the discrete sense) may be violated.
 
-The skew-symmetric discretization of \eqref{eq:3.8} is a centered scheme that exploits the skew-adjoint property of $S_u$, and ensures conservation of kinetic energy at the discrete level.
+A skew-symmetric discretization of \eqref{eq:3.8} is a centered scheme that exploits the skew-adjoint property of $S_u$, and ensures conservation of kinetic energy at the discrete level.
 We uniformly discretize $\Omega$ into $N$ points and denote by $\mathbf u \in \mathbb R^{N\times d}$, $\mathbf p \in \mathbb R^N$, and $T \in R^{N\times d\times d} $ the discrete representation of $u$, $p$, and $\tau$, respectively.
-Let $D_j$ be the centered finite difference matrix operator for $\partial / \partial x_j$, and for $j = 1,\dots,d$.
-The momentum equation in \eqref{eq:3.8} is then discretized as
+Let $D_j$ be the centered finite difference scheme for $\partial / \partial x_j$, and for $j = 1,\dots,d$.
+The momentum equation in \eqref{eq:3.8} is discretized as
 \begin{equation} \label{eq:3.13}
@@
 \end{enumerate}
-Condition 1 and 2 yield
+Conditions 1 and 2 yield
 \begin{equation} \label{eq:3.15}
@@
 \end{equation}
-Conservation of momentum in the discrete sense reads
+Conservation of momentum in the discrete sense is expressed as
 \begin{equation} \label{eq:3.16}
@@
 \end{equation}
-Similarly, using \eqref{eq:3.10}, it is verified that
+Similarly, it is verified that
 \begin{equation} \label{eq:3.17}
@@
 \end{equation}
-
-Conditions 1 and 2 for $D_i$ can be easily checked for a centered finite differences scheme on a periodic domain.
-For other types of boundaries, e.g., wall boundary and inflow/outflow, we refer the reader to \cite{morinishi1998fully,desjardins2008high} for construction of the proper discrete centered differentiation operator.
+Conditions 1 and 2 for $D_i$ are easily checked for a centered finite differences scheme on a periodic domain.
+For other types of boundaries, e.g., wall boundary and inflow/outflow, we refer the reader to \cite{morinishi1998fully,desjardins2008high} for the construction of the proper discrete centered differentiation operator.
+We note that the finite differences schemes are chosen here for illustration purposes.
+It is easily checked that any discrete differentiation operator that satisfies discrete integration by parts, e.g.
+summation by part (SBP) methods and discontinuous Galerkin (DG) methods, also satisfies conditions 1 and 2 and can be used to construct a skew-symmetric discretization.
 
 \subsection{Compressible Fluid} \label{sec:skew.3}
-Consider the equation governing the evolution of a compressible fluid in a skew-symmetric form in one spacial dimension
+Consider the equations governing the evolution of a compressible fluid in a skew-symmetric form in one spacial dimension
 \begin{equation} \label{eq:3.18}
@@
 \end{equation}
-Here $E= e + u^2/2$ is the total energy per unit mass, with $e = \frac{p}{\rho(\gamma - 1)}$ the internal energy, $\gamma$ the adiabatic gas index, and $\phi = -\lambda \frac{\partial T}{\partial x}$ is the heat flux, with $\lambda$ the heat conductivity.
-The rest of the variables are the same as those discussed in \Cref{sec:skew.2}.
-Following \cite{reiss2014conservative}, the evolution of the momentum equation reads
+Here $E= e + u^2/2$ is the total energy per unit mass, with $e = {p}/{\rho(\gamma - 1)}$ being the internal energy, $\gamma$ the adiabatic gas index, and $\phi = -\lambda \frac{\partial T}{\partial x}$ is the heat flux, with $\lambda$ as the heat conductivity.
+The remaining variables are the same as those discussed in \Cref{sec:skew.2}.
+Following \cite{reiss2014conservative}, the evolution of the momentum equation is
 \begin{equation} \label{eq:3.19}
@@
 \end{equation}
-Substituting this into the energy equation in \eqref{eq:3.18} while assuming a constant adiabatic index yields
+Substituting this into the energy equation in \eqref{eq:3.18}, while assuming a constant adiabatic index, yields
 \begin{equation} \label{eq:3.20}
@@
 \end{equation}
-
 We discretize the real line, uniformly, into $N$ grid points and denote by $\mathbf r, \mathbf u, \mathbf p \in \mathbb R^{N}$, the discrete representations of $\rho$, $u$, and $p$, respectively.
 Using the matrix differentiation operator $D\in \mathbb R^{N\times N}$ (we omit the subscript ``$i$'' for the one dimensional case), introduced in \Cref{sec:skew.2}, we define the skew-symmetric matrix operator $S_{\mathbf r \mathbf u} = \frac 1 2 (DUR + RUD)$, where $R$ is the matrix that contains $r$ in its diagonal.
-Now, a semi-discretization of \eqref{eq:3.18} and \eqref{eq:3.20} takes the form
+Semi-discrete expression of \eqref{eq:3.18} and \eqref{eq:3.20} takes the form
 \begin{equation} \label{eq:3.21}
@@
 \end{equation}
-
-Considering conditions 1 and 2 for $D$, discussed in \Cref{sec:skew.2}, it is easily verified that
+Recalling conditions 1 and 2 for $D$, discussed in \Cref{sec:skew.2}, it is easily verified that
 \begin{equation} \label{eq:3.22}
@@
 \end{equation}
-Conservation of mass yields
+Conservation of mass is expressed as
 \begin{equation} \label{eq:3.23}
@@
 \end{equation}
-Here we used \eqref{eq:3.22} and the mass and the momentum equation in \eqref{eq:3.21}. Similarly, for the conservation of the total energy, we have
+Here we used \eqref{eq:3.22} and the mass and the momentum equation in \eqref{eq:3.21}. Similarly, for conservation of the total energy, we have
 \begin{equation} \label{eq:3.25}
@@
 \end{equation}
-In addition to the conservation of the total energy, skew-symmetric form of \eqref{eq:3.21} also conserves the evolutions of the kinetic energy:
+In addition to the conservation of the total energy, the skew-symmetric form of \eqref{eq:3.21} also conserves the evolutions of the kinetic energy:
 \begin{equation} \label{eq:3.26}
@@
 \end{equation}
-Here, we used the skew-symmetry of $S_{\mathbf r \mathbf u}$. Therefore, only the pressure and viscous terms contribute to a change in the level of kinetic energy.
+Here, we used the skew-symmetry of $S_{\mathbf r \mathbf u}$. Therefore, only the pressure and the viscous terms contribute to a change in the kinetic energy.
 
@@
 An entropy preserving skew-symmetric form can be found in \cite{sjogreen2010skew}.
-Furthermore, a fully quasi-skew-symmetric form for \eqref{eq:3.18}, where all quadratic fluxes are in a skew-symmetric form, is shown to have lowest aliasing error \cite{honein2004higher,honein2005numerical}
+Furthermore, a fully quasi-skew-symmetric form for \eqref{eq:3.18}, where all quadratic fluxes are in a skew-symmetric form, is shown to minimize aliasing errors \cite{honein2004higher,honein2005numerical}
 
 \subsection{Time integration}
-Following steps in \cite{reiss2014conservative,morinishi2010skew} we can construct a fully discrete scheme for \eqref{sec:skew.3} as
+Following \cite{reiss2014conservative,morinishi2010skew} we can construct a fully discrete second order accurate scheme for \eqref{sec:skew.3} as
 \begin{equation} \label{eq:3.27}
@@
 \end{equation}
-Here, $\Delta t$ is the time discretization unit, superscript $n$ denotes evaluating a variable at $t = n\Delta t$, superscript $n+1/2$ denotes the arithmetic average of a variable evaluated at $t=n\Delta t$ and $t=(n+1)\Delta t$, the square root sign denotes element-wise application of square root, and
+Here, $\Delta t$ is the time step, superscript $n$ denotes evaluating at $t = n\Delta t$, superscript $n+1/2$ denotes the arithmetic average of a variable evaluated at $t=n\Delta t$ and $t=(n+1)\Delta t$, the square root sign denotes element-wise application of square root, and
 \begin{equation}
@@
 \end{equation}
-It is discussed in \cite{reiss2014conservative} that this time discretization scheme preserves the symmetries expressed in \eqref{eq:3.17}, \eqref{eq:3.24}, \eqref{eq:3.25}, and \eqref{eq:3.26}.
+As discussed in \cite{reiss2014conservative}, this time discretization scheme preserves the symmetries expressed in \eqref{eq:3.17}, \eqref{eq:3.24}, \eqref{eq:3.25}, and \eqref{eq:3.26}.
 In the incompressible case, the method reduces to the implicit mid-point scheme \cite{hairer2006geometric}.

### 2018-07-17 sections/1.intro.tex
all corrections added, a backupfile included

@@
 
-Constructing MOR techniques and RB methods that preserve intrinsic structures has recently attracted attention \cite{doi:10.1137/17M1111991,1705.00498,kalashnikova2014stabilization,farhat2015structure,doi:10.1137/110836742,beattie2011structure,doi:10.1137/140978922}.
+Constructing MOR techniques and RB methods that preserve intrinsic structures has recently attracted attention \cite{doi:10.1137/17M1111991,kalashnikova2014stabilization,farhat2015structure,doi:10.1137/110836742,beattie2011structure,doi:10.1137/140978922}.
 Structure preservation can recover a physically meaningful reduced model, rather than a pure algebraic coupling of equations.
 This enforces robustness and can help with the stability of the reduced model.
-Preserving time-symmetries of Lagrangian, Hamiltonian, and port-Hamiltonian systems can be found in the works of \cite{Carlberg:2014ky,doi:10.1137/140978922,doi:10.1137/17M1111991,1705.00498,beattie2011structure,chaturantabut2016structure,gugercin2012structure}.
+Preserving time-symmetries of Lagrangian, Hamiltonian, and port-Hamiltonian systems can be found in the works of \cite{Carlberg:2014ky,doi:10.1137/140978922,doi:10.1137/17M1111991,beattie2011structure,chaturantabut2016structure,gugercin2012structure}.
 Conserving inf-sup stability, in the context of finite element methods, can be found in \cite{farhat2015structure,ballarin2015supremizer}.
@@
 Combined wirh centered time and space discretization schemes, typically a finite differences discretization method, they recover time-symmetries of a fluid at the discrete level.
-Such discretization schemes are studies comprehensively over the past few decades and can be found in the works of \cite{morinishi2010skew,morinishi1998fully,desjardins2008high,reiss2014conservative,reiss2014conservative} and the references therein.
+Such discretization schemes are studies comprehensively over the past few decades and can be found in the works of \cite{morinishi2010skew,morinishi1998fully,desjardins2008high,tadmor1984skew,reiss2014conservative,reiss2014conservative} and the references therein.
 
@@
 Therefore, a proper time stepping scheme preserves the reduced representation of the energy, and therefore, the loss in energy due to model reduction remains constant in time.
+Furthermore, we demonstrate, through numerical experiments, that a quasi-skew-symmetric form of fluid flow, i.e.
+a formulation where only spacial differential operators are in a skew-symmetric form, offer remarkable stability properties in terms of MOR.
+This allows an explicit time-integration to be utilized while recovering robustness of skew-symmetric forms at the reduced level.
 

### 2018-07-17 sections/3.skew.tex
all corrections added, a backupfile included

@@
 
-In this section we summarize the conservation properties of skew-symmetric forms and discretization schemes, following, closely, the works of \cite{morinishi2010skew,morinishi1998fully,reiss2014conservative}.
+In this section we summarize the conservation properties of skew-symmetric forms and discretization schemes, following, closely, the works of \cite{morinishi2010skew,morinishi1998fully,tadmor1984skew,reiss2014conservative}.
 

### 2018-07-17 sections/5.res_part2.tex
all corrections added, a backupfile included

@@
 
-CVRC is a model rocket combustor designed and operated at Purdue University (Indiana, U.S.) to investigate combustion instabilities \cite{yu2008combustion}.
+CVRC is a model rocket combustor, designed and operated at Purdue University (Indiana, U.S.) to investigate combustion instabilities \cite{yu2008combustion}.
 This setup is called the Continuously Variable Resonance Combustor (CVRC) because the length of the oxidizer injector can be varied continuously, allowing for a detailed investigation of the coupling between acoustics and combustion in the chamber \cite{garby2013simulations}.
@@
 \ref{fig:radius}.
-The oxidizer is injected from the left end of the oxidizer post and meets the fuel that is injected through an annular ring around the oxidizer injector, at the back-step.
+The oxidizer is injected from the left end of the oxidizer post and meets the fuel, injected through an annular ring around the oxidizer injector, at the back-step.
 The combustion happens in a region around the back-step.
@@
 Both the injector and the nozzle are operated at choked condition during the experiment.
-The length of the oxidizer post $L_{op}$ of the CVRC can be varied continuously, leading to different behavior of the combustion stability.
-In this paper, we will focus on the case with $L_{op}= 14.0$ cm, in which the combustion is unstable.
+The length of the oxidizer post $L_{op}$ of the CVRC can be varied continuously, leading to different dynamics.
+Here, we focus on the case with $L_{op}= 14.0$ cm, in which the combustion is unstable.
 
 The geometry parameters of the quasi-1D CVRC with a oxidizer post length  $L_{op}= 14.0$ cm are shown in Table \ref{tab:geometry_parameters}.
-The back-step and the converging part of the nozzle are sinusoidally contoured to avoid discontinuity of the radius that will invalidate the quasi-1D governing equations presented in the next subsection.
+The back-step and the converging part of the nozzle are sinusoidally contoured to avoid a discontinuity of the radius that will invalidate the quasi-1D governing equations presented in the next subsection.
 
@@
 \end{table}
-
 The fuel is pure gaseous methane.
 The oxidizer is a mixture of 42\% oxygen and 58\% water (per unit mass).
-The oxidizer is injected in the oxidizer post at a temperature $T_{ox}=1030$ K so that both water and oxygen are in the gaseous phase.
+And is injected in the oxidizer post at a temperature $T_{ox}=1030$ K so that both water and oxygen are in the gaseous phase.
 The operating conditions are listed in Table \ref{tab:operating-conditions}.
@@
 \end{table}
-
 For the combustion, we consider the one-step reaction model
@@
 \end{equation}
-where $\rho$ is the density, $u$ is the velocity, $p$ is the pressure, $E$ is the total energy, $Y_{ox}$ is the mass fraction of oxidizer, and $A=A(x)$ is the cross section area of the duct.
+where $\rho$ is the density, $u$ is the velocity, $p$ is the pressure, $E$ is the total energy, $Y_{ox}$ is the mass fraction of oxidizer, and $A=A(x)$ is the cross sectional area of the duct.
 The pressure $p$ can be computed using the conserved variables as
@@
 \end{equation}
-where $T_{ref}$ is the reference temperature and is set as 298.15 K in this paper.
+where $T_{ref}$ is the reference temperature and is set as 298.15 K.
 The temperature $T$ is recovered from the equation of state $p = \rho R T$.
@@
 The unsteady heat release term $q'$, also called the combustion response function, models the coupling between acoustics and combustion.
-In this paper, we use the combustion response function designed by Frezzotti et al.
-\cite{frezzotti2017numerical,frezzotti2018quasi}, which is a function of the velocity, sampled at specific abscissa $\hat{x}$ that is almost coincident with the antinode of the first longitudinal modal shape, with a certain time lag $t_0$, i.e.,
+Here, we use the combustion response function designed by Frezzotti et al.
+\cite{frezzotti2017numerical,frezzotti2018quasi}, which is a function of the velocity, sampled at specific abscissa $\hat{x}$ that is almost coincident with the antinode of the first longitudinal modal shape with a time lag $t_0$, i.e.,
 \begin{equation}\label{eq:5p2.7}
@@
 \begin{equation}\label{eq:5p2.8}
-g\left(x\right)= \frac{e^{-\frac{\left(x-\mu\right)^2}{2\sigma^2}}}{\sqrt{2\pi\sigma^2}},
+g\left(x\right)= \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left( -\frac{\left(x-\mu\right)^2}{2\sigma^2} \right),
 \end{equation}
-where $\mu$ is the mean and $\sigma$ is the standard deviation. The amount of heat release due to velocity oscillations is controlled by the parameter $\alpha$.
+where $\mu$ is the mean and $\sigma$ is the standard deviation. The amount of heat release due to velocity oscillations is controlled by the parameter $\alpha$, in \eqref{eq:5p2.7}.
 
@@
 
-Prior to unsteady simulation, the quasi-1D CVRC needs to be excited, which can be achieved by adding a perturbation to the steady-state solution.
+Prior to the unsteady simulation, the quasi-1D CVRC needs to be excited, which is achieved by adding a perturbation to the steady-state solution.
 The perturbation is added by forcing the mass flow rate with a multi-sine signal
@@
 \end{enumerate}
-
-Note that the right hand side in \eqref{eq:5p2.3} suggests that, in general, mass, momentum, and energy is not conserved.
-Furthermore, the complex coupling of the variables in \eqref{eq:5p2.3} prohibits the application of complex and implicit time integration schemes.
-Therefore, a quasi-skew-symmetric form, introduced in \eqref{eq:3.7}, is considered for \eqref{eq:5p2.3}.
-This allows us to benefit from stability properties of skew-symmetric forms while using an explicit time integration scheme.
-
 Introduction of an artificial viscosity is essential for a robust and long time-integration of \eqref{eq:5p2.3}.
-Common discretization schemes for \eqref{eq:5p2.3} are often dissipative, e.g.
-the Lax-Friedrich scheme used in \cite{Wang:255719}.
-Since the skew-symmetric discretization is non-dissipative, we modify \ref{eq:5p2.3} to write
+Common discretization schemes for \eqref{eq:5p2.3} are often dissipative, e.g., the Lax-Friedrich scheme used in \cite{Wang:255719}.
+Since the skew-symmetric discretization is non-dissipative, we modify \eqref{eq:5p2.3} as
 \begin{equation} \label{eq:5p2.10} 
@@
 with $\tau = \mu \partial (u A)/ \partial x$, and $\mu = 6\times 10^{-5}$.
-This type of artificial viscosity is chosen due to its simplicity.
+This type of artificial viscosity is chosen for its simplicity.
 This, however, can be replaced with a more moderate and sophisticated method.
-The three-stage Runge-Kutta (SSP RK3) \cite{jiang1996efficient} is used to then integrate \eqref{eq:5p2.10} in time.
-The pressure profile for the steady state, with $q'=0$, and the pressure oscillatory mode in the unsteady phase is presented in \Cref{steady_state}.
-We report that the added viscous term affects the level of pressure in the steady state and the aplitude of oscilations in the unsteady mode, compared to \cite{Wang:255719}.
+
+Note that the right hand side in \eqref{eq:5p2.10} suggests that, in general, mass, momentum, and energy is not conserved.
+Furthermore, the complex coupling of the variables in \eqref{eq:5p2.3} prohibits the application of complex and implicit time integration schemes.
+Therefore, a quasi-skew-symmetric form, introduced in \eqref{eq:3.7}, is used for \eqref{eq:5p2.3}.
+It is straight-forward to check \cite{sjogreen2010skew}, for $t,s\in \mathbb R^{N}$
+\begin{equation} \label{eq:5p2.9.1}
+	\frac 1 2 \delta_x (st)_j + \frac 1 2 s_j \delta_x (t)_j + \frac 1 2 t_j \delta_x (s)_j = \frac 1 4 \delta_x^+( s_j + s_{j-1} )(t_j + t_{j-1}).
+\end{equation}
+where $\delta_x (v)_j = \left( v_{j+1} - v_{j-1} \right)/\Delta x$ is a centered finite difference approximation of the space derivative and $\delta_x^+ (v_j) = \left( v_{j+1} - v_j \right) /\Delta x$, for some $v\in \mathbb R^{N}$.
+Therefore,
+\begin{equation} \label{eq:5p2.9.2}
+	F_{i+1/2}^{\Delta}(s_jt_j,s_{j+1}t_{j+1}) = ( s_j + s_{j-1} )(t_j + t_{j-1}),
+\end{equation}
+can be interpreted as an approximation of a quadratic flux function at the boundary of two adjacent finite volume cells.
+A better approximation of the flux in \eqref{eq:5p2.9.2} corresponds to a higher order skew-symmetric form for a quadratic variable $st$ in \eqref{eq:5p2.9.1}.
+We discretize the real line into N uniform cells of size $\Delta x$.
+A quasi-skew-symmetric form for \eqref{eq:5p2.10} now takes the form
+\begin{equation}
+\begin{aligned}
+	\frac{d}{dt} q^i_j + \delta^+ F^{\Delta}_{i+1/2}(q^i_jr^i_j,q^i_{j+1}r^i_{j+1}) &- \delta^+ F_d^{\Delta}(d^i_j,d^i_{j+1}) + \delta^+ F_p^{\Delta}(p_j,p_{j+1}) \\
+	&= \int_{c_j} s_A + s_f + s_q \ dx.
+\end{aligned}
+\end{equation}
+for $j=1,\dots,N$.
+Here, $c_j$ is the $j$th cell, $q^i_j = \int_{c_j} v^i \ dx$ is the cell average of the $i$th component of $v$, $F^{\Delta}_p$ is the flux approximation of the pressure term, $F^{\Delta}_d$ is the flux approximation for the viscous term and $r = ( u , u , u , u )^T$.
+
+The three-stage Runge-Kutta (SSP RK3) \cite{jiang1996efficient} is used to integrate \eqref{eq:5p2.10} in time.
+The pressure profile for the steady state, with $q'=0$, and the pressure oscillatory mode in the unsteady phase is presented in \Cref{fig:5p2.2a}.
 
@@
   \end{tikzpicture}
-  \caption{}
+  \caption{} \label{fig:5p2.2a}
   \label{steady_state}
@@
   \end{tikzpicture}
-  \caption{}
+  \caption{} \label{fig:5p2.2b}
   \label{oscill_pressure}
@@
   \end{tikzpicture}
-  \caption{}
+  \caption{} \label{fig:5p2.2c}
   \label{error_growth_comb}
@@
   \end{tikzpicture}
-  \caption{}
+  \caption{} \label{fig:5p2.2d}
   \label{oscill_focus}
@@
 
-The discontinuities that appear in the solution of \eqref{eq:5p2.10} suggests that a, relatively, large basis is required to resolve fine structures in the solution.
-In this paper, a POD basis is generated with $k=200$, $k=300$ and $k=400$ number of basis vectors.
-To avoid basis changes in reduced system, only one POD basis is considered for $\rho$, $\rho u$ $\rho E$ and $\rho Y_{ox}$.
+The discontinuities that appear in the solution of \eqref{eq:5p2.10} suggests that a relatively large basis is required to resolve fine structures in the solution.
+Here, a POD basis is generated with $k=200$, $k=300$ and $k=400$ number of basis vectors.
+To avoid basis changes in the reduced system, only one POD basis is considered for $\rho$, $\rho u$ $\rho E$ and $\rho Y_{ox}$.
 The explicit SSP RK3 is then used to integrated the reduced system in time, for the unsteady system.
-The source terms are evaluated in the high-fidelity space and then projected onto the reduced space.
-However, in principle, the DEIM can be applied to accelerate this evaluation.
+The source terms are evaluated in the high-fidelity space and projected onto the reduced space.
+However, in principle, the DEIM can be applied to accelerate this component.
 
-\Cref{error_growth_comb} shows the approximation error of the pressure, due to MOR.
-It is observed that the approximation is coherently enhanced as the number of basis vectors are increase.
-Furthermore, the approximated solution maintains high accuracy over a relatively long time-integration.
-The oscilations of pressure is demostrated in \Cref{oscill_focus}.
-It is seen that the overall behaviour of pressure is well approximated using the reduced system.
+\Cref{fig:5p2.2c} shows the approximation error of the pressure, due to MOR.
+It is observed that the approximation is consistently improved as the number of basis vectors increases.
+Furthermore, the approximate solution maintains high accuracy over a relatively long time-integration.
+The oscillations of pressure is demostrated in \Cref{fig:5p2.2d}.
+The overall behaviour of pressure is well approximated by the reduced system.
 Similar results are obtained for a POD basis with higher number of modes.
 
-We note that the discrete form of \eqref{eq:5p2.10} is not in the full skew-symmetric form. Nontheless, the quisi-skew-symmetric discretization provides a remarkable stability preservation.
+We note that the discrete form of \eqref{eq:5p2.10} is not in the full skew-symmetric form. Nonetheless, the quasi-skew-symmetric discretization offers remarkable stability preservation.

### 2018-07-17 sections/6.con.tex
all corrections added, a backupfile included

@@
 Conservation of nonlinear invariants are not, in general, guaranteed with conventional model reduction techniques.
-The violation of such invariants often result in a qualitatively wrong or unstable reduce system, even when the high-fidelity system is stable.
+The violation of such invariants often result in a qualitatively wrong or unstable reduced system, even when the high-fidelity system is stable.
 This is particularly important for fluid flow, where conservation of the energy, as a nonlinear invariant of the system, is crucial for a correct numerical evaluation.
@@
 In this paper, we discuss that conservative properties of the skew-symmetric form for fluid flow can naturally be extended to the reduced system.
-Conventional MOR techniques preserves the skew-symmetry of differential operator which result in conservation of quadratic invariants at the level of reduced system.
-Furthermore, we see that the reduced system, also, contains quadratic invariants with respect to the reduced variables that approximates the invariants of the high-fidelity system.
-This results in construction of a physically meaningful reduced system, rather than a mere couple systems of differential equations.
+Conventional MOR techniques preserves the skew-symmetry of differential operator which result in the conservation of quadratic invariants at the level of the reduced system.
+Furthermore, the reduced system also contains quadratic invariants with respect to the reduced variables that approximates the invariants of the high-fidelity system.
+This results in the construction of a physically meaningful reduced system, rather than a mere couple systems of differential equations.
 
-Numerical experiments of the incompressible and compressible Euler equation confirms conservation of mass, momentum and energy for the model reduction with the skew-symmetric discretization.
-It is seen that when a non-skew-symmetric form, e.g.
+Numerical experiments for the incompressible and compressible Euler equation confirms conservation of mass, momentum and energy for the reduced model with the skew-symmetric discretization.
+In contrast, when a non-skew-symmetric form, e.g.
 divergence form or advective form, is considered, MOR does not necessarily yield a stable reduced system.
-On the other hand the skew-symmetric form consistently yields a robust reduced system over long time-integration, even if when the reduce space does not represent the high-fidelity solution accurately.
+On the other hand the skew-symmetric form consistently yields a robust reduced system over long time-integration, even when the reduced space does not represent the high-fidelity solution accurately.
 
 Finally, a MOR of a quasi-skew-symmetric form for the CVRC model is presented.
-Although this model is not in a full skew-symmetric form and am explicit Runge-Kutta method used for time-integration, we still recover remarkable stability preservation.
+Although this model is not in a full skew-symmetric form and an explicit Runge-Kutta method used for time-integration, we still recover a reduced model with excellent stability properties.
+
+\section*{Acknowledgement} The work was partially supported by AFOSR under grant FA9550-17-1-9241 and by SNSF under the grant number P1ELP2-175039.

### 2018-10-05 backup.tex
updated version

--- 2018-07-17 sections/5.res_part2.tex
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%% Combustor images %%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
 	\centering
-\begin{tikzpicture}[]
-    \begin{axis}[width=12cm,
-                 height=4cm,
-                 ylabel = $r(m)$,
-                 xlabel=$x(m)$,
-                 yticklabel style={
-                  /pgf/number format/fixed,
-                  /pgf/number format/precision=5,
-                  style = {font=\normalsize}
-                  },
-                 xticklabel style={
-                  style = {font=\normalsize}
-                  },
-%                 label style={font=\large},
-%                 legend style={font=\large},
-%                 grid=both,
-%                 ticks=both,
-%                 width=0.7\linewidth, 
-%                 height=0.5\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 scaled y ticks = false,
-%                 enlargelimits=false,
-%                 samples = 100,
-                 ymax = 0.04]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = radius] {./data/Combustor/radius_combustor.txt};
-                \node[pin=100:{injector}] at (-0.05,0.01) {};
-                \node[pin=93:{back-step}] at (0.001,0.015) {};
-                \node[pin=90:{chamber}] at (0.2,0.023) {};
-                \node[pin=80:{nozzle}] at (0.4,0.015) {};
-    \end{axis}
-\end{tikzpicture}
+	\includegraphics[width=0.8\linewidth]{pic/radius}
 	\caption{Geometry of quasi-1D CVRC model.}
@@
 \end{table}
+
 For the combustion, we consider the one-step reaction model
@@
 
-%\begin{figure}[t]
-%\centering
-%\begin{subfigure}[]{0.47\linewidth}
-%	\includegraphics[width=\textwidth]{./pic/init_pressure}
-%	\caption{} \label{fig:5p2.2a}
-%\end{subfigure}
-%\begin{subfigure}[]{0.47\linewidth}
-%	\includegraphics[width=\textwidth]{./pic/init_osc}
-%	\caption{} \label{fig:5p2.2b}
-%\end{subfigure} \\
-%\begin{subfigure}[]{0.47\linewidth}
-%	\includegraphics[width=\textwidth]{./pic/p_error}
-%	\caption{} \label{fig:5p2.2c}
-%\end{subfigure}
-%\begin{subfigure}[]{0.47\linewidth}
-%	\includegraphics[width=\textwidth]{./pic/rom_freq}
-%	\caption{} \label{fig:5p2.2d}
-%\end{subfigure}
-%\caption{(a) Pressure profile of the steady state.
+\begin{figure}[t]
+\centering
+\begin{subfigure}[]{0.47\linewidth}
+	\includegraphics[width=\textwidth]{./pic/init_pressure}
+	\caption{} \label{fig:5p2.2a}
+\end{subfigure}
+\begin{subfigure}[]{0.47\linewidth}
+	\includegraphics[width=\textwidth]{./pic/init_osc}
+	\caption{} \label{fig:5p2.2b}
+\end{subfigure} \\
+\begin{subfigure}[]{0.47\linewidth}
+	\includegraphics[width=\textwidth]{./pic/p_error}
+	\caption{} \label{fig:5p2.2c}
+\end{subfigure}
+\begin{subfigure}[]{0.47\linewidth}
+	\includegraphics[width=\textwidth]{./pic/rom_freq}
+	\caption{} \label{fig:5p2.2d}
+\end{subfigure}
+\caption{(a) Pressure profile of the steady state.
 (b) Oscillatory mode of pressure located at $x=0.36$ for the unsteady flow.
@@
 }
-%\label{fig:5p2.2}
-%\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%% Combustor %%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-  \centering
-  % Pressure steady
-  \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = pressure $p$,
-                 xlabel=$x$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-%                 ymin=0,
-                 ymax = 1500000,
-                 samples = 100]
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = x, y = pressure] {./data/Combustor/pressure_steady_state.txt};
-    \end{axis}%  
-  \end{tikzpicture}
-  \caption{} \label{fig:5p2.2a}
-  \label{steady_state}
-  \end{subfigure}\hfill% 
-  % Pressure oscilaltions
-  \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = pressure $p$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 scaled y ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=0,
-%                 samples = 100,
-                 xmax = 0.06,
-                 ymin = 1360000,
-                 ymax = 1460000,
-                 tick label style={/pgf/number format/fixed} ]
-                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = pressure] {./data/Combustor/ciao.txt};
-    \end{axis}%  
-  \end{tikzpicture}
-  \caption{} \label{fig:5p2.2b}
-  \label{oscill_pressure}
-  \end{subfigure}
-
-% Total momentum
-  \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[ylabel = $\| p-\tilde{p}\|_2$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=south east,
-                 legend entries={$k=200$,$k=300$,$k=300$},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 scaled y ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 samples = 300,
-                 ymin = 0.000001,
-                 ymax = 0.0001]
-                 \addplot[color=red,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_200.txt};
-                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_300.txt};
-                 \addplot[color=black!50!green,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_400.txt};
-    \end{semilogyaxis}%  
-  \end{tikzpicture}
-  \caption{} \label{fig:5p2.2c}
-  \label{error_growth_comb}
-  \end{subfigure}\hfill% 
-  % Pressure reduction  
-  \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = pressure $p$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 legend entries={High fidelity,  POD with $k=200$},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 xmin = 0.9,
-                 xmax = 0.98,
-                 ymin = 1390000,
-                 ymax = 1450000,
-                 tick label style={/pgf/number format/fixed} ]
-                 \addplot[color=green,style=solid,style=ultra thick]  table[x = t, y = pressure] {./data/Combustor/full.txt};
-                 \addplot[color=black,style=dashed,style=thick]  table[x = t, y = pressure] {./data/Combustor/red.txt};
-    \end{axis}%  
-  \end{tikzpicture}
-  \caption{} \label{fig:5p2.2d}
-  \label{oscill_focus}
-  \end{subfigure}
-  \caption{(\protect\subref{steady_state}) Pressure profile of the steady state.
-(\protect\subref{oscill_pressure}) Oscillatory mode of pressure located at $x=0.36$ for the unsteady flow.
-(\protect\subref{error_growth_comb}) Relative error between the high-fidelity and approximated pressure.
-(\protect\subref{oscill_focus}) Approximation of the oscillations.}
 \label{fig:5p2.2}

### 2018-10-05 paper.tex
Update remaining figures Nicolo
updated version

@@
 
+\pgfplotsset{every tick label/.append style={font=\Large}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 % your contribution title if the original one is too long
-\author{Babak Maboudi Afkham, Nicol\`o Ripamonti, Qian Wang, Jan S. Hesthaven and Karen E. Willcox}
+\author{Babak Maboudi Afkham, Nicol\`o Ripamonti, Qian Wang, and Jan S. Hesthaven}
 % Use \authorrunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
-\and Name of Second Author \at Name, Address of Institute \email{name@email.address}}
+\institute{B. Maboudi Afkham, N. Ripamonti, Q. Wang, J.S. Hesthaven \at EPFL, Lausanne, Switzerland \email{babak.maboudi@epfl.ch}}
 %

### 2018-10-05 sections/1.intro.tex
updated version

@@
 
-Skew-symmetric formulation of fluid flows construct a skew-symmetric differential operator, acting on the momentum vector field, that ensures conservation of quadratic invariants, such as energy.
+Skew-symmetric formulation of fluid flows constructs a skew-symmetric differential operator, acting on the momentum vector field, that ensures conservation of quadratic invariants, such as energy.
 Combined wirh centered time and space discretization schemes, typically a finite differences discretization method, they recover time-symmetries of a fluid at the discrete level.
-Such discretization schemes are studies comprehensively over the past few decades and can be found in the works of \cite{morinishi2010skew,morinishi1998fully,desjardins2008high,tadmor1984skew,reiss2014conservative,reiss2014conservative} and the references therein.
+Such discretization schemes are studies comprehensively over the past few decades and can be found in the works of \cite{morinishi2010skew,morinishi1998fully,desjardins2008high,tadmor1984skew,reiss2014conservative} and the references therein.
 

### 2018-10-05 sections/4.mor_skew.tex
updated version

@@
 	& S^r_{\mathbf r ,\partial_t} + S^r _{\mathbf r \mathbf u} \mathbf u^r + V_{\mathbf r \mathbf u, \mathbf u}^T D V_{\mathbf p} \mathbf p^r = V_{\mathbf r \mathbf u, \mathbf u}^T D T, \\
-	&\frac{1}{\gamma -1} \frac{d}{dt} \mathbf p^r + \frac{\gamma}{\gamma -1} V_{\mathbf p}^T D U V_{\mathbf p} \mathbf p^r - V_{\mathbf p}^T UD V_{\mathbf p} \mathbf p^r = - V_{\mathbf p}^T UDT + V_{\mathbf p}^T D(UT - \mathbf \phi).
+	&\frac{1}{\gamma -1} \frac{d}{dt} \mathbf p^r + \frac{\gamma}{\gamma -1} V_{\mathbf p}^T D U V_{\mathbf p} \mathbf p^r - V_{\mathbf p}^T UD V_{\mathbf p} \mathbf p^r = - V_{\mathbf p}^T UDT + V_{\mathbf p}^T D(UT - \mathbf \phi),
 \end{aligned}
@@
 \end{equation}
+respectively.
 Note that in \eqref{eq:4.4}, dependency of $T$ on $V_{\mathbf r \mathbf u , \mathbf u}$ is not shown for abbreviation.
@@
 However, POD preserves linear properties of snapshots.
-To demonstrate this, let the overscript ``\textasciitilde'' denote the representation of a reduced variable in the high fidelity space.
-A reduced variable, e.g.
+To demonstrate this, let the overscript ``\textasciitilde'' denote the representation of a reduced variable in the high-fidelity space.
+An approximated variable, e.g.
 density, can be represented as a linear combination of some snapshots as $\mathbf r \approx \tilde{\mathbf r} = \sum_{i=1}^k c_i \mathbf r_i$, for some snapshots $\mathbf r_i$ and some coefficients $c_i \in \mathbb R$, for $i=1,\dots,k$.
@@
 Note, that only the reduced pressure and the viscous term contribute to the evolution of kinetic energy.
-Furthermore, the quantity $ \frac 1 2 {\mathbf u^r}^T \{ R \mathbf u\}^r$ is the kinetic energy associated with the reduced system \eqref{eq:4.4}, approximating the kinetic energy of the high-fidelity system \eqref{eq:3.21} and is a quadratic form with respect to the reduced variables.
+Furthermore, the quantity $ \frac 1 2 {\mathbf u^r}^T \{ R \mathbf u\}^r$ is the kinetic energy associated with the reduced system \eqref{eq:4.4}, approximating the kinetic energy of the high-fidelity system \eqref{eq:3.21}, and is a quadratic form with respect to the reduced variables.
 Conservation of kinetic energy for \eqref{eq:4.3} follows similarly.

### 2018-10-05 sections/5.res.tex
updated version

@@
 \end{equation*}
-The domain is discretized into $N=2000$ nodes and a centered finite differences scheme are used to assemble the discrete Euler equation in skew-symmetric form, as discussed in \Cref{sec:skew.3}.
+The domain is discretized into $N=2000$ nodes and a centered finite differences scheme is used to assemble the discrete Euler equation in skew-symmetric form, as discussed in \Cref{sec:skew.3}.
 
@@
 Here, the high-fidelity model is also considered in the divergence and advective form in addition to the skew-symmetric form.
-It is clear than when the reduced systems is not in skew-symmetric form, it violates conservation of mass, momentum, and energy.
+It is clear that when the reduced systems is not in skew-symmetric form, it violates conservation of mass, momentum, and energy.
 Even while the high-fidelity systems in divergence and advective forms are stable, the constructed reduced system is unstable, independent on the number of basis vectors.
@@
 
-As discussed in \Cref{sec:mor_skew}, the DEIM approximation needed for efficient evaluation of the nonlinear components of \eqref{eq:3.18}, can affect the conservation properties of the skew-symmetric form.
+As discussed in \Cref{sec:mor_skew}, the DEIM approximation needed for an efficient evaluation of the nonlinear components of \eqref{eq:3.18}, can affect the conservation properties of the skew-symmetric form.
 \Cref{fig:singular_values_decay_1D} shows the decay of the singular values of the nonlinear snapshots.
@@
 The conservation of energy is recovered once DEIM approximates the nonlinear terms with enough accuracy.
-While straightforward POD reduction does not offer a significative speed up if compared to the solution of the original high-dimensional nonlinear system of equations, with the DEIM treatment of nonlinearity solvers of the reduced models are of the order of tens faster than high fidelity solvers.
+In this numerical experiment, evaluation of the nonlinear terms in \eqref{eq:3.18} using the DEIM is ten times faster than the high-fidelity evaluation.
 

### 2018-10-05 sections/5.res_part2.tex
updated version

@@
 The fuel is pure gaseous methane.
-The oxidizer is a mixture of 42\% oxygen and 58\% water (per unit mass).
-And is injected in the oxidizer post at a temperature $T_{ox}=1030$ K so that both water and oxygen are in the gaseous phase.
+The oxidizer is a mixture of 42\% oxygen and 58\% water (per unit mass), and is injected in the oxidizer post at a temperature $T_{ox}=1030$ K so that both water and oxygen are in the gaseous phase.
 The operating conditions are listed in Table \ref{tab:operating-conditions}.
@@
 \begin{equation*}\label{eq:combustion}
-CH_4 + 2O_2 \rightarrow CO_2 + 2H_2O
+CH_4 + 2O_2 \rightarrow CO_2 + 2H_2O.
 \end{equation*}
@@
 Note that the right hand side in \eqref{eq:5p2.10} suggests that, in general, mass, momentum, and energy is not conserved.
-Furthermore, the complex coupling of the variables in \eqref{eq:5p2.3} prohibits the application of complex and implicit time integration schemes.
+Furthermore, the complex coupling of the variables in \eqref{eq:5p2.3} and the non-constant adiabatic gas index prohibits the application of complex and implicit time integration schemes.
 Therefore, a quasi-skew-symmetric form, introduced in \eqref{eq:3.7}, is used for \eqref{eq:5p2.3}.
@@
 \end{equation}
-where $\delta_x (v)_j = \left( v_{j+1} - v_{j-1} \right)/\Delta x$ is a centered finite difference approximation of the space derivative and $\delta_x^+ (v_j) = \left( v_{j+1} - v_j \right) /\Delta x$, for some $v\in \mathbb R^{N}$.
+where $\delta_x (v)_j = \left( v_{j+1} - v_{j-1} \right)/\Delta x$ is centered finite difference approximation of the space derivative and $\delta_x^+ (v_j) = \left( v_{j+1} - v_j \right) /\Delta x$, for some $v\in \mathbb R^{N}$.
 Therefore,
@@
 The three-stage Runge-Kutta (SSP RK3) \cite{jiang1996efficient} is used to integrate \eqref{eq:5p2.10} in time.
-The pressure profile for the steady state, with $q'=0$, and the pressure oscillatory mode in the unsteady phase is presented in \Cref{fig:5p2.2a}.
+The pressure profile for the steady state, with $q'=0$, and the pressure oscillatory mode in the unsteady phase is presented in \Cref{fig:5p2.2a,fig:5p2.2b}, respectively.
 
@@
 The source terms are evaluated in the high-fidelity space and projected onto the reduced space.
-However, in principle, the DEIM can be applied to accelerate this component.
+However, in principle, the DEIM can be applied to accelerate the evaluation this component.
 
@@
 Furthermore, the approximate solution maintains high accuracy over a relatively long time-integration.
-The oscillations of pressure is demostrated in \Cref{fig:5p2.2d}.
+The oscillations of pressure is demonstrated in \Cref{fig:5p2.2d}.
 The overall behaviour of pressure is well approximated by the reduced system.

### 2018-10-05 sections/1.intro.tex
corrections added

@@
 Conventional model reduction techniques often violates conservation of mass, momentum \cite{carlberg2018conservative}, or energy in fluid flows which result in an unstable reduced system, in particular for long time-integration.
-The method discussed in \cite{carlberg2018conservative} conserves the mass and momentum for a finite volume discretization scheme.
-However, a method that also conserves the energy of the fluid flow is not known to the authors.
+\edit{In \cite{barone2009stable} an entropy stable model reduction method for linear compressible flows is presented by considering an entropy-stable formulation of linearized compressible flows.
+Furthermore, a conservative model reduction for finite-volume models is presented in \cite{carlberg2018conservative} that conserves any quantity conserved by the finite-volume scheme.
+This method finds a reduced linear subspace that ensures conservation of quantities by solving an optimization problem with, generally nonlinear, equality constraints.
+The constrained optimization problem is solved online, and is only slightly more expensive than solving the unconstrained optimization problem associated with a typical Galerkin MOR.}
+
+%\edit{The method discussed in \cite{carlberg2018conservative} conserves the mass and momentum for a finite volume discretization scheme.
+However, a method that also conserves the energy of the fluid flow is not known to the authors.}
 
 Skew-symmetric formulation of fluid flows constructs a skew-symmetric differential operator, acting on the momentum vector field, that ensures conservation of quadratic invariants, such as energy.
-Combined wirh centered time and space discretization schemes, typically a finite differences discretization method, they recover time-symmetries of a fluid at the discrete level.
+\edit{Combined with} centered time and space discretization schemes, typically a finite differences discretization method, they recover time-symmetries of a fluid at the discrete level.
 Such discretization schemes are studies comprehensively over the past few decades and can be found in the works of \cite{morinishi2010skew,morinishi1998fully,desjardins2008high,tadmor1984skew,reiss2014conservative} and the references therein.
@@
 This results in conservation of quadratic invariants.
-Furthermore, we show that the reduced system, as a system of coupled differential equations, contains quadratic invariants and an associated energy which approximates the energy of the high-fidelity system.
+\edit{The conservation of quantities in the proposed method is guaranteed through the mathematical formulation of the reduced system, for any orthonormal reduced basis.
+Therefore, the offline and online computational costs of this method is comparable with conventional MOR techniques.
+However, other conservative model reduction methods, e.g.
+\cite{carlberg2018conservative}, often require solving multiple nonlinear optimization problems to ensure conservation which can increase the computational costs.} Furthermore, we show that the reduced system, as a system of coupled differential equations, contains quadratic invariants and an associated energy which approximates the energy of the high-fidelity system.
 Therefore, a proper time stepping scheme preserves the reduced representation of the energy, and therefore, the loss in energy due to model reduction remains constant in time.

### 2018-10-05 sections/3.skew.tex
corrections added

@@
 where $\partial \Omega$ is the boundary of $\Omega$, and $\hat n$ is the unit outward normal vector to $\partial \Omega$.
-When the right hand side of \eqref{eq:3.2} vanishes, e.g.
-in case where $\Omega$ is periodic and $\varphi$ is flux-free, the quantity $(\rho \varphi)$ is conserved.
-Therefore, \eqref{eq:3.1} is referred to as the \emph{conservative form} and the convective term in \eqref{eq:3.1} is referred to as the \emph{divergence form}.
+\edit{This means that the quantity $(\rho\varphi)$ is explicitly conserved over control volumes.} Therefore, \eqref{eq:3.1} is referred to as the \emph{conservative form} and the convective term in \eqref{eq:3.1} is referred to as the \emph{divergence form}.
 However, using the \emph{continuity equation}
@@
 \end{equation}
-Therefore, $\varphi^2$ is a conserved quantity for a flux-free $\varphi$.
+\edit{Therefore, $\rho \varphi^2$} is a conserved quantity for a flux-free $\varphi$.
 Since the divergence, the advective and the skew-symmetric forms are identical at the continuous level, $\varphi^2$ is a conserved quantity for all forms.
@@
 \begin{equation} \label{eq:3.7}
-	\frac{\partial }{\partial t} (\rho \varphi) + S_{\rho u}(\varphi) = \nabla \cdot F_{\varphi}.
+	\frac{\partial }{\partial t} (\rho \varphi) + \edit{ \frac 1 2 \left( \nabla \cdot(\rho u \varphi) + \rho u \cdot \nabla \varphi + \varphi \nabla \cdot(\rho u) \right) } = \nabla \cdot F_{\varphi}.
 \end{equation}
@@
 	&\frac 1 2 \sqrt{\mathbf r} ^{n+1/2} \frac{\sqrt{\mathbf r}^{n+1} - \sqrt{\mathbf r}^{n}}{\Delta t} + DU^{n+1/2} \mathbf r^{n} = 0, \\
-	& \sqrt{\mathbf r} ^{n+1/2}  \frac{\sqrt{ \mathbf R}^{n+1} u^{n+1} - \sqrt{\mathbf R}^{n}u^n}{\Delta t} + S_{\mathbf r^{n} \mathbf u^n} \mathbf u^{n+1/2}_\alpha + D \mathbf p^{n} = DT^{n}, \\
-	& \frac 1 {\gamma -1} \frac{\mathbf p^{n+1} - \mathbf p^n}{\Delta t} + \frac{\gamma}{\gamma -1} D U^{n} \mathbf p - U^{n} D \mathbf p = - U^{n}D T^{n} + D (U^nT^n - \phi^n).
+	& \sqrt{\mathbf r} ^{n+1/2}  \frac{\sqrt{ \mathbf R}^{n+1} \mathbf u^{n+1} - \sqrt{\mathbf R}^{n}\mathbf u^n}{\Delta t} + S_{\mathbf r^{n} \mathbf u^n} \mathbf u^{n+1/2}_\alpha + D \mathbf p^{n} = DT^{n}, \\
+	& \frac 1 {\gamma -1} \frac{\mathbf p^{n+1} - \mathbf p^n}{\Delta t} + \frac{\gamma}{\gamma -1} D U^{n} \mathbf p^n - U^{n} D \mathbf p^n = - U^{n}D T^{n} + D (U^nT^n - \phi^n),
 	\end{aligned}
@@
 \end{equation}
-Here, $\Delta t$ is the time step, superscript $n$ denotes evaluating at $t = n\Delta t$, superscript $n+1/2$ denotes the arithmetic average of a variable evaluated at $t=n\Delta t$ and $t=(n+1)\Delta t$, the square root sign denotes element-wise application of square root, and
+\edit{and all the variables are stored at the same location with the same resolution (colocated).} Here, \edit{$\mathbf R$ contains elements of $\mathbf r$ on its diagonal,} $\Delta t$ is the time step, superscript $n$ denotes evaluating at $t = n\Delta t$, superscript $n+1/2$ denotes the arithmetic average of a variable evaluated at $t=n\Delta t$ and $t=(n+1)\Delta t$, the square root sign denotes element-wise application of square root, and
 \begin{equation}

### 2018-10-10 sections/5.res.tex
Implement final corrections manuscript: add number of snapshots, briefly explain low pass filter on reduced modes, move the legends in figure 9

@@
 As centered schemes are often dissipation free, resolving the discontinuous initial data requires some artificial viscosity.
-In the high-fidelity model, the method discussed in \cite{artificial_dissipation} is used as an artificial viscosity.
+In the high-fidelity model, the method discussed in \cite{artificial_dissipation}\edit{, based on a derivative-based model,} is used as an artificial viscosity.
 However, at the level of the reduced system, this is replaced with a low pass filter on the expansion coefficients of POD basis vectors.
+\edit{The last $5\%$ of the POD modes are put to zero at each time iteration.
+The reason for the different treatment is that we want to avoid the reconstruction of the derivative of the solution in the full space during the integration of the reduced system.}
 
 The fully discrete skew-symmetric form \eqref{eq:3.27} is used as a time marching scheme with $\Delta t = 5 \cdot 10^{-4}$ over a period of $1$ time unit.
+\edit{A total of $500$ snapshots have been used for the computation of the basis in the offline stage.}
 
@@
 To resolve the discontinuous solution we use an artificial viscosity with $\tau = \mu \partial u / \partial x$, where $\mu = 0.5 \cdot 10^{-4}$.
+\edit{Regarding the reduction procedure, $1000$ snapshots of the numerical solution given by the high fidelity method have been collected.}
 
@@
 \centering
-\begin{subfigure}[]{0.47\linewidth}
+\begin{subfigure}[t]{0.47\linewidth}
 \begin{tikzpicture}[scale=0.58]
@@
                  label style={font=\large},
-                 legend pos=south west,
+                 %legend pos=south west,
                  legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
                  legend style={font=\large},
+                 legend style={at={(axis cs:0.375,0.45)},anchor=south west},
                  grid=both,
@@
 \end{subfigure} 
-\begin{subfigure}[]{0.47\linewidth}
+\begin{subfigure}[t]{0.47\linewidth}
 \begin{tikzpicture}[scale=0.58]
@@
                  label style={font=\large},
-                 legend pos=south west,
+                 legend pos=north east,
                  legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},

### 2018-11-07 response/response.tex
revision completed

\documentclass[a4paper]{article}
\usepackage{url}
\usepackage[margin=1in]{geometry}
\newcommand{\breview}{\begin{quotation}\begin{bf}\noindent}
\newcommand{\ereview}{\end{bf}\end{quotation}}
\newcommand{\reviewbullet}[1]{\breview \begin{itemize}\item #1 \end{itemize}\ereview}

\usepackage[colorinlistoftodos,prependcaption,textsize=tiny]{todonotes}

\begin{document}
Dear Editor, \\[1cm]

Attached you will find the revised version of the paper, titled ``Conservative Model Order Reduction for Fluid Flow'', with file name ``paper.pdf''. Another document under the file name ``paper-highlighted.pdf'' is also attached, where the changes in the paper are highlighted in the color red.

Yours Sincerely,\\[1.0cm]
Babak Maboudi Afkham
\\[1cm]

\section*{Response to Reviewer}

All the comments of the reviewer are addressed in the revision of the paper. Below you can find the response to some of the comments.

\breview
In some of the numerical examples is not reported the number of snapshots used to generate the POD spaces. For completeness I would add the number of snapshots used to generate the POD space in every numerical example.\ereview

The number of snapshots used in each simulation is now reported.

\breview
In section 5.2 page 17 it is mentioned that a different strategy to ensure stability is used at the full order and at the reduced order level (artificial viscosity vs low pass filter). I would add a sentence to better explain the procedure used at the reduced order level (low pass filter on the expansion coefficients).
\ereview

The strategy used for stability in this simulation is now included.

\breview
It is not clear to me the strategy used, at the reduced order level, to deal with the pressure-
velocity coupling. Are equations 39-40 solved using a monolithic approach?
\ereview

The reduced system is solved similar to the high fidelity system, on a collocated grid. Therefore, at each time step one system of equations is solved for density, velocity, as well as for pressure. This is clarified in the paper in page 13.

\end{document}

### 2018-11-07 sections/4.mor_skew.tex
revision completed

@@
 Subsequently, a basis for $\sqrt{\mathbf r}$, denoted by $V_{\sqrt{\mathbf r}}$, is constructed.
-The nonlinear terms are evaluated exactly using the quadratic expansion or approximated using the DEIM.
+\edit{Since the reduced system shows the same structure of \eqref{eq:3.27},  the same numerical integrator is used to compute the reduced solution, without decoupling the modes related to velocity, density and pressure.} The nonlinear terms are evaluated exactly using the quadratic expansion or approximated using the DEIM.

### 2019-01-08 sections/5.res.tex
Last fix to comment on POD modes filter
Change the included figures from tikz to pdf

@@
   \begin{subfigure}[]{0.47\linewidth}
-  \begin{tikzpicture}[scale=0.58]
-    \begin{axis}[ylabel=$K$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=south west,
-                 legend entries={Skew Symmetric form, Divergence form, Advective form},
-                 legend style={font=\large},
-                 width=1.4\linewidth, 
-                 height=1\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=4},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_skew_symmetric.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_divergence.txt};
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_convective.txt};
-    \end{axis}%  
-  \end{tikzpicture}
+            \includegraphics[scale=1]{Figures/paper-figure0.pdf}
+%  \begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[ylabel=$K$,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=south west,
+%                 legend entries={Skew Symmetric form, Divergence form, Advective form},
+%                 legend style={font=\large},
+%                 width=1.4\linewidth, 
+%                 height=1\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=4},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_skew_symmetric.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_divergence.txt};
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_convective.txt};
+%    \end{axis}%  
+%  \end{tikzpicture}
 \caption{}
@@
   \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
-                 xlabel=Basis POD,
-                 label style={font=\Large},
-                 %legend pos=north east,
-                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=0,
-                 ymax = 2,
-                 samples = 100]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = s] {./data/Incompressible_Euler/Singular_values/sv.txt};
-    \end{semilogyaxis}
-\end{tikzpicture}
+            \includegraphics[scale=1]{Figures/paper-figure1.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
+%                 xlabel=Basis POD,
+%                 label style={font=\Large},
+%                 %legend pos=north east,
+%                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 ymin=0,
+%                 ymax = 2,
+%                 samples = 100]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = s] {./data/Incompressible_Euler/Singular_values/sv.txt};
+%    \end{semilogyaxis}
+%\end{tikzpicture}
 \caption{}
@@
 \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{semilogyaxis}[ylabel = $\| \mathbf{u}-\tilde{\mathbf{u}}\|_2$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 samples = 100,
-                 cycle list name=exotic]
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_5.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_8.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_11.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_14.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_23.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_26.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_29.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_35.txt};
-    \end{semilogyaxis}
-\end{tikzpicture}
+          \includegraphics[scale=1]{Figures/paper-figure2.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{semilogyaxis}[ylabel = $\| \mathbf{u}-\tilde{\mathbf{u}}\|_2$,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 samples = 100,
+%                 cycle list name=exotic]
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_5.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_8.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_11.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_14.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_23.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_26.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_29.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_35.txt};
+%    \end{semilogyaxis}
+%\end{tikzpicture}
 \caption{}
@@
 \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[ylabel = $|K-\tilde{K}|$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=south west,
-                 legend entries={$k=5$ , $k=8$, $k=11$, $k=14$, $k=23$, $k=26$, $k=29$, $k=35$},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymax = 0.5598,
-                 samples = 100,
-                 cycle list name=exotic]
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_5.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_8.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_11.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_14.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_23.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_26.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_29.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_35.txt};
-    \end{axis}
-\end{tikzpicture}
+          \includegraphics[scale=1]{Figures/paper-figure3.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[ylabel = $|K-\tilde{K}|$,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=south west,
+%                 legend entries={$k=5$ , $k=8$, $k=11$, $k=14$, $k=23$, $k=26$, $k=29$, $k=35$},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 ymax = 0.5598,
+%                 samples = 100,
+%                 cycle list name=exotic]
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_5.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_8.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_11.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_14.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_23.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_26.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_29.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_35.txt};
+%    \end{axis}
+%\end{tikzpicture}
 \caption{}
@@
 However, at the level of the reduced system, this is replaced with a low pass filter on the expansion coefficients of POD basis vectors.
-\edit{The last $5\%$ of the POD modes are put to zero at each time iteration.
+\edit{The last $5\%$ of the POD modes are put to zero every $20$ time iterations.
 The reason for the different treatment is that we want to avoid the reconstruction of the derivative of the solution in the full space during the integration of the reduced system.}
@@
 \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[xlabel=$t$,
-                 ylabel=$e(t)$,
-                 label style={font=\Large},
-                 legend pos=outer north east,
-                 legend style={font=\large},
-                 legend entries={$k=200$,$k=300$,$k=400$,$k=500$,$k=600$},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 cycle list name=exotic]
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_200.txt};  
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_300.txt};      
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_400.txt}; 
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_500.txt};      
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_600.txt};               
-    \end{semilogyaxis}%  
-  \end{tikzpicture}
+          \includegraphics[scale=1]{Figures/paper-figure4.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{semilogyaxis}[xlabel=$t$,
+%                 ylabel=$e(t)$,
+%                 label style={font=\Large},
+%                 legend pos=outer north east,
+%                 legend style={font=\large},
+%                 legend entries={$k=200$,$k=300$,$k=400$,$k=500$,$k=600$},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 cycle list name=exotic]
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_200.txt};  
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_300.txt};      
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_400.txt}; 
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_500.txt};      
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_600.txt};               
+%    \end{semilogyaxis}%  
+%  \end{tikzpicture}
 \end{subfigure}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[ylabel = error in mass,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 legend entries={$k=200$ ,$k=300$, $k=400$,$k=500$,$k=600$},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 cycle list name=exotic]
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_200.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_300.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_400.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_500.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_600.txt};
-    \end{semilogyaxis}%  
-  \end{tikzpicture}
+            \includegraphics[scale=1]{Figures/paper-figure5.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{semilogyaxis}[ylabel = error in mass,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 legend entries={$k=200$ ,$k=300$, $k=400$,$k=500$,$k=600$},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 cycle list name=exotic]
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_200.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_300.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_400.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_500.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_600.txt};
+%    \end{semilogyaxis}%  
+%  \end{tikzpicture}
   \caption{}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[ylabel = error in total momentum,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-%                 legend entries={$k=200$ Conv,$k=201$ Conv},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 cycle list name=exotic]
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_200.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_300.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_400.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_500.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_600.txt};
-    \end{semilogyaxis}%  
-  \end{tikzpicture}
+            \includegraphics[scale=1]{Figures/paper-figure6.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{semilogyaxis}[ylabel = error in total momentum,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%%                 legend entries={$k=200$ Conv,$k=201$ Conv},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 cycle list name=exotic]
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_200.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_300.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_400.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_500.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_600.txt};
+%    \end{semilogyaxis}%  
+%  \end{tikzpicture}
   \caption{}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[ylabel = error in total energy,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-%                 legend entries={$k=200$ Conv,$k=201$ Conv},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 cycle list name=exotic]
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_200.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_300.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_400.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_500.txt};
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_600.txt};
-    \end{semilogyaxis}%  
-  \end{tikzpicture}
+            \includegraphics[scale=1]{Figures/paper-figure7.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{semilogyaxis}[ylabel = error in total energy,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%%                 legend entries={$k=200$ Conv,$k=201$ Conv},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 cycle list name=exotic]
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_200.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_300.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_400.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_500.txt};
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_600.txt};
+%    \end{semilogyaxis}%  
+%  \end{tikzpicture}
    \caption{}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = Mass,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=0,
-                 ymax = 2,
-                 samples = 100]
-                 \addplot[color=red,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/mass_102_1.txt};
-                 \addplot[color=blue,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/mass_201_1.txt};
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/mass_102_1.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/mass_201_1.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_102_1.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_201_1.txt};
-    \end{axis}%  
-  \end{tikzpicture}
+            \includegraphics[scale=1]{Figures/paper-figure8.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[ylabel = Mass,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 ymin=0,
+%                 ymax = 2,
+%                 samples = 100]
+%                 \addplot[color=red,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/mass_102_1.txt};
+%                 \addplot[color=blue,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/mass_201_1.txt};
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/mass_102_1.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/mass_201_1.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_102_1.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_201_1.txt};
+%    \end{axis}%  
+%  \end{tikzpicture}
   \end{subfigure}\hfill% 
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=south west,
-                 legend entries={$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymax=0.5000001]
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_24_1.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_102_1.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_201_1.txt};
-    \end{axis}%  
-  \end{tikzpicture}
+          \includegraphics[scale=1]{Figures/paper-figure9.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=south west,
+%                 legend entries={$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 ymax=0.5000001]
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_24_1.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_102_1.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_201_1.txt};
+%    \end{axis}%  
+%  \end{tikzpicture}
   \end{subfigure}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = Momentum,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=1,
-                 ymax = 2,
-                 samples = 100]
-                 \addplot[color=red,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/momentum_102_1.txt};
-                 \addplot[color=blue,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/momentum_201_1.txt};
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/momentum_102_1.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/momentum_201_1.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_102_1.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_201_1.txt};
-    \end{axis}%  
-  \end{tikzpicture} 
+          \includegraphics[scale=1]{Figures/paper-figure10.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[ylabel = Momentum,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 ymin=1,
+%                 ymax = 2,
+%                 samples = 100]
+%                 \addplot[color=red,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/momentum_102_1.txt};
+%                 \addplot[color=blue,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/momentum_201_1.txt};
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/momentum_102_1.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/momentum_201_1.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_102_1.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_201_1.txt};
+%    \end{axis}%  
+%  \end{tikzpicture} 
   \end{subfigure}\hfill% 
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=south west,
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 ymax=1.04963,
-                 scale only axis]
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_24_1.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_102_1.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_201_1.txt};
-    \end{axis}%  
-  \end{tikzpicture}
+          \includegraphics[scale=1]{Figures/paper-figure11.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=south west,
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 ymax=1.04963,
+%                 scale only axis]
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_24_1.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_102_1.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_201_1.txt};
+%    \end{axis}%  
+%  \end{tikzpicture}
   \end{subfigure}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = Energy,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=2.5,
-                 ymax = 4.5,
-                 samples = 100]
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/energy_102_1.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/energy_201_1.txt};                
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/energy_102_1.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/energy_201_1.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_102_1.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_201_1.txt};
-    \end{axis}%  
-  \end{tikzpicture} 
+          \includegraphics[scale=1]{Figures/paper-figure12.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[ylabel = Energy,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 ymin=2.5,
+%                 ymax = 4.5,
+%                 samples = 100]
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/energy_102_1.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/energy_201_1.txt};                
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/energy_102_1.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/energy_201_1.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_102_1.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_201_1.txt};
+%    \end{axis}%  
+%  \end{tikzpicture} 
   \caption{}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=south west,
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymax = 2.87438]
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_24_1.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_102_1.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_201_1.txt};
-    \end{axis}%  
-  \end{tikzpicture}
+          \includegraphics[scale=1]{Figures/paper-figure13.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=south west,
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 ymax = 2.87438]
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_24_1.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_102_1.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_201_1.txt};
+%    \end{axis}%  
+%  \end{tikzpicture}
   \caption{}
@@
 \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[xlabel=$t$,
-                 ylabel=$e(t)$,
-                 label style={font=\Large},
-                 legend pos=outer north east,
-                 legend style={font=\large},
-                 legend entries={$k=75$,$k=126$,$k=177$,$k=225$,$k=276$,$k=327$,$k=375$,$k=426$},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 cycle list name=exotic]
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_75.txt};  
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_126.txt};      
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_177.txt}; 
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_225.txt};      
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_276.txt};  
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_327.txt}; 
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_375.txt};      
-                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_426.txt};              
-    \end{semilogyaxis}%  
-  \end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure14.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{semilogyaxis}[xlabel=$t$,
+%                 ylabel=$e(t)$,
+%                 label style={font=\Large},
+%                 legend pos=outer north east,
+%                 legend style={font=\large},
+%                 legend entries={$k=75$,$k=126$,$k=177$,$k=225$,$k=276$,$k=327$,$k=375$,$k=426$},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 cycle list name=exotic]
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_75.txt};  
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_126.txt};      
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_177.txt}; 
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_225.txt};      
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_276.txt};  
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_327.txt}; 
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_375.txt};      
+%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_426.txt};              
+%    \end{semilogyaxis}%  
+%  \end{tikzpicture}
 \end{subfigure}
@@
 \begin{subfigure}[t]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[xlabel=$x$,
-                 ylabel=Density,
-                 label style={font=\large},
-                 %legend pos=south west,
-                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 legend style={at={(axis cs:0.375,0.45)},anchor=south west},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_300.txt};
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_300.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_300.txt};
-                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_300.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_300.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_300.txt};
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_300.txt};
-    \end{axis}% 
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure15.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[xlabel=$x$,
+%                 ylabel=Density,
+%                 label style={font=\large},
+%                 %legend pos=south west,
+%                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 legend style={at={(axis cs:0.375,0.45)},anchor=south west},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_300.txt};
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_300.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_300.txt};
+%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_300.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_300.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_300.txt};
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_300.txt};
+%    \end{axis}% 
+%\end{tikzpicture}
 \end{subfigure} 
 \begin{subfigure}[t]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[xlabel=$x$,
-                 ylabel=Pressure,
-                 label style={font=\large},
-                 legend pos=south west,
-                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_300.txt};
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_300.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_300.txt};
-                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_300.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_300.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_300.txt};
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_300.txt};
-    \end{axis}% 
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure16.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[xlabel=$x$,
+%                 ylabel=Pressure,
+%                 label style={font=\large},
+%                 legend pos=south west,
+%                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_300.txt};
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_300.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_300.txt};
+%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_300.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_300.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_300.txt};
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_300.txt};
+%    \end{axis}% 
+%\end{tikzpicture}
 \label{density_reduction}
@@
 \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[xlabel=$x$,
-                 ylabel=Density,
-                 label style={font=\large},
-                 legend pos=north east,
-                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_1000.txt};
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_1000.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_1000.txt};
-                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_1000.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_1000.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_1000.txt};
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_1000.txt};
-    \end{axis}% 
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure17.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[xlabel=$x$,
+%                 ylabel=Density,
+%                 label style={font=\large},
+%                 legend pos=north east,
+%                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_1000.txt};
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_1000.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_1000.txt};
+%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_1000.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_1000.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_1000.txt};
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_1000.txt};
+%    \end{axis}% 
+%\end{tikzpicture}
 \end{subfigure} 
 \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[xlabel=$x$,
-                 ylabel=Pressure,
-                 label style={font=\large},
-                 legend pos=south west,
-                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_1000.txt};
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_1000.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_1000.txt};
-                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_1000.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_1000.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_1000.txt};
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_1000.txt};
-    \end{axis}% 
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure18.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[xlabel=$x$,
+%                 ylabel=Pressure,
+%                 label style={font=\large},
+%                 legend pos=south west,
+%                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_1000.txt};
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_1000.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_1000.txt};
+%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_1000.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_1000.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_1000.txt};
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_1000.txt};
+%    \end{axis}% 
+%\end{tikzpicture}
 \end{subfigure}
@@
 \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[xlabel=$x$,
-                 ylabel=Density,
-                 label style={font=\large},
-                 legend pos=north east,
-                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_3000.txt};
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_3000.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_3000.txt};
-                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_3000.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_3000.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_3000.txt};
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_3000.txt};
-    \end{axis}% 
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure19.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[xlabel=$x$,
+%                 ylabel=Density,
+%                 label style={font=\large},
+%                 legend pos=north east,
+%                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_3000.txt};
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_3000.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_3000.txt};
+%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_3000.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_3000.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_3000.txt};
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_3000.txt};
+%    \end{axis}% 
+%\end{tikzpicture}
 \caption{}
@@
 \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[xlabel=$x$,
-                 ylabel=Pressure,
-                 label style={font=\large},
-                 legend pos=south west,
-                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_3000.txt};
-                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_3000.txt};
-                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_3000.txt};
-                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_3000.txt};
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_3000.txt};
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_3000.txt};
-                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_3000.txt};
-    \end{axis}% 
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure20.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[xlabel=$x$,
+%                 ylabel=Pressure,
+%                 label style={font=\large},
+%                 legend pos=south west,
+%                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_3000.txt};
+%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_3000.txt};
+%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_3000.txt};
+%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_3000.txt};
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_3000.txt};
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_3000.txt};
+%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_3000.txt};
+%    \end{axis}% 
+%\end{tikzpicture}
 \caption{}
@@
 \centering
-\begin{tikzpicture}[scale=0.5452]
-    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
-                 xlabel=Basis,
-                 label style={font=\Large},
-                 legend style={font=\large},
-                 legend entries = {POD,DEIM},
-                 grid=both,
-                 ticks=both,
-                 width=0.7\linewidth, 
-                 height=0.5\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 samples = 100,
-                 xtick = {400, 800, 1200, 1600}]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = n, y = sing_values] {./data/Compressible_Euler/1D/Singular_values/sv.txt};
-                 \addplot[color=black,style=dashed,style=ultra thick]  table[x = n, y = sv] {./data/Compressible_Euler/1D/Singular_values/sv_DEIM.txt};
-    \end{semilogyaxis}
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure21.pdf}
+%\begin{tikzpicture}[scale=0.5452]
+%    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
+%                 xlabel=Basis,
+%                 label style={font=\Large},
+%                 legend style={font=\large},
+%                 legend entries = {POD,DEIM},
+%                 grid=both,
+%                 ticks=both,
+%                 width=0.7\linewidth, 
+%                 height=0.5\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 samples = 100,
+%                 xtick = {400, 800, 1200, 1600}]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = n, y = sing_values] {./data/Compressible_Euler/1D/Singular_values/sv.txt};
+%                 \addplot[color=black,style=dashed,style=ultra thick]  table[x = n, y = sv] {./data/Compressible_Euler/1D/Singular_values/sv_DEIM.txt};
+%    \end{semilogyaxis}
+%\end{tikzpicture}
 \caption{Decay of the singular values of the snapshot matrix related to POD and DEIM algorithms for the 1D compressible Euler problem.}
@@
 \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[ylabel = e(T),
-                 xlabel=Basis DEIM,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 legend entries={POD+DEIM,POD},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1\linewidth,
-%                 minor x tick num=1,
-                 minor y tick num=2,	
-                 xticklabel style={font = \large},
-%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_DEIM.txt};      
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_POD.txt};
-    \end{axis}
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure22.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[ylabel = e(T),
+%                 xlabel=Basis DEIM,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 legend entries={POD+DEIM,POD},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1\linewidth,
+%%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 xticklabel style={font = \large},
+%%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_DEIM.txt};      
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_POD.txt};
+%    \end{axis}
+%\end{tikzpicture}
 \caption{}
@@
 \begin{subfigure}[]{0.47\linewidth}
-\begin{tikzpicture}[scale=0.58]
-    \begin{axis}[ylabel = Energy(T),
-                 xlabel=Basis DEIM,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 legend entries={POD+DEIM,POD},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis]
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_energy_DEIM.txt};      
-                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_energy_POD.txt};
-    \end{axis}
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure23.pdf}
+%\begin{tikzpicture}[scale=0.58]
+%    \begin{axis}[ylabel = Energy(T),
+%                 xlabel=Basis DEIM,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 legend entries={POD+DEIM,POD},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis]
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_energy_DEIM.txt};      
+%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_energy_POD.txt};
+%    \end{axis}
+%\end{tikzpicture}
 \caption{}

### 2019-01-08 sections/5.res_part2.tex
Change the included figures from tikz to pdf

@@
 \centering
-\begin{tikzpicture}[]
-    \begin{axis}[width=12cm,
-                 height=4cm,
-                 ylabel = $r(m)$,
-                 xlabel=$x(m)$,
-                 yticklabel style={
-                  /pgf/number format/fixed,
-                  /pgf/number format/precision=5,
-                  style = {font=\normalsize}
-                  },
-                 xticklabel style={
-                  style = {font=\normalsize}
-                  },
-%                 label style={font=\large},
-%                 legend style={font=\large},
-%                 grid=both,
-%                 ticks=both,
-%                 width=0.7\linewidth, 
-%                 height=0.5\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 scaled y ticks = false,
-%                 enlargelimits=false,
-%                 samples = 100,
-                 ymax = 0.04]
-                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = radius] {./data/Combustor/radius_combustor.txt};
-                \node[pin=100:{injector}] at (-0.05,0.01) {};
-                \node[pin=93:{back-step}] at (0.001,0.015) {};
-                \node[pin=90:{chamber}] at (0.2,0.023) {};
-                \node[pin=80:{nozzle}] at (0.4,0.015) {};
-    \end{axis}
-\end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure24.pdf}
+%\begin{tikzpicture}[]
+%    \begin{axis}[width=12cm,
+%                 height=4cm,
+%                 ylabel = $r(m)$,
+%                 xlabel=$x(m)$,
+%                 yticklabel style={
+%                  /pgf/number format/fixed,
+%                  /pgf/number format/precision=5,
+%                  style = {font=\normalsize}
+%                  },
+%                 xticklabel style={
+%                  style = {font=\normalsize}
+%                  },
+%%                 label style={font=\large},
+%%                 legend style={font=\large},
+%%                 grid=both,
+%%                 ticks=both,
+%%                 width=0.7\linewidth, 
+%%                 height=0.5\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 scaled y ticks = false,
+%%                 enlargelimits=false,
+%%                 samples = 100,
+%                 ymax = 0.04]
+%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = radius] {./data/Combustor/radius_combustor.txt};
+%                \node[pin=100:{injector}] at (-0.05,0.01) {};
+%                \node[pin=93:{back-step}] at (0.001,0.015) {};
+%                \node[pin=90:{chamber}] at (0.2,0.023) {};
+%                \node[pin=80:{nozzle}] at (0.4,0.015) {};
+%    \end{axis}
+%\end{tikzpicture}
 \caption{Geometry of quasi-1D CVRC model.}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = pressure $p$,
-                 xlabel=$x$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-%                 ymin=0,
-                 ymax = 1500000,
-                 samples = 100]
-                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = x, y = pressure] {./data/Combustor/pressure_steady_state.txt};
-    \end{axis}%  
-  \end{tikzpicture}
+          \includegraphics[scale=1]{Figures/paper-figure25.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[ylabel = pressure $p$,
+%                 xlabel=$x$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%%                 ymin=0,
+%                 ymax = 1500000,
+%                 samples = 100]
+%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = x, y = pressure] {./data/Combustor/pressure_steady_state.txt};
+%    \end{axis}%  
+%  \end{tikzpicture}
   \caption{} \label{fig:5p2.2a}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = pressure $p$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 scaled y ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 ymin=0,
-%                 samples = 100,
-                 xmax = 0.06,
-                 ymin = 1360000,
-                 ymax = 1460000,
-                 tick label style={/pgf/number format/fixed} ]
-                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = pressure] {./data/Combustor/ciao.txt};
-    \end{axis}%  
-  \end{tikzpicture}
+        \includegraphics[scale=1]{Figures/paper-figure26.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[ylabel = pressure $p$,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 scaled y ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 ymin=0,
+%%                 samples = 100,
+%                 xmax = 0.06,
+%                 ymin = 1360000,
+%                 ymax = 1460000,
+%                 tick label style={/pgf/number format/fixed} ]
+%                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = pressure] {./data/Combustor/ciao.txt};
+%    \end{axis}%  
+%  \end{tikzpicture}
   \caption{} \label{fig:5p2.2b}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{semilogyaxis}[ylabel = $\| p-\tilde{p}\|_2$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=south east,
-                 legend entries={$k=200$,$k=300$,$k=300$},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 scaled y ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 samples = 300,
-                 ymin = 0.000001,
-                 ymax = 0.0001]
-                 \addplot[color=red,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_200.txt};
-                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_300.txt};
-                 \addplot[color=black!50!green,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_400.txt};
-    \end{semilogyaxis}%  
-  \end{tikzpicture}
+      \includegraphics[scale=1]{Figures/paper-figure27.pdf}
+%  \begin{tikzpicture}[scale=0.55]
+%    \begin{semilogyaxis}[ylabel = $\| p-\tilde{p}\|_2$,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=south east,
+%                 legend entries={$k=200$,$k=300$,$k=300$},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 scaled y ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 samples = 300,
+%                 ymin = 0.000001,
+%                 ymax = 0.0001]
+%                 \addplot[color=red,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_200.txt};
+%                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_300.txt};
+%                 \addplot[color=black!50!green,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_400.txt};
+%    \end{semilogyaxis}%  
+%  \end{tikzpicture}
   \caption{} \label{fig:5p2.2c}
@@
   \begin{subfigure}[]{0.48\linewidth}
-  \begin{tikzpicture}[scale=0.55]
-    \begin{axis}[ylabel = pressure $p$,
-                 xlabel=$t$,
-                 label style={font=\Large},
-                 legend pos=north east,
-                 legend entries={High fidelity,  POD with $k=200$},
-                 legend style={font=\large},
-                 grid=both,
-                 ticks=both,
-                 width=1.4\linewidth, 
-                 height=1.0\linewidth,
-                 minor x tick num=1,
-                 minor y tick num=2,	
-                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
-                 scaled x ticks = true,
-                 enlargelimits=false,
-                 scale only axis,
-                 xmin = 0.9,
-                 xmax = 0.98,
-                 ymin = 1390000,
-                 ymax = 1450000,
-                 tick label style={/pgf/number format/fixed} ]
-                 \addplot[color=green,style=solid,style=ultra thick]  table[x = t, y = pressure] {./data/Combustor/full.txt};
-                 \addplot[color=black,style=dashed,style=thick]  table[x = t, y = pressure] {./data/Combustor/red.txt};
-    \end{axis}%  
-  \end{tikzpicture}
+    \includegraphics[scale=1]{Figures/paper-figure28.pdf}
+ % \begin{tikzpicture}[scale=0.55]
+%    \begin{axis}[ylabel = pressure $p$,
+%                 xlabel=$t$,
+%                 label style={font=\Large},
+%                 legend pos=north east,
+%                 legend entries={High fidelity,  POD with $k=200$},
+%                 legend style={font=\large},
+%                 grid=both,
+%                 ticks=both,
+%                 width=1.4\linewidth, 
+%                 height=1.0\linewidth,
+%                 minor x tick num=1,
+%                 minor y tick num=2,	
+%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
+%                 scaled x ticks = true,
+%                 enlargelimits=false,
+%                 scale only axis,
+%                 xmin = 0.9,
+%                 xmax = 0.98,
+%                 ymin = 1390000,
+%                 ymax = 1450000,
+%                 tick label style={/pgf/number format/fixed} ]
+%                 \addplot[color=green,style=solid,style=ultra thick]  table[x = t, y = pressure] {./data/Combustor/full.txt};
+%                 \addplot[color=black,style=dashed,style=thick]  table[x = t, y = pressure] {./data/Combustor/red.txt};
+%    \end{axis}%  
+%  \end{tikzpicture}
   \caption{} \label{fig:5p2.2d}

### 2019-01-09 final/paper.tex
the final version added

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{epstopdf}

\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{subcaption}
\captionsetup{compatibility=false} % otherwise it raises some issues regarding compatibility

\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{mathtools}
%\usepackage[linesnumbered, ruled, vlined]{algorithm2e}
%\usepackage{algorithm}% http://ctan.org/pkg/algorithms
%\usepackage{algorithmicx} 
%\usepackage{algpseudocode}% http://ctan.org/pkg/algorithmicx
%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%\renewcommand{\algorithmicensure}{\textbf{Output:}}
\usepackage{enumerate}
\usepackage{multirow}
\usepackage{cleveref}

\newcommand{\edit}[1]{{\color{black} #1}}

\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\pgfplotsset{
    % most recent feature set of pgfplots
    compat=newest,
    % some settings for grid
    grid style={black!20!white, thin, densely dotted},
    % modify plot appearance
    every axis plot/.append style={no markers, thick},
    % i like the labels a bit smaller
    label style={font=\small},
    tick label style={font=\small}
}
\usepgfplotslibrary{external} 
\tikzexternalize[prefix=TikzFigures/]

%\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
%\usepackage{hyperref} % For hyperlinks in the PDF

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

\pgfplotsset{every tick label/.append style={font=\Large}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{Conservative Model Order Reduction for Fluid Flow}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Babak Maboudi Afkham, Nicol\`o Ripamonti, Qian Wang, and Jan S. Hesthaven}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{B. Maboudi Afkham, N. Ripamonti, Q. Wang, J.S. Hesthaven \at EPFL, Lausanne, Switzerland \email{babak.maboudi@epfl.ch}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

%\abstract*{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content. The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access. This allows unregistered users to read the abstract as a teaser for the complete chapter. As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.
%Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf. source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript. Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}

%\abstract{In the context of model order reduction, conservation of stability for systems of hyperbolic partial differential equations, remains a challenge. Recently preserving structures, invariants and conservation laws, in order to help with stability, and ensure robustness in long-time integrations, has been an area of active research. Energy conservation is a fundamental feature of fluid flows which is often violated in the course of model reduction. In this paper we discuss a model reduction routine, that exploits skew-symmetry of conservative and centered discretization schemes, to recover conservation of energy at the level of reduced system. This results in an, overall, correct evolution of the fluid and ensures robustness of the reduced system. We evaluate the performance of the proposed method through numerical simulation of various fluid flows, and also in a numerical simulation of continuous variable resonance combustor model.}

\abstract{In the past decade, model order reduction (MOR) has been successful in reducing the computational complexity of elliptic and parabolic systems of partial differential equations (PDEs). However, MOR of hyperbolic equations remains a challenge. Symmetries and conservation laws, which are a distinctive feature of such systems, are often destroyed by conventional MOR techniques which result in a perturbed, and often unstable reduced system. The importance of conservation of energy is well-known for a correct numerical integration of fluid flow. In this paper, we discuss model reduction, that exploits skew-symmetry of conservative and centered discretization schemes, to recover conservation of energy at the level of the reduced system. Moreover, we argue that the reduced system, constructed with the new method, can be identified by a reduced energy that mimics the energy of the high-fidelity system. Therefore, the loss in energy, associated with the model reduction, remains constant in time. This results in an, overall, correct evolution of the fluid that ensures robustness of the reduced system. We evaluate the performance of the proposed method through numerical simulation of various fluid flows, and through a numerical simulation of a continuous variable resonance combustor model.}

% sections are added here

\section{Introduction} \label{sec:intro}

Model order reduction (MOR), and in particular reduced basis (RB) methods, has emerged as a powerful approach to cope with the complex and computationally intensive models in engineering and science. Such techniques construct a reduced ordered representation for the state of a model which accurately approximates the configuration of the system. The evaluation of this representation is then possible with considerable acceleration.

Although RB methods are successful in reducing the computational complexity of models with elliptic and parabolic partial differential equations (PDEs), MOR of systems of hyperbolic equations, or models with strong advective terms, remains a challenge. Often, such models arise from a set of invariants and conservation laws, some of which are violated by MOR which result in a qualitatively wrong, and sometimes unstable, solution.

Constructing MOR techniques and RB methods that preserve intrinsic structures has recently attracted attention \cite{doi:10.1137/17M1111991,kalashnikova2014stabilization,farhat2015structure,doi:10.1137/110836742,beattie2011structure,doi:10.1137/140978922}. Structure preservation can recover a physically meaningful reduced model, rather than a pure algebraic coupling of equations. This enforces robustness and can help with the stability of the reduced model. Preserving time-symmetries of Lagrangian, Hamiltonian, and port-Hamiltonian systems can be found in the works of \cite{Carlberg:2014ky,doi:10.1137/140978922,doi:10.1137/17M1111991,beattie2011structure,chaturantabut2016structure,gugercin2012structure}. Conserving inf-sup stability, in the context of finite element methods, can be found in \cite{farhat2015structure,ballarin2015supremizer}. Furthermore, a flux preserving model reduction for finite volume methods is presented in \cite{carlberg2018conservative}.

Large scale simulations of fluid flows arise in a wide range of disciplines and industries. Therefore, MOR of fluid flows, specially when advective terms are dominant, is important. It is well known that conservation of the energy, specially kinetic energy, is essential for a qualitatively correct numerical integration of fluid flows. Conventional model reduction techniques often violates conservation of mass, momentum \cite{carlberg2018conservative}, or energy in fluid flows which result in an unstable reduced system, in particular for long time-integration. \edit{In \cite{barone2009stable} an entropy stable model reduction method for linear compressible flows is presented by considering an entropy-stable formulation of linearized compressible flows. Furthermore, a conservative model reduction for finite-volume models is presented in \cite{carlberg2018conservative} that conserves any quantity conserved by the finite-volume scheme. This method finds a reduced linear subspace that ensures conservation of quantities by solving an optimization problem with, generally nonlinear, equality constraints. The constrained optimization problem is solved online, and is only slightly more expensive than solving the unconstrained optimization problem associated with a typical Galerkin MOR.}

%\edit{The method discussed in \cite{carlberg2018conservative} conserves the mass and momentum for a finite volume discretization scheme. However, a method that also conserves the energy of the fluid flow is not known to the authors.}

Skew-symmetric formulation of fluid flows constructs a skew-symmetric differential operator, acting on the momentum vector field, that ensures conservation of quadratic invariants, such as energy. \edit{Combined with} centered time and space discretization schemes, typically a finite differences discretization method, they recover time-symmetries of a fluid at the discrete level. Such discretization schemes are studies comprehensively over the past few decades and can be found in the works of \cite{morinishi2010skew,morinishi1998fully,desjardins2008high,tadmor1984skew,reiss2014conservative} and the references therein.

In this paper we discuss how to preserve skew-symmetry of the differential operators at the level of the reduced system. This results in conservation of quadratic invariants. \edit{The conservation of quantities in the proposed method is guaranteed through the mathematical formulation of the reduced system, for any orthonormal reduced basis. Therefore, the offline and online computational costs of this method is comparable with conventional MOR techniques. However, other conservative model reduction methods, e.g. \cite{carlberg2018conservative}, often require solving multiple nonlinear optimization problems to ensure conservation which can increase the computational costs.} Furthermore, we show that the reduced system, as a system of coupled differential equations, contains quadratic invariants and an associated energy which approximates the energy of the high-fidelity system. Therefore, a proper time stepping scheme preserves the reduced representation of the energy, and therefore, the loss in energy due to model reduction remains constant in time. Furthermore, we demonstrate, through numerical experiments, that a quasi-skew-symmetric form of fluid flow, i.e. a formulation where only spacial differential operators are in a skew-symmetric form, offer remarkable stability properties in terms of MOR. This allows an explicit time-integration to be utilized while recovering robustness of skew-symmetric forms at the reduced level.

The rest of this paper is organized as follows. In \Cref{sec:mor} we summarize the theory on MOR and introduce the proper orthogonal decomposition (POD) as a conventional RB method. We discuss skew-symmetric and conservatives methods for compressible and incompressible fluid flows in \Cref{sec:skew}. Conservative and energy-preserving model reduction of fluid flows is discussed in \Cref{sec:mor_skew}. We evaluate the performance of the method through numerical simulations of incompressible and compressible fluid flow in \Cref{sec:res}. We also apply the method to construct a reduced system for the continuous variable resonance combustor, a one dimensional reaction-diffusion model for a rocket engine. Finally, we present conclusive remarks in \Cref{sec:con}.

\section{Model Order Reduction for Time Dependent Problems} \label{sec:mor}

Consider a dynamical system of the form
\begin{equation} \label{eq:1}
	\left\{
	\begin{aligned}
		\frac{d}{dt} u(t) &= f(t,u(t)),\\
		u(0) &= u_0.
	\end{aligned}
	\right.
\end{equation}
Here, $u(t),u_0\in \mathbb R^{n}$ and $f: [0,T]\times \mathbb R^{n} \to \mathbb R^{n}$, for some $T<\infty$, is a Lipschitz function. We may apply the \emph{method of lines} \cite{Edsberg:2008:ICM:1477735} to a system of partial differential equations to obtain a dynamical system of the form \eqref{eq:1}. The \emph{solution manifold} for \eqref{eq:1} is defined as
\begin{equation} \label{eq:2}
	\mathcal M_u := \{ u(t) | t \in [0,T] \}.
\end{equation}
When $\mathcal M_u$ has a low-dimensional representation, it is referred to as \emph{reducible}. Assume that $\mathcal M_u$ can be well approximated by a $k$-dimensional linear subspace $\mathcal V_k$, with $k\ll n$ and let $E_k = \{ v_1,\dots,v_k \}$ be the basis vectors for $\mathcal V_k$ and $V_k$ the basis matrix that contains these vectors in its columns. A reduced basis (RB) method assumes that $u \approx \tilde u = V_k v$, where $v\in \mathbb R^{k}$ is the expansion coefficients of $\tilde u$ in the basis $V_k$. Substituting this into \eqref{eq:1} yields
\begin{equation} \label{eq:3}
	V_k \frac{d}{dt} v(t) = f(t,V_{k}v) + r(t,u).	
\end{equation}
Here, $r$ is the error vector in this approximation. The Petrov-Galerkin projection of \eqref{eq:1} onto $\mathcal V_k$ requires $r$ to be orthogonal to a $k$-dimensional subspace $\mathcal W_k$. One can construct a projection operator $P_{\mathcal V_{k},\mathcal W_k}$ that projects elements of $\mathbb R^{n}$ onto $\mathcal V_k$, orthogonal to $\mathcal W_k$ as $P_{\mathcal V_{k},\mathcal W_k} = V_k(W_k^TV_k)^{-1}W_k^T$, where $W_k$ is the basis matrix that contains the basis vectors of $\mathcal W_k$ in its columns and $W_k^TV_k$ is assumed to be invertible. With this projection, \eqref{eq:1} reduces to the $k$-dimensional problem
\begin{equation} \label{eq:4}
	\left\{
	\begin{aligned}
		\frac{d}{dt} v(t) &= (W_k^TV_k)^{-1} f(t,V_{k}v),\\
		v(0) &= (W_k^TV_k)^{-1}u_0.
	\end{aligned}
	\right.
\end{equation}
When we require $W_k=V_k$, then \eqref{eq:4} is referred to as the \emph{Galerkin} projection of \eqref{eq:1} onto $\mathcal V_k$. Since \eqref{eq:4} has a smaller size, as compared to \eqref{eq:1}, one can expect an accelerated evaluation. To numerically identify the best possible subspace $\mathcal V_{k}$ we first discretize the solution manifold to obtain
\begin{equation} \label{eq:5}
	\mathcal M_{u}^{\Delta} = \{ u(t_i) | i\in \{ 1,\dots,N_t \} \}.
\end{equation}
Members of $\mathcal M_{u}^{\Delta}$ are referred to as \emph{snapshots} of \eqref{eq:1}. One can obtain these snapshots by applying a time-integration scheme, e.g., the Runge-Kutta methods, to \eqref{eq:1} to obtain $\tilde {\mathcal M}_{u}^{\Delta}$ as an approximation to $\mathcal M_{u}^{\Delta}$. Throughout this paper, we assume that we can choose $\tilde{\mathcal M}_{u}^{\Delta}$ arbitrary close to $\mathcal M_{u}^{\Delta}$. By an abuse of notation, we drop the overscript ``\textasciitilde''. For a Galerkin projection, the best possible basis $V_k$ is the one that minimizes the collective projection error \cite{hesthaven2015certified}, i.e., the solution to the minimization problem
\begin{equation} \label{eq:6}
\begin{aligned}
&  \underset{V_k\in\mathbb R^{n\times k}}{\text{minimize}}
& &  \| S - V_kV_k^TS\|_F, \\
& \text{subject to}
& & V_k^TV_k=I_k.
\end{aligned}
\end{equation}
Here $S$ collects vectors in $\mathcal M_{u}^{\Delta}$ in its columns, referred to as the \emph{snapshot matrix}, $\|\cdot \|_F$ is the Frobenius norm \cite{trefethen97}, and $I_{k}$ is the identity matrix of size $k$. Note that the constraint in \eqref{eq:6} requires $V_k$ to be orthonormal. The basis matrix $V_k$ that solves the minimization problem \eqref{eq:6} is referred to as the \emph{proper orthogonal decomposition} (POD) of $S$ of size $k$ \cite{hesthaven2015certified} and, according to the Schmidt-Mirsky theorem, can be constructed using the left singular vectors of $S$ as
\begin{equation}
	V_{k} = [u_i]_{i=1}^{k}.
\end{equation}
Here $u_i$, for $i=1,\dots k$, are the first $k$ singular vectors of $S$.

Model order reduction is often studied in the parametric setting, where the vector $u,u_0$, and the right hand side function $f$ of \eqref{eq:1} are of the form $u(t;\mu)$, $u_0(\mu)$, and $f(t,u;\mu)$, respectively. Here $\mu$ belongs to $\mathbb P$, a closed subset of $\mathbb R^d$. In this case, the reduced system can recover quantities of interest at low cost. Since the nature of time, as a parameter, is different from other spacial and physical parameters, in this paper we solely focus on $t$ as the parameter. Nevertheless, it is straight forward to extend the results of this paper to the parameter setting by using POD in time and parametric space, or by using the POD-greedy \cite{haasdonk2013convergence,hesthaven2015certified,quarteroni2015reduced} method to generate a basis $V_k$.

Since the approximate solution $\tilde u$ is a linear combination of the POD basis vectors, $\tilde u$ inherits linear properties of these basis vectors. However, when the solution $u$ to \eqref{eq:1} satisfies some nonlinear invariants, there is no guarantee that, in general, $\tilde u$ also satisfy such invariants \cite{doi:10.1137/140959602,doi:10.1137/140978922,doi:10.1137/17M1111991,MaboudiAfkham2018}. This results in a qualitatively wrong and often unstable solution to \eqref{eq:4}. In the later sections, we discuss how the skew-symmetric formulation of the fluid flow allows conservation of quadratic invariants, e.g. the kinetic energy, at the level of the reduced system.

\section{Skew Symmetric and Centered Schemes for Fluid Flows} \label{sec:skew}

In this section we summarize the conservation properties of skew-symmetric forms and discretization schemes, following, closely, the works of \cite{morinishi2010skew,morinishi1998fully,tadmor1984skew,reiss2014conservative}.

\subsection{Conservation Laws} \label{sec:skew.1}
In the context of fluid flows, transport of conserved quantities, can be expressed as
\begin{equation} \label{eq:3.1}
	\frac{\partial }{\partial t} \rho \varphi + \nabla \cdot ( \rho u \varphi  ) = \nabla \cdot F_{\varphi}\quad \text{defined in} \quad \Omega \subset \mathbb R^{d}.
\end{equation}
Here, $d = 1,2$ or $3$, $\rho:\Omega\to \mathbb R$ is the density, $u\in \Omega \to \mathbb R^{d}$ is the velocity vector field, $\varphi$ is a measured scalar quantity of the flow, and $F_{\varphi}$ is the flux function associated to $\varphi$. Integration of \eqref{eq:3.1} over $ \Omega$ yields
\begin{equation} \label{eq:3.2}
	\frac{d}{dt} \int_{\Omega} \rho \varphi \ dx = \int_{\partial \Omega} (F_{\varphi} - \rho u \varphi) \cdot \hat n\ ds,
\end{equation}
where $\partial \Omega$ is the boundary of $\Omega$, and $\hat n$ is the unit outward normal vector to $\partial \Omega$. \edit{This means that the quantity $(\rho\varphi)$ is explicitly conserved over control volumes.} Therefore, \eqref{eq:3.1} is referred to as the \emph{conservative form} and the convective term in \eqref{eq:3.1} is referred to as the \emph{divergence form}. However, using the \emph{continuity equation}
\begin{equation} \label{eq:3.3}
	\frac{\partial }{\partial t} \rho + \nabla \cdot (\rho u) = 0,
\end{equation}
we can rewrite \eqref{eq:3.1} as
\begin{equation} \label{eq:3.4}
	\rho \frac{\partial }{\partial t} \varphi + (\rho u)\cdot \nabla \varphi = \nabla \cdot F_{\varphi}.
\end{equation}
The convective term in this formulation is referred to as the \emph{advective form}. The \emph{skew-symmetric} form of the convective term is obtained by the arithmetic average of the divergent and the advective form:
\begin{equation} \label{eq:3.5}
	\frac{1}{2} \left( \rho \frac{\partial }{\partial t} \varphi + \frac{\partial }{\partial t} (\rho \varphi) \right) + \frac 1 2 \left( (\rho u)\cdot \nabla \varphi + \nabla \cdot (\rho u \varphi) \right) = \nabla \cdot F_{\varphi}.
\end{equation}
Multiplying \eqref{eq:3.5} with $\varphi$ yields
\begin{equation}
	\frac{\partial }{\partial t} \rho \varphi^2 + \nabla \cdot ( \rho u \varphi^2  ) = \varphi \nabla \cdot F_{\varphi}.
\end{equation}
\edit{Therefore, $\rho \varphi^2$} is a conserved quantity for a flux-free $\varphi$. Since the divergence, the advective and the skew-symmetric forms are identical at the continuous level, $\varphi^2$ is a conserved quantity for all forms. However, the equivalence of these forms is not preserved through a general discretization scheme and we can not expect $\varphi^2$ to be a conserved quantity at the discrete level. To motivate numerical advantages of the skew-symmetric form consider the operator 
\begin{equation}
	S_{\rho u}(\cdot) = \frac 1 2 ( [ \nabla \cdot \rho u ] + (\rho u)\cdot \nabla )(\cdot).
\end{equation}
With a proper set of boundary condition, this operator is a skew-adjoint operator on $L^2$. Here, $[\cdot]$ indicates that the inside of the brackets act as a differential operator. This skew-adjoint property is used later to show the conservation of some quadratic quantities in \eqref{eq:3.1}. Similarly, we can define a skew-adjoint operator with respect to the time variable as
\begin{equation}
	S_{\rho,\partial_t} = \frac{1}{2} \left( \rho \frac{\partial}{\partial t} + [ \frac{\partial}{\partial t} \rho] \right).
\end{equation}
Here, the subscript $\partial t$ is to emphasize that $S_{\rho,\partial_t}$ is a differential operator with respect to $t$. A proper time and space discretization of $S_{\rho u}$ and $S_{\rho,\partial_t}$ can preserve the skewness property.

Numerical time integration of \eqref{eq:3.5} can be challenging since the time differentiation of different variables is present. Following \cite{morinishi2010skew}, we rewrite \eqref{eq:3.5} as
\begin{equation} \label{eq:3.6}
	\sqrt{\rho } \frac{\partial }{\partial t} (\sqrt \rho \varphi ) + S_{\rho u}(\varphi) = \nabla \cdot F_{\varphi}.
\end{equation}
Time integration of this form is presented in \cite{morinishi2010skew,reiss2014conservative}. Note that one can also generate a quasi-skew-symmetric form \cite{blaisdell1991numerical,morinishi2003dns} of \eqref{eq:3.1} as
\begin{equation} \label{eq:3.7}
	\frac{\partial }{\partial t} (\rho \varphi) + \edit{ \frac 1 2 \left( \nabla \cdot(\rho u \varphi) + \rho u \cdot \nabla \varphi + \varphi \nabla \cdot(\rho u) \right) } = \nabla \cdot F_{\varphi}.
\end{equation}
Even though this is not a fully skew-symmetric form (skew-symmetric only in space), the numerical stability of this form is significantly better than the divergence and advective form \cite{morinishi2010skew,blaisdell1991numerical,morinishi2003dns}. Note that this quasi-skew-symmetric form is identical to the skew-symmetric form in the incompressible limit.

\subsection{Incompressible Fluid} \label{sec:skew.2}
Consider the governing equations of an incompressible fluid with skew-symmetric convective term:
\begin{equation} \label{eq:3.8}
	\left\{
	\begin{aligned}
	&\nabla \cdot u = 0, \\
	&\frac{\partial}{\partial t} u + S_{u}(u) + \nabla p = \nabla \cdot \tau,
	\end{aligned}
	\right.
\end{equation}
defined on $\Omega$. Here, $p: \Omega \to \mathbb R^+$ is the pressure, $\tau: \Omega \to \mathbb R^{d\times d}$ is the viscous stress tensor, and $S_u = \frac 1 2 ([ \nabla \cdot u] + u\cdot \nabla)$. It is straight forward to check
\begin{equation} \label{eq:3.9}
	\frac{d}{dt} K + \nabla \cdot (Ku) + \nabla \cdot (pu)= \nabla \cdot (\tau u) - (\tau \nabla)\cdot u,
\end{equation}
where $K = \frac 1 2 \sum_{i=1}^d u_i^2 $ is the kinetic energy and we used 
\begin{equation} \label{eq:3.11}
	u\cdot S_{u}(u) = \nabla \cdot(Ku).
\end{equation}
The only non-conservative term in \eqref{eq:3.9} is $-(\tau \nabla)\cdot u$, which corresponds to dissipation of kinetic energy. Therefore, in the absence of the viscous terms, $K$ is a conserved quantity of the system, and $\frac d {dt} \int_{\Omega} K \ dx <0$ when $\tau\neq 0$. Note that as long as $\nabla \cdot u = 0$, as discussed in \Cref{sec:skew.1}, the divergence, the convective, and the skew-symmetric forms are identical for the incompressible fluid equation. Thus, kinetic energy is conserved for all forms. However, for a general discretization scheme, these forms are not identical and often conservation of kinetic energy (in the discrete sense) may be violated.

A skew-symmetric discretization of \eqref{eq:3.8} is a centered scheme that exploits the skew-adjoint property of $S_u$, and ensures conservation of kinetic energy at the discrete level. We uniformly discretize $\Omega$ into $N$ points and denote by $\mathbf u \in \mathbb R^{N\times d}$, $\mathbf p \in \mathbb R^N$, and $T \in R^{N\times d\times d} $ the discrete representation of $u$, $p$, and $\tau$, respectively. Let $D_j$ be the centered finite difference scheme for $\partial / \partial x_j$, and for $j = 1,\dots,d$. The momentum equation in \eqref{eq:3.8} is discretized as
\begin{equation} \label{eq:3.13}
	\frac{d}{dt}{\mathbf u}_i + S_{\mathbf u} \mathbf u_i + D_i \mathbf p = \sum_{j=1}^d D_j T_{ij}, \quad i=1,\dots,d,
\end{equation}
where $S_{\mathbf u}$ is the discretization of $S_{u}$ given by
\begin{equation} \label{eq:3.14}
	S_{\mathbf u} = \sum_{j=1}^d D_j U_j + U_j D_j,
\end{equation}
and $U_i$ contains components of $\mathbf u_i$ on its diagonal. We require $D_i$ to satisfy
\begin{enumerate}
	\item $D_i = -D_i^T$
	\item $D_i \mathbf 1 = \mathbf 0$, where $\mathbf 1$ and $\mathbf 0$ are vectors of ones and zeros, respectively.
\end{enumerate}
Conditions 1 and 2 yield
\begin{equation} \label{eq:3.15}
	S_{\mathbf u} = -S_{\mathbf u}^T, \quad \mathbf 1^T S_{\mathbf u} \mathbf u_i = 0, \quad i=1,\dots,d.
\end{equation}
Conservation of momentum in the discrete sense is expressed as
\begin{equation} \label{eq:3.16}
	\frac{d}{dt} \sum_{i=1}^d  \mathbf 1^T \mathbf u_i = \sum_{i=1}^d \left( - \mathbf 1^T S_{\mathbf u} \mathbf u_i - \mathbf 1^T D_i \mathbf p + \sum_{j=1}^d \mathbf 1^T D_j T_{ij}  \right) = 0.
\end{equation}
Similarly, it is verified that
\begin{equation} \label{eq:3.17}
\frac{d}{dt} \sum_{i=1}^d \left( \frac 1 2 \mathbf u_i^T \mathbf u_i \right) = - \sum_{i,j=1}^d T_{ij}D_j \mathbf u_i \leq 0.
\end{equation}
Conditions 1 and 2 for $D_i$ are easily checked for a centered finite differences scheme on a periodic domain. For other types of boundaries, e.g., wall boundary and inflow/outflow, we refer the reader to \cite{morinishi1998fully,desjardins2008high} for the construction of the proper discrete centered differentiation operator. We note that the finite differences schemes are chosen here for illustration purposes. It is easily checked that any discrete differentiation operator that satisfies discrete integration by parts, e.g. summation by part (SBP) methods and discontinuous Galerkin (DG) methods, also satisfies conditions 1 and 2 and can be used to construct a skew-symmetric discretization.

\subsection{Compressible Fluid} \label{sec:skew.3}
Consider the equations governing the evolution of a compressible fluid in a skew-symmetric form in one spacial dimension
\begin{equation} \label{eq:3.18}
\left\{
\begin{aligned}
	&\frac{\partial}{\partial t} \rho + \frac{\partial }{\partial x}(\rho u) = 0, \\ 
	& S_{\rho,\partial_t}(u)+ S_{\rho u}(u) + \frac{\partial }{\partial x} p = \frac{\partial }{\partial x} \tau, \\
	&\frac{\partial}{\partial t} \rho E + \frac{\partial}{\partial x}(u E + up) = \frac{\partial }{\partial x}(u\tau - \phi).
\end{aligned}
\right.
\end{equation}
Here $E= e + u^2/2$ is the total energy per unit mass, with $e = {p}/{\rho(\gamma - 1)}$ being the internal energy, $\gamma$ the adiabatic gas index, and $\phi = -\lambda \frac{\partial T}{\partial x}$ is the heat flux, with $\lambda$ as the heat conductivity. The remaining variables are the same as those discussed in \Cref{sec:skew.2}. Following \cite{reiss2014conservative}, the evolution of the momentum equation is
\begin{equation} \label{eq:3.19}
	\begin{aligned}
	\frac{\partial}{\partial t}(\frac{\rho u^2}{2}) + \frac{\partial }{\partial x}(\rho u \frac{u^2}{2}) &= \frac 1 2 u( \frac{d}{dt} \rho u + \rho \frac{d}{dt} u ) + \frac 1 2 u ( [ \frac{\partial}{\partial x} \rho u ] u + \rho u \frac{\partial }{\partial x} u ) \\
	& = - u \frac{\partial}{\partial x} p + u \frac{\partial}{\partial x} \tau.
	\end{aligned}
\end{equation}
Substituting this into the energy equation in \eqref{eq:3.18}, while assuming a constant adiabatic index, yields
\begin{equation} \label{eq:3.20}
	\frac{1}{\gamma -1} \frac{d}{dt} p + \frac{\gamma}{\gamma -1} \frac{\partial }{\partial x} up - u \frac{\partial }{\partial x}(p) = - u \frac{\partial}{\partial x} \tau + \frac{\partial }{\partial x}(u\tau - \phi).
\end{equation}
We discretize the real line, uniformly, into $N$ grid points and denote by $\mathbf r, \mathbf u, \mathbf p \in \mathbb R^{N}$, the discrete representations of $\rho$, $u$, and $p$, respectively. Using the matrix differentiation operator $D\in \mathbb R^{N\times N}$ (we omit the subscript ``$i$'' for the one dimensional case), introduced in \Cref{sec:skew.2}, we define the skew-symmetric matrix operator $S_{\mathbf r \mathbf u} = \frac 1 2 (DUR + RUD)$, where $R$ is the matrix that contains $r$ in its diagonal. Semi-discrete expression of \eqref{eq:3.18} and \eqref{eq:3.20} takes the form
\begin{equation} \label{eq:3.21}
\left\{
\begin{aligned}
	& \frac{d}{dt} \mathbf r + DU\mathbf r = 0, \\
	& S_{\mathbf r,\partial_t} (\mathbf u) + S_{\mathbf r \mathbf u} \mathbf u + D \mathbf p = D T, \\
	&\frac{1}{\gamma -1} \frac{d}{dt} \mathbf p + \frac{\gamma}{\gamma -1} D U \mathbf p - UD\mathbf p = - UDT + D(UT - \mathbf \phi).
\end{aligned}
\right.
\end{equation}
Recalling conditions 1 and 2 for $D$, discussed in \Cref{sec:skew.2}, it is easily verified that
\begin{equation} \label{eq:3.22}
	S_{\mathbf r \mathbf u}^T = - S_{\mathbf r \mathbf u}, \quad \mathbf 1^T S_{\mathbf r \mathbf u} \mathbf u = - \mathbf u^T DU \mathbf r.
\end{equation}
Conservation of mass is expressed as
\begin{equation} \label{eq:3.23}
	\frac{d}{dt} (\mathbf 1^T \mathbf r) = - \mathbf 1^T DR\mathbf u = 0. 
\end{equation}
Furthermore, we recover conservation of momentum in the discrete sense as
\begin{equation} \label{eq:3.24}
\begin{aligned}
	\frac{d}{dt}(\mathbf r^T \mathbf u) &= \frac{1}{2} \frac{d}{dt}(\mathbf r^T \mathbf u) + \frac{1}{2} \left( \mathbf r^T \frac d{dt} \mathbf u +\mathbf u^T \frac{d}{dt} \mathbf r \right)\\
	&= \frac{1}{2}u^T \frac d{dt} \mathbf r + \mathbf 1^T S_{\mathbf r,\partial_t} (\mathbf u) \\
	&= -\frac 1 2 \mathbf u^T DU \mathbf r  - \frac 1 2 \mathbf 1^T S_{\mathbf r \mathbf u} \mathbf u - \mathbf 1^T D\mathbf p +  \mathbf 1^T D T = 0.
\end{aligned}
\end{equation}
Here we used \eqref{eq:3.22} and the mass and the momentum equation in \eqref{eq:3.21}. Similarly, for conservation of the total energy, we have
\begin{equation} \label{eq:3.25}
\begin{aligned}
	\frac{d}{dt} \left( \frac{1}{\gamma - 1} \mathbf 1^T \mathbf p + \frac 1 2 \mathbf (R\mathbf u)^T \mathbf u  \right) &= \frac{d}{dt} \left( \frac{1}{\gamma - 1} \mathbf 1^T \mathbf p \right) + \frac 1 2 \mathbf u^T  S_{\mathbf r,\partial_t} (\mathbf u) = 0.
\end{aligned}
\end{equation}
In addition to the conservation of the total energy, the skew-symmetric form of \eqref{eq:3.21} also conserves the evolutions of the kinetic energy:
\begin{equation} \label{eq:3.26}
\begin{aligned}
	\frac{d}{dt} ( \frac 1 2 \mathbf u^T R\mathbf u) = \frac 1 2 \mathbf u^T S_{\mathbf r,\partial_t} (\mathbf u) &= -\mathbf u ^T S_{\mathbf r \mathbf u} \mathbf u + \mathbf u^T D p + \mathbf u^T DT \\
	&= \mathbf u^T D p + \mathbf u^T DT.
\end{aligned}
\end{equation}
Here, we used the skew-symmetry of $S_{\mathbf r \mathbf u}$. Therefore, only the pressure and the viscous terms contribute to a change in the kinetic energy.

We point out that there are other methods to obtain a skew-symmetric form for \eqref{eq:3.18}, that result in the conservation of other quantities. An entropy preserving skew-symmetric form can be found in \cite{sjogreen2010skew}. Furthermore, a fully quasi-skew-symmetric form for \eqref{eq:3.18}, where all quadratic fluxes are in a skew-symmetric form, is shown to minimize aliasing errors \cite{honein2004higher,honein2005numerical}

\subsection{Time integration}
Following \cite{reiss2014conservative,morinishi2010skew} we can construct a fully discrete second order accurate scheme for \eqref{sec:skew.3} as
\begin{equation} \label{eq:3.27}
	\left\{
	\begin{aligned}
	&\frac 1 2 \sqrt{\mathbf r} ^{n+1/2} \frac{\sqrt{\mathbf r}^{n+1} - \sqrt{\mathbf r}^{n}}{\Delta t} + DU^{n+1/2} \mathbf r^{n} = 0, \\
	& \sqrt{\mathbf r} ^{n+1/2}  \frac{\sqrt{ \mathbf R}^{n+1} \mathbf u^{n+1} - \sqrt{\mathbf R}^{n}\mathbf u^n}{\Delta t} + S_{\mathbf r^{n} \mathbf u^n} \mathbf u^{n+1/2}_\alpha + D \mathbf p^{n} = DT^{n}, \\
	& \frac 1 {\gamma -1} \frac{\mathbf p^{n+1} - \mathbf p^n}{\Delta t} + \frac{\gamma}{\gamma -1} D U^{n} \mathbf p^n - U^{n} D \mathbf p^n = - U^{n}D T^{n} + D (U^nT^n - \phi^n),
	\end{aligned}
	\right.
\end{equation}
\edit{and all the variables are stored at the same location with the same resolution (colocated).} Here, \edit{$\mathbf R$ contains elements of $\mathbf r$ on its diagonal,} $\Delta t$ is the time step, superscript $n$ denotes evaluating at $t = n\Delta t$, superscript $n+1/2$ denotes the arithmetic average of a variable evaluated at $t=n\Delta t$ and $t=(n+1)\Delta t$, the square root sign denotes element-wise application of square root, and 
\begin{equation}
	\mathbf u_{\alpha}^{n+1/2} = \frac{\sqrt{\mathbf R}^{n+1} \mathbf u^{n+1} + \sqrt{\mathbf R}^{n} \mathbf u^{n}}{2\sqrt{\mathbf r}^{n+1/2} }.
\end{equation}
As discussed in \cite{reiss2014conservative}, this time discretization scheme preserves the symmetries expressed in \eqref{eq:3.17}, \eqref{eq:3.24}, \eqref{eq:3.25}, and \eqref{eq:3.26}. In the incompressible case, the method reduces to the implicit mid-point scheme \cite{hairer2006geometric}. For further information see \cite{reiss2014conservative,morinishi2010skew}.

\section{Model Reduction of Fluid Flow} \label{sec:mor_skew}
A straight-forward model reduction of \eqref{eq:3.8} and \eqref{eq:3.18} does not, in general, preserve symmetries and conservation laws, presented in \Cref{sec:skew}. In this section we discuss how to exploit the discrete skew-symmetric structure of \eqref{eq:3.13} and \eqref{eq:3.21} to recover conservation of mass, momentum, and energy at the level of the reduced system.

Let $V_{\mathbf r}$, $V_{\mathbf r \mathbf u}$, and $V_{\mathbf u_i}$ be the reduced bases for the snapshots of $\mathbf r$, $R \mathbf u$, and $\mathbf u_i$, respectively. For the one dimensional case, the subscript ``$i$'' is omitted and for an incompressible fluid, $V_{ \mathbf r}$ and $V_{\mathbf r \mathbf u}$ are not computed. For the purpose of simplicity, we assume that all bases have the size $k$. We seek to project $S_{\mathbf u}$ and $S_{\mathbf r \mathbf u}$ onto the reduced space, such that the projection preserves the skew-symmetric property. The projected operators, using a Galerkin projection, read
\begin{equation} \label{eq:4.1}
	S^r _{\mathbf u} = V_{ \mathbf u_i}^T S _{\mathbf u} V_{ \mathbf u_i}, \quad i=1,\dots,d,
\end{equation}
and
\begin{equation} \label{eq:4.2}
	S^r_{\mathbf r ,\partial_t} =V_{\mathbf r \mathbf u}^T  S_{\mathbf r ,\partial_t} V_{\mathbf u}, \quad S^r _{\mathbf r \mathbf u} = V_{\mathbf r \mathbf u}^T  S _{\mathbf r \mathbf u} V_{\mathbf u}.
\end{equation}
Note that $S^r_{\mathbf r ,\partial_t}$ is not computed explicitly. It is clear that $S^r _{\mathbf u}$ is already in a skew-symmetric form. On the other hand, $S^r_{\mathbf r ,\partial_t}$ and $S^r _{\mathbf r \mathbf u}$ are not, in general, skew-adjoint and skew-symmetric, respectively. This can be ensured, however, by requiring $V_{\mathbf r \mathbf u} = V_{\mathbf u}$. We denote such a basis by $V_{\mathbf r \mathbf u, \mathbf u}$.Using \eqref{eq:4.1} and \eqref{eq:4.2}, a Galerkin projection of the momentum equation in \eqref{eq:3.13} and the governing equations for a compressible fluid in \eqref{eq:3.21} take the form
\begin{equation} \label{eq:4.3}
	\frac{d}{dt} {\mathbf u^r}_i + S^r_{\mathbf u} \mathbf u^r_i + V_{\mathbf u_i} ^T D_i \mathbf p = \sum_{j=1}^d V_{k_3, \mathbf u_i}^T D_j T_{ij}(V_{ \mathbf u_i} \mathbf u^r_i), \quad i=1,\dots,d,
\end{equation}
and
\begin{equation} \label{eq:4.4}
\left\{
\begin{aligned}
	& \frac{d}{dt} \mathbf r^r + \sum_{i=1}^k V^T_{\mathbf r}DU_iV_{\mathbf r}\mathbf r^r = 0, \\
	& S^r_{\mathbf r ,\partial_t} + S^r _{\mathbf r \mathbf u} \mathbf u^r + V_{\mathbf r \mathbf u, \mathbf u}^T D V_{\mathbf p} \mathbf p^r = V_{\mathbf r \mathbf u, \mathbf u}^T D T, \\
	&\frac{1}{\gamma -1} \frac{d}{dt} \mathbf p^r + \frac{\gamma}{\gamma -1} V_{\mathbf p}^T D U V_{\mathbf p} \mathbf p^r - V_{\mathbf p}^T UD V_{\mathbf p} \mathbf p^r = - V_{\mathbf p}^T UDT + V_{\mathbf p}^T D(UT - \mathbf \phi),
\end{aligned}
\right.
\end{equation}
respectively. Note that in \eqref{eq:4.4}, dependency of $T$ on $V_{\mathbf r \mathbf u , \mathbf u}$ is not shown for abbreviation. In \eqref{eq:4.3} and \eqref{eq:4.4}, $D_i$ is always multiplied from the left with a basis matrix or a diagonal matrix. Therefore, the telescoping sum, discussed in Condition 2 in \Cref{sec:skew.1}, cannot be used to show conservation of mass and momentum. However, POD preserves linear properties of snapshots. To demonstrate this, let the overscript ``\textasciitilde'' denote the representation of a reduced variable in the high-fidelity space. An approximated variable, e.g. density, can be represented as a linear combination of some snapshots as $\mathbf r \approx \tilde{\mathbf r} = \sum_{i=1}^k c_i \mathbf r_i$, for some snapshots $\mathbf r_i$ and some coefficients $c_i \in \mathbb R$, for $i=1,\dots,k$. Conservation of mass, evaluated by $\tilde{\mathbf r}$, reads
\begin{equation} \label{eq:4.5}
	\frac{d}{dt} \mathbf 1^T \tilde {\mathbf r} = \sum_{i=1}^k c_i  \left( \mathbf 1^T \frac{d}{dt} \mathbf r_i \right) = - \sum_{i=1}^k c_i  \left( \mathbf 1^T DR_i\mathbf u_i \right) = 0,
\end{equation}
where we used the fact that $\mathbf 1^T D = \mathbf 0^T$. Similarly, we recover conservation of momentum
\begin{equation} \label{eq:4.6}
\begin{aligned}
	\frac{d}{dt}(\tilde {\mathbf r}^T \tilde{\mathbf u}) &= \frac{1}{2} \frac{d}{dt}(\tilde{\mathbf r}^T \tilde{\mathbf u}) + \frac{1}{2} \left( \tilde{ \mathbf r }^T \frac d{dt} \tilde{ \mathbf u } + \tilde {\mathbf u}^T \frac{d}{dt} \tilde {\mathbf r} \right)\\
	&= \sum_{i,j=1}^k d_i c_j \left( \mathbf u_i^T \frac{d}{dt} \mathbf r_j + \left( \mathbf r_j^T \frac d{dt} \mathbf u_i +\mathbf u_i^T \frac{d}{dt} \mathbf r_j \right)\right) = 0.\\
\end{aligned}
\end{equation}
Here, $\tilde{\mathbf u} = \sum_{i=1}^k d_i \mathbf u_i$, for some snapshot $\mathbf u_i$ and coefficients $d_i \in \mathbb R$. Denoting by $\{ R \mathbf u\}^r$ the reduced representation of $R\mathbf u$ in basis $V_{\mathbf r \mathbf u , \mathbf u}$, the evolution of kinetic energy is expressed as
\begin{equation} \label{eq:4.7}
	\begin{aligned}
	\frac{d}{dt}\left( \frac 1 2 \tilde{\mathbf u}^T \tilde{ R } \tilde {\mathbf u} \right) &= \frac{d}{dt}\left( \frac 1 2 {\mathbf u^r}^T V_{\mathbf r \mathbf u , \mathbf u}^T V_{\mathbf r \mathbf u , \mathbf u} \{ R \mathbf u\}^r \right) = \frac{d}{dt}\left( \frac 1 2 {\mathbf u^r}^T \{ R \mathbf u\}^r \right) \\
	&= \frac 1 2 \left( {\mathbf u^r}^T \frac{d}{dt} \{ R \mathbf u \}^r + \{ R \mathbf u \}^r \frac{d}{dt} \mathbf u^r \right) \\
	&= \frac 1 2 \left( {\mathbf u^r}^T V_{\mathbf r \mathbf u , \mathbf u}^T V_{\mathbf r \mathbf u , \mathbf u} \frac{d}{dt} \{ R \mathbf u \}^r + \{ R \mathbf u \}^r \frac{d}{dt} V_{\mathbf r \mathbf u , \mathbf u}^T V_{\mathbf r \mathbf u , \mathbf u} \mathbf u^r \right) \\
	&= {\mathbf u^r}^T S^r_{\mathbf r, \partial_t} \mathbf u^r = { \mathbf u^r }^T V_{\mathbf r \mathbf u , \mathbf u} D V_{\mathbf p} \mathbf P^r + { \mathbf u^r }^T V_{\mathbf r \mathbf u , \mathbf u}^T D T.
	\end{aligned}
\end{equation}
In the missing steps in the last line, skew-symmetry of $S_{\mathbf r \mathbf u}^r$ is used. Note, that only the reduced pressure and the viscous term contribute to the evolution of kinetic energy. Furthermore, the quantity $ \frac 1 2 {\mathbf u^r}^T \{ R \mathbf u\}^r$ is the kinetic energy associated with the reduced system \eqref{eq:4.4}, approximating the kinetic energy of the high-fidelity system \eqref{eq:3.21}, and is a quadratic form with respect to the reduced variables. Conservation of kinetic energy for \eqref{eq:4.3} follows similarly. It is  straight-forward to check that
\begin{equation} \label{eq:4.8}
	\frac{d}{dt} \left( \frac{1}{\gamma - 1} \mathbf 1^T \tilde{\mathbf p} + \frac{1}{2} \tilde{\mathbf u}^T \tilde R \tilde{\mathbf u} \right) = 0,
\end{equation}
i.e., the total energy is conserved. We immediately recognize that $ \mathbf p^r /(\gamma - 1)$ is the internal energy of the reduced system. However, the total internal energy of \eqref{eq:4.4} is a weighted sum, $ b^T\mathbf p^r /(\gamma - 1)$, with $b = V_{\mathbf p}^T \mathbf 1$ which is an approximation of the total internal energy in \eqref{eq:3.21}. From \eqref{eq:4.5}, \eqref{eq:4.6}, \eqref{eq:4.7}, and \eqref{eq:4.8} we conclude the following proposition.
\begin{proposition}
	The loss in the mass, momentum and energy associated with the model reduction in \eqref{eq:4.4} is constant in time, and therefore, bounded.
\end{proposition}

\subsection{Assembling Nonlinear Terms and Time Integration}
Nonlinear terms that appear in \eqref{eq:4.3} and \eqref{eq:4.4} are of quadratic nature. These terms can be evaluated exactly using a set of precomputed matrices as proposed in \cite{Benner2018}. As an example, consider
\begin{equation}
	S_{\mathbf u}^r = V^T_{\mathbf u} ( DU + UD ) V^T_{\mathbf u}.
\end{equation}
We write $U$ as a linear combination of matrices as $U = \sum_{j=1}^k \mathbf u ^r_j U_j$, where $\mathbf u ^r_j$ is the $j$th component of $\mathbf u ^r$, and $U_j$ contains the $j$th column of $V_{\mathbf u}$ on its diagonal. It follows
\begin{equation}
	S_{\mathbf u}^r = \sum_{j=1}^k \mathbf u ^r_j \left( V^T_{\mathbf u} ( DU_j + U_jD ) V^T_{\mathbf u} \right).
\end{equation}
The matrices $V^T_{\mathbf u} ( DU_j + U_jD ) V^T_{\mathbf u}$ can be computed prior to the time integration of the reduced system. However, the form of the fully discrete system in \eqref{eq:3.27} introduces cubic and even quartic terms. In principle, the same method can be applied to assemble the nonlinear terms. However, the number of precomputed matrices grows proportional to the order of the nonlinear term.

To accelerate assembly of the nonlinear terms we may approximately evaluate them using the discrete empirical interpolation method (DEIM). This approximation can affect the accuracy of conserved quantities in \eqref{eq:4.4}. Therefore, the accuracy of the DEIM approximation must be chosen higher than the one of POD.

To integrate \eqref{eq:4.4} in time, the fully discrete system \eqref{eq:3.27} is modified prior to model reduction, by dividing the mass and momentum equation with $\sqrt{\mathbf r}^{n+1}$. Note that since the new form is identical to \eqref{eq:3.27}, it does not affect the conserved quantities. Subsequently, a basis for $\sqrt{\mathbf r}$, denoted by $V_{\sqrt{\mathbf r}}$, is constructed. \edit{Since the reduced system shows the same structure of \eqref{eq:3.27},  the same numerical integrator is used to compute the reduced solution, without decoupling the modes related to velocity, density and pressure.} The nonlinear terms are evaluated exactly using the quadratic expansion or approximated using the DEIM.

\section{Numerical Experiments} \label{sec:res}

\subsection{Vortex Merging} \label{sec:res.1}
Consider the 2-dimensional incompressible Euler equation \eqref{eq:3.8} on a square domain $\Omega = [0,2\pi]^2$, with periodic boundary conditions. Spatial derivatives are discretized using a Fourier spectral method. To capture the fine details characterizing the solution, $256\times 256$ modes is used. We consider the evolution of three vortices, with the initial structure given by
\begin{equation}\label{eqn:initial_cond_vort}
\omega = \omega_0 + \sum_{i=1}^{3} \alpha_i e^{-\dfrac{\left(x-x_i\right)^{2}+\left(y-y_i\right)^{2}}{\beta^2}}.
\end{equation}
Here, $\omega = \nabla \times u$ is the vorticity, $(x,y)$ represents the spatial coordinates, $\left( x_i, y_i\right)$ is the center of the $i$th vortex, $\alpha_i$ its maximum amplitude, and $\beta$ controls the effective radius of the vortex. In this example, the center of three vortices are 
\begin{equation}
\left( x_1, y_1 \right) = \left(0.75\pi,\pi\right) , \left( x_2, y_2 \right) = \left(1.25\pi,\pi\right), \left( x_3, y_3 \right) = \left(1.25\pi,1.5\pi\right),
\end{equation}
close to the center of the domain. Two of the vortices have a positive spin with $\alpha_1 = \alpha_2 = \pi$ and the third rotates in the opposite direction with $\alpha_3 = -0.5\pi$. The effective radius of all the vortices is set to $\beta = 1 / \pi$. This arrangement of vortices is an interesting initial condition to study the process of vortex merging. This phenomenon is often a result of fast-moving dipoles of vortices with the same spin facing another vortex \cite{filaments_vort2} of opposite spin. The merging process transfers the vorticity from the initial configuration into long, narrow, and spiral-shaped strips of intense vorticity \cite{filaments_vort}. The formation of such thin vorticity filaments in the fluid may pose numerical challenges, due to aliasing.

In the context of MOR, conservation of energy and stability is crucial to capturing fine structures. With the absence of natural dissipation, straight forward application of MOR techniques for the Euler equation is often unstable.

To define the initial conditions in terms of the velocity components $u$ and the pressure $p$, we define a stream-function $\Psi$, the solution to the equation 
\begin{equation} \label{eq:5.1}
	- \Delta \Psi = \omega.
\end{equation}
The initial velocity is then given by $\nabla \times \Psi$. To solve the stream-function problem \eqref{eq:5.1}, we require $\int_{\Omega} \omega \ dx= 0$. It is easily verified that this requirement implies $\omega_0 = 0.038$. The pressure is recovered by solving the related Poisson pressure equation 
\begin{equation*}
\Delta p = - \nabla \cdot S_{u}(u),
\end{equation*}
obtained by applying the divergence operator to \eqref{eq:3.8} and using the incompressibility condition.
 The implicit midpoint scheme, to mimic the time integration scheme presented in \eqref{eq:3.27}, is used to integrate in time. The merging phenomenon is simulated for a total of $18$ time units using a temporal step $\Delta t=0.004$.

\Cref{compare_different_models} illustrates the evolution of the kinetic energy for the advective, divergence, and the skew-symmetric form of the high-fidelity system. It is observed that only the skew-symmetric form preserves the kinetic energy, confirming the discussion in \Cref{sec:skew.2}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% Comparison Skew symmetric, divergence and advective form %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \centering
  \begin{subfigure}[]{0.47\linewidth}
            \includegraphics[scale=1]{Figures/paper-figure0.pdf}
%  \begin{tikzpicture}[scale=0.58]
%    \begin{axis}[ylabel=$K$,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=south west,
%                 legend entries={Skew Symmetric form, Divergence form, Advective form},
%                 legend style={font=\large},
%                 width=1.4\linewidth, 
%                 height=1\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=4},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_skew_symmetric.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_divergence.txt};
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Incompressible_Euler/Energy_compare_formulations/energy_convective.txt};
%    \end{axis}%  
%  \end{tikzpicture}
\caption{}
\label{compare_different_models}
\end{subfigure}
  \begin{subfigure}[]{0.47\linewidth}
            \includegraphics[scale=1]{Figures/paper-figure1.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
%                 xlabel=Basis POD,
%                 label style={font=\Large},
%                 %legend pos=north east,
%                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 ymin=0,
%                 ymax = 2,
%                 samples = 100]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = s] {./data/Incompressible_Euler/Singular_values/sv.txt};
%    \end{semilogyaxis}
%\end{tikzpicture}
\caption{}
\label{singular_values_decay}
\end{subfigure}
  \caption{(\protect\subref{compare_different_models}) The kinetic energy $K$ for the advective, divergence and the skew-symmetric formulations. (\protect\subref{singular_values_decay}) The decay of the singular values for the vortex merging. }
  \label{fig:unstable_full_models}
\end{figure}
A total of $5000$ temporal snapshots is used to construct a reduced basis, following the process discussed in \Cref{sec:mor}. The decay of the singular values, used as an indication of the reducibility of the problem, is presented in \Cref{singular_values_decay}. The first $35$ POD modes corresponds to over $99\%$ of the modes of the high fidelity solution. This suggests that an accurate reduced system can be constructed using a small number of basis vectors. To illustrate the effectiveness of the method, smaller bases are also considered.

For a qualitative analysis, in Figure \ref{fig:snap_solution_incompressible_Euler}, four solutions at different times are shown for the high fidelity system and the reduced system with $k=17$ and $k=35$ modes. The overall dynamics of the problem, and in particular the formation and development of vorticity filaments, are correctly represented, even with a moderate number of basis vectors. Although small details are not captured by the reduced system with a small number of basis vectors, the position and the spreading of the vortices are comparable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% Snapshots of merging process %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_2.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_2.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_2.png}\\

\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_3.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_3.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_3.png}\\

\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_4.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_4.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_4.png}\\

\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_17_5.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/red_35_5.png}\hspace{1em}
\includegraphics[scale=0.06]{data/Incompressible_Euler/Snapshots/Full_5.png}

\caption{Snapshots of the high-fidelity system and the reduced system at $t=\left\{ 4,8,12,18 \right\}$. From left to right: the solution of the reduced model with $k=17$, $k=35$ and the high fidelity solution.}
\label{fig:snap_solution_incompressible_Euler}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Singular values decay merging vorteces %%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\Cref{fig:approx_error_incompressible_Euler} shows the $L^2$ error between the high-fidelity solution and the reduced solution. The error decreases, consistently, as the number of basis vectors increases. Furthermore, the accuracy is maintained over the period of time integration.

The conservation of the kinetic energy is presented in \Cref{fig:energy_error_incompressible_Euler}. Even for a small number of basis vectors, where the solution is not well approximated, the kinetic energy remains constant. Furthermore, the error in the kinetic energy, due to MOR, is constant in time. This is central for the robustness of the reduced system during long time-integration.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Approximation error and energy conservation %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\centering
\begin{subfigure}[]{0.47\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure2.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{semilogyaxis}[ylabel = $\| \mathbf{u}-\tilde{\mathbf{u}}\|_2$,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 samples = 100,
%                 cycle list name=exotic]
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_5.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_8.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_11.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_14.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_23.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_26.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_29.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Approximation_Error/err_35.txt};
%    \end{semilogyaxis}
%\end{tikzpicture}
\caption{}
\label{fig:approx_error_incompressible_Euler}
\end{subfigure} \hfill
\begin{subfigure}[]{0.47\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure3.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[ylabel = $|K-\tilde{K}|$,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=south west,
%                 legend entries={$k=5$ , $k=8$, $k=11$, $k=14$, $k=23$, $k=26$, $k=29$, $k=35$},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 ymax = 0.5598,
%                 samples = 100,
%                 cycle list name=exotic]
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_5.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_8.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_11.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_14.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_23.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_26.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_29.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = error] {./data/Incompressible_Euler/Energy_conservation/ene_full_35.txt};
%    \end{axis}
%\end{tikzpicture}
\caption{}
\label{fig:energy_error_incompressible_Euler}
\end{subfigure}
\label{fig:energy_approx_err}
\caption{(\protect\subref{fig:approx_error_incompressible_Euler}) Evolution of $L_2$ error in velocity, between the high-fidelity system and the reduced system. (\protect\subref{fig:energy_error_incompressible_Euler}) Conservation of the kinetic energy.}
\end{figure}

\subsection{2D Kelvin-Helmholtz instability}
Consider the 2-dimensional compressible Euler equation \eqref{eq:3.18} in a periodic square box $[0,1]^2$. Unlike the incompressible example in \Cref{sec:res.1}, a centered finite difference scheme of fourth order is used to discretize \eqref{eq:3.18}. The physical domain is discretized into a grid of $256\times 256$ nodes.

The initial velocity field is given by
\begin{equation*}
\begin{cases}
& \mathbf{r} = 
\begin{cases}
& 2, \text{ if } 0.25<y<0.75,\\
& 1, \text{ otherwise },
\end{cases}
\\
& \mathbf{u}_x = a \sin(4\pi y) \left( e^{-\dfrac{(y-0.25)^2}{2\sigma^2}} + e^{-\dfrac{(y-0.75)^2}{2\sigma^2}} \right),\\
& \mathbf{u}_y = 
\begin{cases}
& 0.5, \text{ if } 0.25<y<0.75,\\
& -0.5, \text{ otherwise },
\end{cases},
\\
& \mathbf{p} = 2.5,\\
\end{cases}
\end{equation*}
where $a=0.1$ and $\sigma=5\sqrt{2}\cdot 10^{-3}$. This corresponds to contacting streams of fluid with different densities. For specific choices of parameters describing the jets, fine structures and vortices emerges at the interface between the streams. Such an instability is referred to as the Kelvin-Helmholtz instability \cite{HHS}.

As centered schemes are often dissipation free, resolving the discontinuous initial data requires some artificial viscosity. In the high-fidelity model, the method discussed in \cite{artificial_dissipation}\edit{, based on a derivative-based model,} is used as an artificial viscosity. However, at the level of the reduced system, this is replaced with a low pass filter on the expansion coefficients of POD basis vectors. \edit{The last $5\%$ of the POD modes are put to zero every $20$ time iterations. The reason for the different treatment is that we want to avoid the reconstruction of the derivative of the solution in the full space during the integration of the reduced system.}

The fully discrete skew-symmetric form \eqref{eq:3.27} is used as a time marching scheme with $\Delta t = 5 \cdot 10^{-4}$ over a period of $1$ time unit.
\edit{A total of $500$ snapshots have been used for the computation of the basis in the offline stage.}

\Cref{fig:error_decay_KH} illustrates that the accuracy of the method consistently improves as a higher number of POD basis modes are considered. Furthermore, the skew-symmetric form preserves the accuracy over the period of time integration. It is observed in \Cref{fig:snap_solution_KH} that all features of the flow are correctly represented in the reduced system, even with a low number of basis vectors.

\begin{figure}[t]
\centering
\begin{subfigure}[]{0.48\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure4.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{semilogyaxis}[xlabel=$t$,
%                 ylabel=$e(t)$,
%                 label style={font=\Large},
%                 legend pos=outer north east,
%                 legend style={font=\large},
%                 legend entries={$k=200$,$k=300$,$k=400$,$k=500$,$k=600$},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 cycle list name=exotic]
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_200.txt};  
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_300.txt};      
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_400.txt}; 
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_500.txt};      
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/error/error_600.txt};               
%    \end{semilogyaxis}%  
%  \end{tikzpicture}
\end{subfigure}
\caption{Evolution in time of the error  between the high fidelity solution of the Kelvin-Helmoltz and the reduced solution for different number of basis $k$. As error measure we use $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{u_xr}-\mathbf{u_xr}^r\|^2 + \|\mathbf{u_yr}-\mathbf{u_yr}^r\|^2 + \|\mathbf{p}-\mathbf{p}^r\|^2}$.}
\label{fig:error_decay_KH}
\end{figure}

Conservation of mass, momentum and energy is presented in \Cref{fig:conservation_DEIM}. The accuracy of the method in approximating these invariants improves as the size of the basis is increased. Furthermore, \Cref{energy_error_KH} shows how the kinetic energy associated with the reduced system mimic the kinetic energy of the high-fidelity system. This helps to ensure the correct evolution of kinetic energy, and thus, the internal energy.

\begin{figure}
  \centering
  \begin{subfigure}[]{0.48\linewidth}
            \includegraphics[scale=1]{Figures/paper-figure5.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{semilogyaxis}[ylabel = error in mass,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 legend entries={$k=200$ ,$k=300$, $k=400$,$k=500$,$k=600$},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 cycle list name=exotic]
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_200.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_300.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_400.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_500.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/mass_red_600.txt};
%    \end{semilogyaxis}%  
%  \end{tikzpicture}
  \caption{}
  \label{mass_error_KH}
  \end{subfigure}\hfill
  \begin{subfigure}[]{0.48\linewidth}
            \includegraphics[scale=1]{Figures/paper-figure6.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{semilogyaxis}[ylabel = error in total momentum,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=north east,
%%                 legend entries={$k=200$ Conv,$k=201$ Conv},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 cycle list name=exotic]
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_200.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_300.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_400.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_500.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/momentum_red_600.txt};
%    \end{semilogyaxis}%  
%  \end{tikzpicture}
  \caption{}
  \label{momentum_error_KH}
  \end{subfigure}

  \begin{subfigure}[]{0.48\linewidth}
            \includegraphics[scale=1]{Figures/paper-figure7.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{semilogyaxis}[ylabel = error in total energy,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=north east,
%%                 legend entries={$k=200$ Conv,$k=201$ Conv},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 cycle list name=exotic]
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_200.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_300.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_400.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_500.txt};
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/KH/conserved_quantities/energy_red_600.txt};
%    \end{semilogyaxis}%  
%  \end{tikzpicture}
   \caption{}
  \label{energy_error_KH}
  \end{subfigure}
\caption{Difference between the high fidelity solution of the Kelvin-Helmholtz problem and the reduced solution of the mass (\protect\subref{mass_error_KH}), the momentum (\protect\subref{momentum_error_KH}), and the total energy (\protect\subref{energy_error_KH}).}
\label{fig:conservation_DEIM}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% Snapshots of KH %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[h!]
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_307.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_307.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_307.png}\\

\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_461.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_461.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_461.png}\\

\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_614.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_614.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_614.png}\\

\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_200_768.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_500_768.png}\hspace{1em}
\includegraphics[scale=0.115]{data/Compressible_Euler/KH/Snapshots/density_exact_768.png}

\caption{Solutions of the Kelvin-Helmholtz problem at $t=\left\{ 0.4, 0.6, 0.8, 1 \right\}$. From left to right we show the solution of the reduced model with $k=200$, $k=500$ and the high fidelity solution.}
\label{fig:snap_solution_KH}
\end{figure}

\subsection{1D Shock problem}
In this section we study the 1-dimensional compressible Euler problem, \eqref{eq:3.18} without viscous terms, with a steady state discontinuous solution. This is in preparation for \Cref{sec:5.res.4}, where development and propagation of shock waves is discussed. Here we asses how the skew-symmetric form of \eqref{eq:3.18} can recover moving discontinuities at the level of the reduced system. Consider a periodic boundary conditions on $\Omega = [0,1]$ with the initial condition
\begin{equation*}
\begin{cases}
& \mathbf{r} = 0.5+0.2 \cos(2\pi x),\\
& \mathbf{u} = 1.5,\\
& \mathbf{p} = 0.5+0.2 \sin(2\pi x).\\
\end{cases}
\end{equation*}
The domain is discretized into $N=2000$ nodes and a centered finite differences scheme is used to assemble the discrete Euler equation in skew-symmetric form, as discussed in \Cref{sec:skew.3}.

The fully discrete skew-symmetric form \eqref{eq:3.27} is used for time integration over a time interval $[0,0.3]$. To resolve the discontinuous solution we use an artificial viscosity with $\tau = \mu \partial u / \partial x$, where $\mu = 0.5 \cdot 10^{-4}$. \edit{Regarding the reduction procedure, $1000$ snapshots of the numerical solution given by the high fidelity method have been collected.}

		\Cref{fig:energy_pres_1D} shows the evolution of conserved quantities for the high-fidelity and reduced system. Here, the high-fidelity model is also considered in the divergence and advective form in addition to the skew-symmetric form. It is clear that when the reduced systems is not in skew-symmetric form, it violates conservation of mass, momentum, and energy. Even while the high-fidelity systems in divergence and advective forms are stable, the constructed reduced system is unstable, independent on the number of basis vectors. On the other hand, the skew-symmetric form yields a stable and conservative reduce system. Note that the loss in the energy associated with the skew-symmetric form, illustrated in \Cref{conservation_1D_focus}, is due to the application of an artificial viscosity.

\Cref{error_behaviour_1D} shows the total error, when the reduced system captures a discontinuous solution at $t=0.16$. It is observed that the formation of a discontinuity affects the accuracy of the method. This is expected as a sharp gradient is approximated by a relatively few POD modes. However, the method remains robust and stable during the period of time integration.

In \Cref{fig:snaps_1D_Euler} we compare the numerical artifacts of different formulations of the Euler equation. The advective formulation is not presented since it does not yield a stable reduced system. It is observed that the reduced system based on the skew-symmetric formulation accurately represent the overall behavior of the high-fidelity solution. On the other hand, a Gibbs-type error \cite{thompson1992fourier} appears near sharp gradients, for the reduced system based on the divergence form of the Euler equation. The well-representation of the skew-symmetric form is due the low aliasing error property.

As discussed in \Cref{sec:mor_skew}, the DEIM approximation needed for an efficient evaluation of the nonlinear components of \eqref{eq:3.18}, can affect the conservation properties of the skew-symmetric form. \Cref{fig:singular_values_decay_1D} shows the decay of the singular values of the nonlinear snapshots. The decay of these snapshots is significantly slower than the temporal snapshots of \eqref{eq:3.18}. This indicates that to maintain the accuracy of the reduced system, the DEIM basis should be chosen richer than the POD basis. \Cref{error_DEIM} and \Cref{energy_DEIM} present the error and the conservation of total energy when the DEIM is used to approximate the nonlinear term. The conservation of energy is recovered once DEIM approximates the nonlinear terms with enough accuracy. 
In this numerical experiment, evaluation of the nonlinear terms in \eqref{eq:3.18} using the DEIM is ten times faster than the high-fidelity evaluation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Mass, Total momentum & Energy %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  % MASS
  \begin{subfigure}[]{0.48\linewidth}
            \includegraphics[scale=1]{Figures/paper-figure8.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[ylabel = Mass,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 ymin=0,
%                 ymax = 2,
%                 samples = 100]
%                 \addplot[color=red,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/mass_102_1.txt};
%                 \addplot[color=blue,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/mass_201_1.txt};
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/mass_102_1.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/mass_201_1.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_102_1.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_201_1.txt};
%    \end{axis}%  
%  \end{tikzpicture}
  \end{subfigure}\hfill% 
  % MASS (focus)
  \begin{subfigure}[]{0.48\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure9.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=south west,
%                 legend entries={$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 ymax=0.5000001]
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_24_1.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_102_1.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/mass_201_1.txt};
%    \end{axis}%  
%  \end{tikzpicture}
  \end{subfigure}
 % TOTAL MOMENTUM
  \begin{subfigure}[]{0.48\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure10.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[ylabel = Momentum,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 ymin=1,
%                 ymax = 2,
%                 samples = 100]
%                 \addplot[color=red,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/momentum_102_1.txt};
%                 \addplot[color=blue,style=dashdotted,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/momentum_201_1.txt};
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/momentum_102_1.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/momentum_201_1.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_102_1.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_201_1.txt};
%    \end{axis}%  
%  \end{tikzpicture} 
  \end{subfigure}\hfill% 
 % TOTAL MOMENTUM (focus)
  \begin{subfigure}[]{0.48\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure11.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=south west,
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 ymax=1.04963,
%                 scale only axis]
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_24_1.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_102_1.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/momentum_201_1.txt};
%    \end{axis}%  
%  \end{tikzpicture}
  \end{subfigure}
 % ENERGY
  \begin{subfigure}[]{0.48\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure12.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[ylabel = Energy,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 %legend entries={$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 ymin=2.5,
%                 ymax = 4.5,
%                 samples = 100]
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/energy_102_1.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/convective_data/energy_201_1.txt};                
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/energy_102_1.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/divergence_data/energy_201_1.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_102_1.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_201_1.txt};
%    \end{axis}%  
%  \end{tikzpicture} 
  \caption{}
  \label{conservation_1D}
  \end{subfigure}\hfill% 
 % ENERGY (focus)
  \begin{subfigure}[]{0.48\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure13.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=south west,
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 ymax = 2.87438]
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_24_1.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_102_1.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/skew_symm_data/energy_201_1.txt};
%    \end{axis}%  
%  \end{tikzpicture}
  \caption{}
  \label{conservation_1D_focus}
  \end{subfigure}
  \caption{(\protect\subref{conservation_1D})  Evolution of the three conserved quantities for the reduced solution of the compressible Euler equation (mass, total momentum and total energy).  The divergent, advective and skew-symmetric formulations have been considered and $k=102,204$ basis are used in the reduced model. (\protect\subref{conservation_1D_focus}) Evolution of the conserved quantity for a stable reduced model using the skew-symmetric formulation.} 
  \label{fig:energy_pres_1D}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%% Approximation Error %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\begin{subfigure}[]{0.48\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure14.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{semilogyaxis}[xlabel=$t$,
%                 ylabel=$e(t)$,
%                 label style={font=\Large},
%                 legend pos=outer north east,
%                 legend style={font=\large},
%                 legend entries={$k=75$,$k=126$,$k=177$,$k=225$,$k=276$,$k=327$,$k=375$,$k=426$},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 cycle list name=exotic]
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_75.txt};  
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_126.txt};      
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_177.txt}; 
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_225.txt};      
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_276.txt};  
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_327.txt}; 
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_375.txt};      
%                 \addplot+[style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error/error_426.txt};              
%    \end{semilogyaxis}%  
%  \end{tikzpicture}
\end{subfigure}
\caption{Evolution in time of the error  between the high fidelity solution of the 1D compressible Euler and the reduced solution for different number of basis $k$. As error measure we consider $e(t)=\sqrt{\|\mathbf{r}-\mathbf{r}^r\|^2+\|\mathbf{ur}-\mathbf{ur}^r\|^2+\|\mathbf{p}-\mathbf{p}^r\|^2}$.}
\label{error_behaviour_1D}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Snapshot of pressure and density %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
\begin{subfigure}[t]{0.47\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure15.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[xlabel=$x$,
%                 ylabel=Density,
%                 label style={font=\large},
%                 %legend pos=south west,
%                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 legend style={at={(axis cs:0.375,0.45)},anchor=south west},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_300.txt};
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_300.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_300.txt};
%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_300.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_300.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_300.txt};
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_300.txt};
%    \end{axis}% 
%\end{tikzpicture}
\end{subfigure} 
\begin{subfigure}[t]{0.47\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure16.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[xlabel=$x$,
%                 ylabel=Pressure,
%                 label style={font=\large},
%                 legend pos=south west,
%                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_300.txt};
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_300.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_300.txt};
%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_300.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_300.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_300.txt};
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_300.txt};
%    \end{axis}% 
%\end{tikzpicture}
\label{density_reduction}
\end{subfigure}

\begin{subfigure}[]{0.47\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure17.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[xlabel=$x$,
%                 ylabel=Density,
%                 label style={font=\large},
%                 legend pos=north east,
%                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_1000.txt};
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_1000.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_1000.txt};
%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_1000.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_1000.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_1000.txt};
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_1000.txt};
%    \end{axis}% 
%\end{tikzpicture}
\end{subfigure} 
\begin{subfigure}[]{0.47\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure18.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[xlabel=$x$,
%                 ylabel=Pressure,
%                 label style={font=\large},
%                 legend pos=south west,
%                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_1000.txt};
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_1000.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_1000.txt};
%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_1000.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_1000.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_1000.txt};
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_1000.txt};
%    \end{axis}% 
%\end{tikzpicture}
\end{subfigure}

\begin{subfigure}[]{0.47\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure19.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[xlabel=$x$,
%                 ylabel=Density,
%                 label style={font=\large},
%                 legend pos=north east,
%                 legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_exact_3000.txt};
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_24_3000.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_102_3000.txt};
%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_unstable_201_3000.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_24_3000.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_102_3000.txt};
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/density_approx_201_3000.txt};
%    \end{axis}% 
%\end{tikzpicture}
\caption{}
\label{density_reduction_1D}
\end{subfigure} 
\begin{subfigure}[]{0.47\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure20.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[xlabel=$x$,
%                 ylabel=Pressure,
%                 label style={font=\large},
%                 legend pos=south west,
%                 %legend entries={HF,$k=24$ Div,$k=102$ Div,$k=201$ Div,$k=24$ Skew,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_exact_3000.txt};
%                 \addplot[color=red,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_24_3000.txt};
%                 \addplot[color=blue,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_102_3000.txt};
%                 \addplot[color=black!50!green,style=dashed,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_unstable_201_3000.txt};
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_24_3000.txt};
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_102_3000.txt};
%                 \addplot[color=black!50!green,style=solid,style=ultra thick]  table[x = time, y = energy] {./data/Compressible_Euler/1D/Snapshots/pressure_approx_201_3000.txt};
%    \end{axis}% 
%\end{tikzpicture}
\caption{}
\label{pressure_reduction_1D}
\end{subfigure}
\caption{Qualitative comparison between different formulations for the reduced model in terms of density (\protect\subref{density_reduction_1D})  and pressure(\protect\subref{pressure_reduction_1D}) at $t=0.1,0.3$ and $1$s. Results for the advective formulation are not showed here because the related reduced solutions are unstable after a few time steps.}
\label{fig:snaps_1D_Euler}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Singular values 1D problem %%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
        \includegraphics[scale=1]{Figures/paper-figure21.pdf}
%\begin{tikzpicture}[scale=0.5452]
%    \begin{semilogyaxis}[ylabel = $\frac{\sigma_j}{\sum_i \sigma_i}$,
%                 xlabel=Basis,
%                 label style={font=\Large},
%                 legend style={font=\large},
%                 legend entries = {POD,DEIM},
%                 grid=both,
%                 ticks=both,
%                 width=0.7\linewidth, 
%                 height=0.5\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 samples = 100,
%                 xtick = {400, 800, 1200, 1600}]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = n, y = sing_values] {./data/Compressible_Euler/1D/Singular_values/sv.txt};
%                 \addplot[color=black,style=dashed,style=ultra thick]  table[x = n, y = sv] {./data/Compressible_Euler/1D/Singular_values/sv_DEIM.txt};
%    \end{semilogyaxis}
%\end{tikzpicture}
\caption{Decay of the singular values of the snapshot matrix related to POD and DEIM algorithms for the 1D compressible Euler problem.}
\label{fig:singular_values_decay_1D}
\end{figure}

\begin{figure}[h!]
\centering
\begin{subfigure}[]{0.47\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure22.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[ylabel = e(T),
%                 xlabel=Basis DEIM,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 legend entries={POD+DEIM,POD},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1\linewidth,
%%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 xticklabel style={font = \large},
%%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_DEIM.txt};      
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_POD.txt};
%    \end{axis}
%\end{tikzpicture}
\caption{}
\label{error_DEIM}
\end{subfigure}
\begin{subfigure}[]{0.47\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure23.pdf}
%\begin{tikzpicture}[scale=0.58]
%    \begin{axis}[ylabel = Energy(T),
%                 xlabel=Basis DEIM,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 legend entries={POD+DEIM,POD},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%%                 yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis]
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_energy_DEIM.txt};      
%                 \addplot[color=red,style=solid,style=ultra thick]  table[x = time, y = quantity] {./data/Compressible_Euler/1D/error_DEIM/error_energy_POD.txt};
%    \end{axis}
%\end{tikzpicture}
\caption{}
\label{energy_DEIM}
\end{subfigure}
\caption{Comparison between standard POD and POD with DEIM treatment of the nonlinear term in terms of the error (\protect\subref{error_DEIM}) and the total energy (\protect\subref{energy_DEIM}).}
\label{fig:RIC2}
\end{figure}

\subsection{Continuous Variable Resonance Combustor} \label{sec:5.res.4}

CVRC is a model rocket combustor, designed and operated at Purdue University (Indiana, U.S.) to investigate combustion instabilities \cite{yu2008combustion}. This setup is called the Continuously Variable Resonance Combustor (CVRC) because the length of the oxidizer injector can be varied continuously, allowing for a detailed investigation of the coupling between acoustics and combustion in the chamber \cite{garby2013simulations}. The 2D/3D high-fidelity simulations of CVRC are expensive. Thus to get a fast analysis tool, a quasi-1D model has been proposed by Smith et al. \cite{smith2008computational} and further developed by Frezzotti et al. \cite{frezzotti2015determination,frezzotti2017numerical,frezzotti2018quasi}.

The CVRC consists of three parts: oxidizer post, combustion chamber and exit nozzle, as shown in Fig. \ref{fig:radius}. The oxidizer is injected from the left end of the oxidizer post and meets the fuel, injected through an annular ring around the oxidizer injector, at the back-step. The combustion happens in a region around the back-step. The combustion products flow through the chamber and exit the system from the nozzle.  Both the injector and the nozzle are operated at choked condition during the experiment. The length of the oxidizer post $L_{op}$ of the CVRC can be varied continuously, leading to different dynamics. Here, we focus on the case with $L_{op}= 14.0$ cm, in which the combustion is unstable.

The geometry parameters of the quasi-1D CVRC with a oxidizer post length  $L_{op}= 14.0$ cm are shown in Table \ref{tab:geometry_parameters}.  The back-step and the converging part of the nozzle are sinusoidally contoured to avoid a discontinuity of the radius that will invalidate the quasi-1D governing equations presented in the next subsection.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%% Combustor images %%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering
        \includegraphics[scale=1]{Figures/paper-figure24.pdf}
%\begin{tikzpicture}[]
%    \begin{axis}[width=12cm,
%                 height=4cm,
%                 ylabel = $r(m)$,
%                 xlabel=$x(m)$,
%                 yticklabel style={
%                  /pgf/number format/fixed,
%                  /pgf/number format/precision=5,
%                  style = {font=\normalsize}
%                  },
%                 xticklabel style={
%                  style = {font=\normalsize}
%                  },
%%                 label style={font=\large},
%%                 legend style={font=\large},
%%                 grid=both,
%%                 ticks=both,
%%                 width=0.7\linewidth, 
%%                 height=0.5\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 scaled y ticks = false,
%%                 enlargelimits=false,
%%                 samples = 100,
%                 ymax = 0.04]
%                 \addplot[color=black,style=solid,style=ultra thick]  table[x = x, y = radius] {./data/Combustor/radius_combustor.txt};
%                \node[pin=100:{injector}] at (-0.05,0.01) {};
%                \node[pin=93:{back-step}] at (0.001,0.015) {};
%                \node[pin=90:{chamber}] at (0.2,0.023) {};
%                \node[pin=80:{nozzle}] at (0.4,0.015) {};
%    \end{axis}
%\end{tikzpicture}
\caption{Geometry of quasi-1D CVRC model.}
\label{fig:radius}
\end{figure}

\begin{table} [h]
	\centering
	\caption{Geometry parameters of the quasi-1D CVRC with an oxidizer post length $L_{op}=14$ cm.}
	\centering
	\begin{tabular}{c c c c c c }
		\toprule
		\centering
		\multirow{2}{*}{Section} &
		\multicolumn{2}{c}{Oxidizer post} &
		\multirow{2}{*}{Chamber} &
		\multicolumn{2}{c}{Nozzle} \\
		\cmidrule(lr){2-3} \cmidrule(lr){5-6}
		& injector & back-step & & converging part & diverging part\\
		\midrule
		Length (cm) & 12.99 & 1.01 & 38.1 & 1.27 & 3.4 \\
		Radius (cm) & 1.02  & $1.02 \sim 2.25$ & 2.25 & $2.25 \sim 1.04$ & $1.04 \sim 1.95$ \\
		\bottomrule
		\label{tab:geometry_parameters}
	\end{tabular} 
\end{table}
The fuel is pure gaseous methane. The oxidizer is a mixture of 42\% oxygen and 58\% water (per unit mass), and is injected in the oxidizer post at a temperature $T_{ox}=1030$ K so that both water and oxygen are in the gaseous phase. The operating conditions are listed in Table \ref{tab:operating-conditions}.

\begin{table} [h]
	\centering
	\caption{CVRC operating conditions.}
	\centering
	\begin{tabular}{l l l}
		\toprule
		\centering
		Parameter & Unit & Value \\
		\midrule
		Fuel mass flow rate, $\dot{m}_{f}$ & kg/s & 0.027   \\
		Fuel temperature, $T_{f}$ & K & 300   \\
		Oxidizer mass flow rate, $\dot{m}_{ox}$ & kg/s & 0.32   \\
		Oxidizer temperature, $T_{ox}$ & K & 1030   \\
		$O_2$ mass fraction in oxidizer, $Y_{O_2}$ & -- & 42.4\%   \\
		$H_2O$ mass fraction in oxidizer, $Y_{H_2O}$ & -- & 57.6\%   \\
		Mean chamber pressure & MPa & 1.34 \\
		Equivalence ratio, $E_r$ & -- & 0.8 \\
		\bottomrule
		\label{tab:operating-conditions}
	\end{tabular} 
\end{table}
For the combustion, we consider the one-step reaction model
\begin{equation*}\label{eq:combustion}
CH_4 + 2O_2 \rightarrow CO_2 + 2H_2O.
\end{equation*}
We assume that the fuel reacts instantaneously to form products, allowing us to neglect intermediate species and finite reaction rates. As the equivalence ratio is less than one, there is oxidizer left after the combustion. Therefore, only two species need to be considered: oxidizer and combustion products.

The governing equations that describe the conservation of mass, momentum, and energy of the quasi-1D CVRC flow, are the quasi-1D unsteady Euler equations for multiple species, expressed in conservative form as
\begin{equation}\label{eq:5p2.1}
\frac{\partial }{\partial t} v + \frac{\partial }{\partial x} F_v = s_A + s_f + s_q.
\end{equation}
The conserved variable vector $v$ and the convective flux vector $F$ are
\begin{equation}\label{eq:5p2.2}
v= \left( \begin{gathered}
\rho A  \\
\rho uA  \\
\rho EA  \\
\rho Y_{ox} A \\
\end{gathered} \right), 
F = \left( \begin{gathered}
\rho uA  \\
\left(\rho u^2 + p\right)A  \\
\left(\rho E + p\right)uA  \\
\rho uY_{ox} A \\
\end{gathered} \right),
\end{equation}
where $\rho$ is the density, $u$ is the velocity, $p$ is the pressure, $E$ is the total energy, $Y_{ox}$ is the mass fraction of oxidizer, and $A=A(x)$ is the cross sectional area of the duct. The pressure $p$ can be computed using the conserved variables as
\begin{equation}\label{eq:total-engery}
E = \frac{p}{\rho (\gamma - 1)} + \frac{u^2}{2} - C_p T_{ref},
\end{equation}
where $T_{ref}$ is the reference temperature and is set as 298.15 K. The temperature $T$ is recovered from the equation of state $p = \rho R T$. The gas properties  $C_p$, $R$ and $\gamma$ are computed as $C_p= \sum C_{pi}Y_i$, $R=\sum R_iY_i$ and $ \gamma= C_p/(C_p-R)$, respectively.

The source terms are
\begin{equation} \label{eq:5p2.3}
s_A = \left( \begin{gathered}
0  \\
p \frac{dA}{dx}  \\
0  \\
0 \\
\end{gathered} \right), 
s_f = \left( \begin{gathered}
{\dot \omega}_f  \\
{\dot \omega}_f u  \\
{\dot \omega}_f \left(h_{0}^{f} + \Delta h_{0}^{rel} \right)  \\
{\dot \omega}_{ox} \\
\end{gathered} \right), 
{s_q} = \left( \begin{gathered}
0  \\
0  \\
q'  \\
0 \\
\end{gathered} \right),
\end{equation}
where $\dot{\omega}_f$ is the depletion rate of the fuel, $\dot{\omega}_{ox}$ is the depletion rate of the oxidizer, $h_0^f$ is the total enthalpy of the fuel, $\Delta h_{0}^{rel}$ is the heat of reaction per unit mass of fuel and $q'$ is the unsteady heat release term. $s_A$ accounts for area variations, $s_f$ and $s_q$ are related to the combustion. $s_f$ represents the addition of the fuel and its combustion with the oxidizer, which in turn results in the creation of the combustion products. The depletion rate of the fuel is
\begin{equation}\label{eq:5p2.4}
\dot{\omega}_{f}= \frac{k_f \dot{m}_f Y_{ox} \left(1+sin\xi\right)}{l_f-l_s},
\end{equation} 
where
\begin{equation}\label{eq:5p2.5}
\xi= -\frac{\pi}{2} + 2\pi\frac{x-l_s}{l_f-l_s}, \hspace{0.5cm} \forall \hspace{0.2cm} l_s < x < l_f.
\end{equation}
The setting of the fuel injection restricts the combustion to the region $l_s < x < l_f$. The reaction constant $k_f$ is selected to insure that the fuel is consumed within the specified combustion zone. The depletion rate of the oxidizer is computed by 
\begin{equation}\label{eq:5p2.6}
\dot{\omega}_{ox} = C_{o/f} \dot{\omega}_f,
\end{equation}
where $C_{o/f}$ is the oxidizer-to-fuel ratio.

The unsteady heat release term $q'$, also called the combustion response function, models the coupling between acoustics and combustion. Here, we use the combustion response function designed by Frezzotti et al. \cite{frezzotti2017numerical,frezzotti2018quasi}, which is a function of the velocity, sampled at specific abscissa $\hat{x}$ that is almost coincident with the antinode of the first longitudinal modal shape with a time lag $t_0$, i.e.,
\begin{equation}\label{eq:5p2.7}
q'\left( x,t\right) = \alpha g\left(x\right)  A\left(x\right) \left[ u\left( \hat{x},t-t_0 \right) - \bar{u}\left( \hat{x} \right) \right].
\end{equation}
Here $\bar{u}$ is the time averaged velocity, estimated with the steady-state quasi-1D model assuming $q'=0$, and $g(x)$ is a Gaussian distribution  
\begin{equation}\label{eq:5p2.8}
g\left(x\right)= \frac{1}{\sqrt{2\pi\sigma^2}} \exp\left( -\frac{\left(x-\mu\right)^2}{2\sigma^2} \right),
\end{equation}
where $\mu$ is the mean and $\sigma$ is the standard deviation. The amount of heat release due to velocity oscillations is controlled by the parameter $\alpha$, in \eqref{eq:5p2.7}.

The boundary conditions for the quasi-1D CVRC flow include the fixed mass flow rate and the stagnation temperature at the head-end of the oxidizer injector, and the supersonic outflow at the exit of the nozzle.

Prior to the unsteady simulation, the quasi-1D CVRC needs to be excited, which is achieved by adding a perturbation to the steady-state solution. The perturbation is added by forcing the mass flow rate with a multi-sine signal
\begin{equation}\label{eq:5p2.9}
\dot{m}_{ox} \left(t\right)= \dot{m}_{ox,0} \left[1 + \delta\sum_{k=1}^{K}  sin\left(2\pi k\Delta f t\right) \right],
\end{equation}
where $\dot{m}_{ox,0}$ is the oxidizer mass flow rate in Table \ref{tab:operating-conditions}, $\Delta f$ is the frequency resolution and $K$ is the number of frequencies. In this paper, $\Delta f = 50 $ Hz and $K=140$, resulting in a minimal frequency of 50 Hz and a maximal frequency of 7000 Hz. $\delta$ is required to be small to control the amplitude of the perturbation and is set as 0.1\%.

The procedure of the unsteady simulation of the quasi-1D CVRC flow includes three steps:
\begin{enumerate}
	\item  Compute the steady-state solution by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $ and $q'=0$.
	\item  Excite the system by adding a perturbation to the oxidizer mass flow rate according to (\ref{eq:5p2.7}) and setting $q'=0$.
	\item  Perform the unsteady simulation by turning on the combustion response function $q'$ in (\ref{eq:5p2.3}) and turning off the oxidizer mass flow rate perturbation by setting $\dot{m}_{ox}=\dot{m}_{ox,0} $.	
\end{enumerate}
Introduction of an artificial viscosity is essential for a robust and long time-integration of \eqref{eq:5p2.3}. Common discretization schemes for \eqref{eq:5p2.3} are often dissipative, e.g., the Lax-Friedrich scheme used in \cite{Wang:255719}. Since the skew-symmetric discretization is non-dissipative, we modify \eqref{eq:5p2.3} as
\begin{equation} \label{eq:5p2.10} 
	\frac{\partial }{\partial t} v + \frac{\partial }{\partial x} F = s_A + s_f + s_q + d, \quad d = (0,\frac{\partial }{\partial x} \tau,0,0)^T,
\end{equation}
with $\tau = \mu \partial (u A)/ \partial x$, and $\mu = 6\times 10^{-5}$. This type of artificial viscosity is chosen for its simplicity. This, however, can be replaced with a more moderate and sophisticated method.

Note that the right hand side in \eqref{eq:5p2.10} suggests that, in general, mass, momentum, and energy is not conserved. Furthermore, the complex coupling of the variables in \eqref{eq:5p2.3} and the non-constant adiabatic gas index prohibits the application of complex and implicit time integration schemes. Therefore, a quasi-skew-symmetric form, introduced in \eqref{eq:3.7}, is used for \eqref{eq:5p2.3}. It is straight-forward to check \cite{sjogreen2010skew}, for $t,s\in \mathbb R^{N}$
\begin{equation} \label{eq:5p2.9.1}
	\frac 1 2 \delta_x (st)_j + \frac 1 2 s_j \delta_x (t)_j + \frac 1 2 t_j \delta_x (s)_j = \frac 1 4 \delta_x^+( s_j + s_{j-1} )(t_j + t_{j-1}).
\end{equation}
where $\delta_x (v)_j = \left( v_{j+1} - v_{j-1} \right)/\Delta x$ is centered finite difference approximation of the space derivative and $\delta_x^+ (v_j) = \left( v_{j+1} - v_j \right) /\Delta x$, for some $v\in \mathbb R^{N}$. Therefore,
\begin{equation} \label{eq:5p2.9.2}
	F_{i+1/2}^{\Delta}(s_jt_j,s_{j+1}t_{j+1}) = ( s_j + s_{j-1} )(t_j + t_{j-1}),
\end{equation}
can be interpreted as an approximation of a quadratic flux function at the boundary of two adjacent finite volume cells. A better approximation of the flux in \eqref{eq:5p2.9.2} corresponds to a higher order skew-symmetric form for a quadratic variable $st$ in \eqref{eq:5p2.9.1}. We discretize the real line into N uniform cells of size $\Delta x$. A quasi-skew-symmetric form for \eqref{eq:5p2.10} now takes the form
\begin{equation}
\begin{aligned}
	\frac{d}{dt} q^i_j + \delta^+ F^{\Delta}_{i+1/2}(q^i_jr^i_j,q^i_{j+1}r^i_{j+1}) &- \delta^+ F_d^{\Delta}(d^i_j,d^i_{j+1}) + \delta^+ F_p^{\Delta}(p_j,p_{j+1}) \\
	&= \int_{c_j} s_A + s_f + s_q \ dx.
\end{aligned}
\end{equation}
for $j=1,\dots,N$. Here, $c_j$ is the $j$th cell, $q^i_j = \int_{c_j} v^i \ dx$ is the cell average of the $i$th component of $v$, $F^{\Delta}_p$ is the flux approximation of the pressure term, $F^{\Delta}_d$ is the flux approximation for the viscous term and $r = ( u , u , u , u )^T$.

The three-stage Runge-Kutta (SSP RK3) \cite{jiang1996efficient} is used to integrate \eqref{eq:5p2.10} in time.
The pressure profile for the steady state, with $q'=0$, and the pressure oscillatory mode in the unsteady phase is presented in \Cref{fig:5p2.2a,fig:5p2.2b}, respectively.

%\begin{figure}[t]
%\centering
%\begin{subfigure}[]{0.47\linewidth}
%	\includegraphics[width=\textwidth]{./pic/init_pressure}
%	\caption{} \label{fig:5p2.2a}
%\end{subfigure}
%\begin{subfigure}[]{0.47\linewidth}
%	\includegraphics[width=\textwidth]{./pic/init_osc}
%	\caption{} \label{fig:5p2.2b}
%\end{subfigure} \\
%\begin{subfigure}[]{0.47\linewidth}
%	\includegraphics[width=\textwidth]{./pic/p_error}
%	\caption{} \label{fig:5p2.2c}
%\end{subfigure}
%\begin{subfigure}[]{0.47\linewidth}
%	\includegraphics[width=\textwidth]{./pic/rom_freq}
%	\caption{} \label{fig:5p2.2d}
%\end{subfigure}
%\caption{(a) Pressure profile of the steady state. (b) Oscillatory mode of pressure located at $x=0.36$ for the unsteady flow. (c) Relative error between the high-fidelity and approximated pressure. (d) Approximation of the oscillations. }
%\label{fig:5p2.2}
%\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%% Combustor %%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \centering
  % Pressure steady
  \begin{subfigure}[]{0.48\linewidth}
          \includegraphics[scale=1]{Figures/paper-figure25.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[ylabel = pressure $p$,
%                 xlabel=$x$,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%%                 ymin=0,
%                 ymax = 1500000,
%                 samples = 100]
%                 \addplot[color=blue,style=solid,style=ultra thick]  table[x = x, y = pressure] {./data/Combustor/pressure_steady_state.txt};
%    \end{axis}%  
%  \end{tikzpicture}
  \caption{} \label{fig:5p2.2a}
  \label{steady_state}
  \end{subfigure}\hfill% 
  % Pressure oscilaltions
  \begin{subfigure}[]{0.48\linewidth}
        \includegraphics[scale=1]{Figures/paper-figure26.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[ylabel = pressure $p$,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 %legend entries={$k=102$ Adv,$k=201$ Adv,$k=102$ Div,$k=201$ Div,$k=102$ Skew,$k=201$ Skew},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 scaled y ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 ymin=0,
%%                 samples = 100,
%                 xmax = 0.06,
%                 ymin = 1360000,
%                 ymax = 1460000,
%                 tick label style={/pgf/number format/fixed} ]
%                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = pressure] {./data/Combustor/ciao.txt};
%    \end{axis}%  
%  \end{tikzpicture}
  \caption{} \label{fig:5p2.2b}
  \label{oscill_pressure}
  \end{subfigure}

% Total momentum
  \begin{subfigure}[]{0.48\linewidth}
      \includegraphics[scale=1]{Figures/paper-figure27.pdf}
%  \begin{tikzpicture}[scale=0.55]
%    \begin{semilogyaxis}[ylabel = $\| p-\tilde{p}\|_2$,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=south east,
%                 legend entries={$k=200$,$k=300$,$k=300$},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 scaled y ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 samples = 300,
%                 ymin = 0.000001,
%                 ymax = 0.0001]
%                 \addplot[color=red,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_200.txt};
%                 \addplot[color=blue,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_300.txt};
%                 \addplot[color=black!50!green,style=solid,style=thick]  table[x = t, y = error] {./data/Combustor/error_400.txt};
%    \end{semilogyaxis}%  
%  \end{tikzpicture}
  \caption{} \label{fig:5p2.2c}
  \label{error_growth_comb}
  \end{subfigure}\hfill% 
  % Pressure reduction  
  \begin{subfigure}[]{0.48\linewidth}
    \includegraphics[scale=1]{Figures/paper-figure28.pdf}
 % \begin{tikzpicture}[scale=0.55]
%    \begin{axis}[ylabel = pressure $p$,
%                 xlabel=$t$,
%                 label style={font=\Large},
%                 legend pos=north east,
%                 legend entries={High fidelity,  POD with $k=200$},
%                 legend style={font=\large},
%                 grid=both,
%                 ticks=both,
%                 width=1.4\linewidth, 
%                 height=1.0\linewidth,
%                 minor x tick num=1,
%                 minor y tick num=2,	
%                 %yticklabel style={/pgf/number format/.cd,fixed,precision=9},
%                 scaled x ticks = true,
%                 enlargelimits=false,
%                 scale only axis,
%                 xmin = 0.9,
%                 xmax = 0.98,
%                 ymin = 1390000,
%                 ymax = 1450000,
%                 tick label style={/pgf/number format/fixed} ]
%                 \addplot[color=green,style=solid,style=ultra thick]  table[x = t, y = pressure] {./data/Combustor/full.txt};
%                 \addplot[color=black,style=dashed,style=thick]  table[x = t, y = pressure] {./data/Combustor/red.txt};
%    \end{axis}%  
%  \end{tikzpicture}
  \caption{} \label{fig:5p2.2d}
  \label{oscill_focus}
  \end{subfigure}
  \caption{(\protect\subref{steady_state}) Pressure profile of the steady state.  (\protect\subref{oscill_pressure}) Oscillatory mode of pressure located at $x=0.36$ for the unsteady flow. (\protect\subref{error_growth_comb}) Relative error between the high-fidelity and approximated pressure. (\protect\subref{oscill_focus}) Approximation of the oscillations.} 
  \label{fig:5p2.2}
\end{figure}

The discontinuities that appear in the solution of \eqref{eq:5p2.10} suggests that a relatively large basis is required to resolve fine structures in the solution. Here, a POD basis is generated with $k=200$, $k=300$ and $k=400$ number of basis vectors. To avoid basis changes in the reduced system, only one POD basis is considered for $\rho$, $\rho u$ $\rho E$ and $\rho Y_{ox}$. The explicit SSP RK3 is then used to integrated the reduced system in time, for the unsteady system. The source terms are evaluated in the high-fidelity space and projected onto the reduced space. However, in principle, the DEIM can be applied to accelerate the evaluation this component.

\Cref{fig:5p2.2c} shows the approximation error of the pressure, due to MOR. It is observed that the approximation is consistently improved as the number of basis vectors increases. Furthermore, the approximate solution maintains high accuracy over a relatively long time-integration. The oscillations of pressure is demonstrated in \Cref{fig:5p2.2d}. The overall behaviour of pressure is well approximated by the reduced system. Similar results are obtained for a POD basis with higher number of modes.

We note that the discrete form of \eqref{eq:5p2.10} is not in the full skew-symmetric form. Nonetheless, the quasi-skew-symmetric discretization offers remarkable stability preservation.

\section{Conclusions} \label{sec:con}

Conservation of nonlinear invariants are not, in general, guaranteed with conventional model reduction techniques. The violation of such invariants often result in a qualitatively wrong or unstable reduced system, even when the high-fidelity system is stable. This is particularly important for fluid flow, where conservation of the energy, as a nonlinear invariant of the system, is crucial for a correct numerical evaluation.

In this paper, we discuss that conservative properties of the skew-symmetric form for fluid flow can naturally be extended to the reduced system. Conventional MOR techniques preserves the skew-symmetry of differential operator which result in the conservation of quadratic invariants at the level of the reduced system. Furthermore, the reduced system also contains quadratic invariants with respect to the reduced variables that approximates the invariants of the high-fidelity system. This results in the construction of a physically meaningful reduced system, rather than a mere couple systems of differential equations.

Numerical experiments for the incompressible and compressible Euler equation confirms conservation of mass, momentum and energy for the reduced model with the skew-symmetric discretization. In contrast, when a non-skew-symmetric form, e.g. divergence form or advective form, is considered, MOR does not necessarily yield a stable reduced system. On the other hand the skew-symmetric form consistently yields a robust reduced system over long time-integration, even when the reduced space does not represent the high-fidelity solution accurately.

Finally, a MOR of a quasi-skew-symmetric form for the CVRC model is presented. Although this model is not in a full skew-symmetric form and an explicit Runge-Kutta method used for time-integration, we still recover a reduced model with excellent stability properties.

\section*{Acknowledgement} The work was partially supported by AFOSR under grant FA9550-17-1-9241 and by SNSF under the grant number P1ELP2-175039. We also thank prof. Karen E. Willcox who provided insight and expertise that greatly assisted this work.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
